---
output: 
  pdf_document:
    fig_caption: yes
---
# Results

```{r setup, include = F, cache=FALSE}
# set working directory to R project instead of "./Thesis_Manuscript" folder
setwd("./")
# set default code chunk settings to save figures in Figures folder, show no output, and cache 
knitr::opts_chunk$set(fig.path = "./Thesis_Manuscript/Figures", echo = FALSE, cache=TRUE)
```

```{r load_packages_data, include=FALSE}
################### Packages ###########################
library(dplyr)
library(tidyr)
library(data.table)
library(magrittr)
library(lubridate) # dealing with time and dates
library(ggplot2)
library(ggthemes) # theme_classic() for graphs
library(stringr)
library(hms)
library(viridisLite)
library(forcats)
library(gridExtra)
library(ggpmisc) # package for adding line equation and R^2 to plots
library(viridis) # Color palette - Options: magma , inferno, plasma, viridis, cividis
library(scales)
library(cowplot) # for arranging multiple plots into a single figure
library(wesanderson)
library(olsrr) 
library(xtable) # creates tables in LaTex
library(MASS) # collection of datasets and functions
library(ISLR) # Dataset in Intro to statistical learning

# source functions 
source("../functions.R")
# define output directory
output_directory = "../output"
# create output directories (same as Insitu_Filtraiton_Analysis_script.Rmd)
createOutputDirectories()

##################### Read in Data from  project output ##########################
Master_analysis_table <- fread(file.path('../output/4_Filtration_Calculations/Filtration_Summary', "Master_Filtration_analysis_table.csv"))
Avg_TPM_summary_table <- fread(file.path('../output/5_TPM_OC_Summary', "Avg_TPM_summary_table.csv"))
Density_directory = "../Data/bivalve_density_community"
NPD_density = fread(file.path(Density_directory, "Insitu_Filter_NPD_bivalve_biomass_data.csv"))

##################### Data #########################################
# Remove San Diego filtration trial - not applicable to this analysis - different experimental set up
Master_analysis_table <- Master_analysis_table %>% 
  filter(!Site %in% c("San Diego"))

# Order Sites by Latitude
site_by_lat <- c("San Rafael", "Morro Bay", "Shellmaker", "Deanza") 

# transform Site variable to factor and arange by Latitude
Master_analysis_table <- arrange(transform(Master_analysis_table, Site = factor(Site,levels = site_by_lat)), Site)

 # Filtration trials only - exclude Negative controls
Filtration_only_data <- Master_analysis_table %>% 
  filter(Experiment %in% c("Filtration"))

# Filtration trials only - exclude Negative controls & Percent Chl removed greater than 0
### Important Note ## When Percent Chl removed is positive, so is L/hr/m^2 and vice visa. 
# Filtering by pcnt_Chl_rmvd effectively filters both values the same, so further analysis 
# withFiltration_pos_data serves both purposes. 
Filtration_pos_data <- Filtration_only_data %>% 
  filter(pcnt_Chl_rmvd > 0)

# Deanza data only - all trials
Deanza_data_all <- Master_analysis_table %>% 
  filter(Site %in% c("Deanza"))
# Deanza only - Filtraiton trials only
Deanza_Filter_data <- Deanza_data_all %>% 
  filter(Experiment %in% c("Filtration"))
# Deanza only- Positive Filtration only
Deanza_PosFilter_data <- Deanza_Filter_data %>% 
  filter(pcnt_Chl_rmvd > 0)

### Average TPM Data ######################
Avg_TPM_summary_table <- arrange(transform(Avg_TPM_summary_table, Site = factor(Site, levels = site_by_lat)), Site)

############### model formulas ###############
# linear model formula
x_y_formula <- y ~ x 
# Quadratic model
x2_y_formula <- y ~ poly(x, degree = 2)
# Exponential model
logy_x_formula <- log(y) ~ x
# logx
y_logx_fomula <- y ~ log(x)
# double log
logy_logx_formula <- log(y) ~ log(x)

############### Site Color Assignments ###############
viridis(4)
Site_colors <- c("San Rafael" = "#440154FF",
                 "Morro Bay" = "#31688EFF",
                 "Shellmaker" = "#35B779FF",
                 "Deanza" = "#FDE725FF")

############### Bivalve Species Color Assignments ###############
# wes_palettes # lists all current palattes 
# Color palette for Species - Royal2, Darjeeling2, Cavalcanti1, BottleRocket2, IsleofDogs1
density_palette <- rev(wes_palette("IsleofDogs1", 7, type = c("continuous")))
Species_colors <- c("Adula diegensis" = "#8D8680",
                    "Argopecten ventricosa" = "#CCC3C5",
                    "Crassostrea gigas" = "#6D6340",
                    "Geukensia demissa" = "#524D4F",
                    "Musculista senhousia" = "#B0915B",
                    "Mytilus galloprovincialis" = "#7E4B41",
                    "Ostrea lurida" = "#9986A5",
                    "Unknown mussel" = "black")

################# Labels for graphs  #########################
Hab_FR_Label <- expression('Habitat Filtration Rate (L/hr/m'^2*')')
Prt_Chl_Label <- expression(paste('Percent Chlorophyll ', alpha, ' Removed'))
Chl_ugL_Label <- expression(paste("Chlorophyll ", alpha, " (", mu, "g/L) "))
TPM_Label <- expression(paste('Total Particulate Matter (', mu,"g/L)"))
PIM_Label <- expression(paste('Particulate Inorganic Matter (', mu,"g/L)"))

###################### Functions ####################################
# function for number of samples - display on graph
n_mean_stats <- function(x){
  return(tibble(y = max(x) * 0.95, 
                    label = paste("n = ",length(x), "\n",
                                  'mean =', round(mean(x), 1), '\n')
                )
         )
}
# function for number of samples - 3 decimal places
n_mean_stats3 <- function(x){
  return(tibble(y = max(x) * 0.95, 
                    label = paste("n = ",length(x), "\n",
                                  'mean =', round(mean(x), 3), '\n')
                )
         )
}

# function to calculate average, standard deviation, outlier data. 
find_outlier <- function(data){
  average <- mean(data)
  stdev <- sd(data)
  # Outlier data defined by outside 2.2 standard deviations from the mean 
  outlier <- ifelse((data < (average - 2.2 * stdev) | (data > (average + 2.2 * stdev))),
         TRUE, FALSE)
}
```

```{r FR_ChlRmd_Site_boxplot, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=4.3, out.width="50%", fig.cap="The habitat level filtration rates and percent chlorophyll removed of all filtration trials across sites. \\label{figurelabel}"}
### Filtration by site (Filtration Trials only)

FR_box <- ggplot((Filtration_only_data), aes(Site, L_hr_m2)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Hab_FR_Label)
plot(FR_box) 

Chl_Rmd_box <- ggplot(Filtration_only_data, aes(Site, pcnt_Chl_rmvd)) +
  geom_boxplot(color = Site_colors) +
  #scale_y_continuous(labels = percent) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Prt_Chl_Label)
plot(Chl_Rmd_box)

#FR_Site_boxplot <- grid.arrange(FR_box, Chl_Rmd_box, nrow = 1)
#FR_Site_boxplot
#ggsave(FR_Site_boxplot, 
      # filename = "FR_Site_boxplot.pdf", 
      # path = "./Figures", 
       #fig.width = 6,
       #scale = 1 )

```

```{r FR_ChlRmd_Site_posFilter_boxplot, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=4.3, out.width="50%", fig.cap="The habitat level filtration rates and percent chlorophyll removed of filtration trials (positive values only) across sites. \\label{figurelabel}"}
# Filtration_pos_data defined in setup

FR_pos_box <- ggplot((Filtration_pos_data), aes(Site, L_hr_m2)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Hab_FR_Label)

plot(FR_pos_box)

ChlRmd_pos_box <- ggplot((Filtration_pos_data), aes(Site, pcnt_Chl_rmvd)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Prt_Chl_Label)
plot(ChlRmd_pos_box)

#grid.arrange(FR_TPM_box_pos, Chl_Rmd_box_pos, nrow = 1)
```

```{r FR_ChlRmd_TPM_point, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=4.3, out.width="50%", fig.cap="The habitat level filtration rates and percent chlorophyll removed of positive filtration trials in response to seston total particulate matter (TPM) . \\label{figurelabel}"}
FRPos_TPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

plot(FRPos_TPM_graph)

Chl_RmdPos_TPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

plot(Chl_RmdPos_TPM_graph)

#grid.arrange(FRPos_TPM_graph, Chl_RmdPos_TPM_graph, nrow = 1)
```

```{r FRpos_TPM_LM, eval=FALSE, cache=TRUE, include=FALSE}
FRPos_TPM_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Avg_TPM)
#summary(FR_TPM_lm)
ols_regress(FRPos_TPM_lm)
# Not significant
```

```{r ChlRmdpos_TPM_LM, eval=FALSE, cache=TRUE, include=FALSE}
ChlRmdPos_TPM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Avg_TPM)
#summary(ChlRmdPos_TPM_lm)
ols_regress(ChlRmdPos_TPM_lm)
# Not significant
```

```{r ChlRmdpos_TPM_LM_diagnostics, eval=FALSE, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_TPM_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_TPM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_TPM_lm)
```

```{r ChlRmd_TPM_Transform, eval=FALSE, fig.width=12, include=FALSE}
Chl_RmdPos_TPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

# log-log model predicitons
logChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_TPM))
# create range of Salinity values to predict with model
TPM_newrange <- data.frame(Avg_TPM = seq(from = 0, to = 0.04, by = 0.001))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
loglogTPM_Pred <- data.frame(pred_ChlRmd = exp(predict(logChlRmdPos_logTPM_lm, newdata = TPM_newrange)))
pred_loglog_TPM_df <- data.frame(TPM_newrange, loglogTPM_Pred)
  

logChlRmdPos_logTPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglog_TPM_df, aes(x = Avg_TPM, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'log(Y) ~ log(X)') +
  guides(fill = FALSE)

# Y-log model predicitons
ChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Avg_TPM))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
logTPM_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_logTPM_lm, newdata = TPM_newrange))
pred_logTPM_df <- data.frame(TPM_newrange, logTPM_Pred)

ChlRmdPos_logTPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_line(data = pred_logTPM_df, aes(x = Avg_TPM, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'Y ~ log(X)') +
  guides(fill = FALSE)

# Y~x + x^2 model predicitons
ChlRmdPos_TPM2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Avg_TPM, degree = 2, raw = T))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
TPM2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_TPM2_lm, newdata = TPM_newrange))
pred_TPM2_df <- data.frame(TPM_newrange, TPM2_Pred)

ChlRmdPos_TPM2_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_line(data = pred_TPM2_df, aes(x = Avg_TPM, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'Y ~ x + x^2') +
  guides(fill = FALSE) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x2_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")

grid.arrange(Chl_RmdPos_TPM_graph, logChlRmdPos_logTPM_graph, 
             ChlRmdPos_logTPM_graph, ChlRmdPos_TPM2_graph, nrow = 2)
```

```{r logChlRmdPos_logTPM_lm, eval=FALSE, cache=TRUE, include=FALSE}
logChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_TPM))
#summary(ChlRmdPos_TPM_lm)
ols_regress(logChlRmdPos_logTPM_lm)
```

```{r logChlRmdPos_logTPM_lm_diag, eval=FALSE, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(logChlRmdPos_logTPM_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(logChlRmdPos_logTPM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(logChlRmdPos_logTPM_lm)
```

```{r ChlRmdPos_logTPM_lm, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Avg_TPM))
#summary(ChlRmdPos_logTPM_lm)
ols_regress(ChlRmdPos_logTPM_lm)
```

```{r ChlRmdPos_TPM2_lm, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_TPM2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Avg_TPM, degree = 2, raw = T))
#summary(ChlRmdPos_TPM_lm)
ols_regress(ChlRmdPos_TPM2_lm)
```

```{r ChlRmdPos_TPM2_lm_diag, eval=FALSE, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_TPM2_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(logChlRmdPos_logTPM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(logChlRmdPos_logTPM_lm)
```

```{r NPD_FRPos_TPM_graph, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=4.3, out.width="50%", fig.cap="The positive habitat level filtration rates in response to seston total particulate matter (TPM). \\label{figurelabel}"}
NPD_FRPos_TPM_graph <- ggplot((Deanza_PosFilter_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  # geom_abline(aes(intercept=0, slope=1)) +
  #scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(NPD_FRPos_TPM_graph)

NPD_ChlRmdPos_TPM_graph <- ggplot((Deanza_PosFilter_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  # geom_abline(aes(intercept=0, slope=1)) +
  #scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(NPD_ChlRmdPos_TPM_graph)
#grid.arrange(NPD_FRPos_TPM_graph, NPD_ChlRmdPos_TPM_graph, nrow = 1)
```

```{r NPD_FRpos_TPM_LM, eval=FALSE, cache=T, include=FALSE}
NPD_PosFR_TPM_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Avg_TPM)
ols_regress(NPD_PosFR_TPM_lm)
```

```{r NPD_ChlRmdPos_TPM_LM, eval=FALSE, cache=T, include=FALSE}
NPD_PosChlRmd_TPM_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Avg_TPM)
ols_regress(NPD_PosChlRmd_TPM_lm)
```

```{r NPD_PosChlRmd_TPM_lm_diag, eval=FALSE, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(NPD_PosChlRmd_TPM_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(NPD_PosChlRmd_TPM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(NPD_PosChlRmd_TPM_lm)
```

```{r FRPos_Chlpos_PIM, eval=FALSE, include=FALSE}
FRPos_PIM_graph <- ggplot(Filtration_pos_data, aes(Avg_PIM, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = PIM_Label,
       y = Hab_FR_Label,
       title = 'Positive Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(FRPos_PIM_graph)

Chl_RmdPos_PIM_graph <- ggplot(Filtration_pos_data, aes(Avg_PIM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = PIM_Label,
       y = Prt_Chl_Label,
       title = 'Positive Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(FRPos_PIM_graph)
#grid.arrange(FRPos_PIM_graph, Chl_RmdPos_PIM_graph, nrow = 1)
```

```{r FRPos_PIM_LM, eval=FALSE, cache=TRUE, include=FALSE}
FRPos_PIM_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Avg_PIM)
ols_regress(FRPos_PIM_lm)
```

```{r ChlRmdPos_PIM_LM, eval=FALSE, cache=TRUE, include=FALSE}
ChlRmdPos_PIM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Avg_PIM)
ols_regress(ChlRmdPos_PIM_lm)
```

```{r ChlRmdPos_PIM_LM_Diag, eval=FALSE, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_PIM_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_PIM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_PIM_lm)
```

```{r Deanza_Filter_Pos_PIM, eval=FALSE, cache=TRUE, include=FALSE}
NPD_FRPos_PIM_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_PIM, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = PIM_Label,
       y = Hab_FR_Label,
       title = 'Deanza Positive Filtration') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_PIM_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_PIM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = PIM_Label,
       y = Prt_Chl_Label,
       title = 'Deanza Positive Filtration') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(NPD_FRPos_PIM_graph, NPD_ChlRmdPos_PIM_graph, nrow = 1)
```

```{r NPD_FRpos_PIM_LM, eval=FALSE, cache=TRUE, include=FALSE}
NPD_FRpos_PIM_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Avg_PIM)
ols_regress(NPD_FRpos_PIM_lm)
```

```{r NPD_ChlRmdpos_PIM_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdpos_PIM_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Avg_PIM)
ols_regress(NPD_ChlRmdpos_PIM_lm)
```

```{r NPD_ChlRmdpos_PIM_LM_diag, eval=FALSE, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(NPD_ChlRmdpos_PIM_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(NPD_ChlRmdpos_PIM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(NPD_ChlRmdpos_PIM_lm)
```

```{r FRPos_OC, eval=FALSE,  cache=TRUE, include=FALSE}
FRPos_OC_graph <- ggplot(Filtration_pos_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_RmdPos_OC_graph <- ggplot(Filtration_pos_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FRPos_OC_graph, Chl_RmdPos_OC_graph, nrow = 1)
```

```{r FRPos_OC_LM, eval=FALSE, cache=TRUE, include=FALSE}
FRPos_OC_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Avg_OC_Ratio)
ols_regress(FRPos_OC_lm)
```

```{r ChlrRmdPos_OC_LM, eval=FALSE, cache=TRUE, include=FALSE}
ChlRmdPos_OC_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Avg_OC_Ratio)
ols_regress(ChlRmdPos_OC_lm)
```

```{r ChlRmdPos_OC_LM_diag, eval=FALSE, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_OC_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_OC_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_OC_lm)
```

```{r ChlRmdPos_OC_LM_Trans, eval=FALSE, cache=TRUE, include=FALSE}
logChl_RmdPos_logOC_graph <- ggplot(Filtration_pos_data, 
                                    aes(log(Avg_OC_Ratio), log(pcnt_Chl_rmvd))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = expression(paste(log[n],' Organic Content of Seston (fraction)')),
       y = expression(paste(log[n], " Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Filtration Trials') +
  guides(fill = FALSE)

# log-log model predicitons
logChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_OC_Ratio))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
OC_newrange <- data.frame(Avg_OC_Ratio = seq(from = 0.6, to = 1, by = 0.025))
loglogOC_Pred <- data.frame(pred_ChlRmd = exp(predict(logChlRmdPos_logOC_lm, newdata = OC_newrange)))
pred_loglogOC_df <- data.frame(OC_newrange, loglogOC_Pred)

ChlRmdPos_loglogOC_graph <- ggplot((Filtration_pos_data), aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglogOC_df, aes(x = Avg_OC_Ratio, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'log(y) ~ log(x)') +
  guides(fill = FALSE)

# Y-log model predicitons
ChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Avg_OC_Ratio))
logOC_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_logOC_lm, newdata = OC_newrange))
pred_logOC_df <- data.frame(OC_newrange, logOC_Pred)

ChlRmdPos_logOC_graph <- ggplot((Filtration_pos_data), aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_line(data = pred_logOC_df, aes(x = Avg_OC_Ratio, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'y ~ log(x)') +
  guides(fill = FALSE)

# Y-x + x^2 model predicitons
ChlRmdPos_OC2_lm <- lm(data = Filtration_pos_data, 
                         pcnt_Chl_rmvd ~ poly(Avg_OC_Ratio, degree = 2, raw = T))
OC2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_OC2_lm, newdata = OC_newrange))
pred_OC2_df <- data.frame(OC_newrange, OC2_Pred)

ChlRmdPos_OC2_graph <- ggplot((Filtration_pos_data), aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_line(data = pred_OC2_df, aes(x = Avg_OC_Ratio, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'y ~ x + x^2') +
  guides(fill = FALSE)

grid.arrange(logChl_RmdPos_logOC_graph, ChlRmdPos_loglogOC_graph,
             ChlRmdPos_logOC_graph, ChlRmdPos_OC2_graph, nrow = 2)

```

```{r ChlRmdPos_Loglog_LM, eval=FALSE, cache=TRUE, include=FALSE}
logChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_OC_Ratio))
ols_regress(logChlRmdPos_logOC_lm)
```

```{r ChlRmdPos_OC_logLM, eval=FALSE, cache=TRUE, include=FALSE}
ChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Avg_OC_Ratio))
ols_regress(ChlRmdPos_logOC_lm)
```

```{r ChlrRmdPos_OC_PolyLM, eval=FALSE, cache=TRUE, include=FALSE}
ChlRmdPos_OC2_lm <- lm(data = Filtration_pos_data, 
                       pcnt_Chl_rmvd ~ poly(Avg_OC_Ratio, degree = 2, raw = T))
ols_regress(ChlRmdPos_OC2_lm)
```

```{r Deanza_Filter_Pos_OC_graph, eval=FALSE, cache=TRUE, include=FALSE}
FRPos_OC_NPD_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'Newport Deanza Positive Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plor(FRPos_OC_NPD_graph)

Chl_RmdPos_OC_NPD_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'Newport Deanza Positive Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(Chl_RmdPos_OC_NPD_graph)
#grid.arrange(FRPos_OC_NPD_graph, Chl_RmdPos_OC_NPD_graph, nrow = 1)
```

```{r NPD_FRpos_OC_LM, eval=FALSE, cache=TRUE, include=FALSE}
FRPos_OC_NPD_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Avg_OC_Ratio)
ols_regress(FRPos_OC_NPD_lm)
```

```{r NPD_ChlRmdpos_OC_LM, eval=FALSE, cache=TRUE, include=FALSE}
ChlRmdPos_OC_NPD_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Avg_OC_Ratio)
ols_regress(ChlRmdPos_OC_NPD_lm)
```

```{r NPD_ChlRmdpos_OC_LM_diag, eval=FALSE, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_OC_NPD_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_OC_NPD_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_OC_NPD_lm)
```

```{r NPD_ChlRmdpos_OC_logLM, eval=FALSE, cache=TRUE, include=FALSE}
ChlRmdPos_logOC_NPD_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Avg_OC_Ratio))
ols_regress(ChlRmdPos_logOC_NPD_lm)
```

```{r ANOVA_ChlRmdPos_OC_NPD_LM, eval=FALSE, include=FALSE}
anova(ChlRmdPos_OC_NPD_lm, ChlRmdPos_logOC_NPD_lm)
```

```{r NPD_ChlRmdpos_OC_loglogLM, eval=FALSE, cache=TRUE, include=FALSE}
logChlRmdPos_logOC_NPD_lm <- lm(data = Deanza_PosFilter_data, log(pcnt_Chl_rmvd) ~ log(Avg_OC_Ratio))
ols_regress(logChlRmdPos_logOC_NPD_lm)
```

```{r TPM_OC_graphs, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=6, out.width="50%", fig.cap="The relationship between seston total particulate matter (TPM) and seston organic content (OC) across all sites and all trials. \\label{figurelabel}"}

TPM_OC <- ggplot(data = Avg_TPM_summary_table, aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "All Trials") + 
  theme_classic() +
  #geom_text(aes(label=Date), nudge_x = 0.007, nudge_y = 0, check_overlap = T)
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(TPM_OC)

# I don't think a box plot is valuable to show the relationship (AM- 2020_8_24)
TPM_box <- ggplot((Avg_TPM_summary_table), aes(Site, Avg_TPM)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats3, geom = "text") + # mean isn't working 
  labs(x = 'Site',
       y = TPM_Label,
       title = "Total Particulate Matter by Site")
# I don't think a box plot is valuable to show the relationship (AM- 2020_8_24)
OC_box <- ggplot((Avg_TPM_summary_table), aes(Site, Avg_OC_Ratio)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats3, geom = "text") + 
  labs(x = 'Site',
       y = "Average Organic Content Ratio",
       title = "Seston Organic Content Ratio by Site")

# Y-log model
# I don't think a log transformation is valuable to show the relationship (AM- 2020_8_24)
OC_logTPM_all_LM <- lm(data = Avg_TPM_summary_table, Avg_OC_Ratio ~ log(Avg_TPM))
TPM_newrange <- data.frame(Avg_TPM = seq(from = 0, to = 0.075, by = 0.005))
TPMlog_Pred <- data.frame(Avg_OC_Ratio = predict(OC_logTPM_all_LM, newdata = TPM_newrange))
pred_TPMlog_df <- data.frame(TPM_newrange, TPMlog_Pred)

OC_logTPM_graph <- ggplot(Avg_TPM_summary_table, aes(Avg_TPM, Avg_OC_Ratio)) +
  geom_line(data = pred_TPMlog_df, aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = TPM_Label,
       y = "Average Organic Content Ratio",
       title = 'All trials',
       subtitle = 'y ~ log(x)')

# grid.arrange(OC_box, TPM_box, TPM_OC, OC_logTPM_graph, nrow = 2)
```

```{r TPM_OC_LM, eval=FALSE, cache=TRUE, include=FALSE}
OC_TPM_all_LM <- lm(data = Avg_TPM_summary_table, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_all_LM)
```

```{r OC_logTPM_all_LM, eval=FALSE, cache=TRUE, include=FALSE}
OC_logTPM_all_LM <- lm(data = Avg_TPM_summary_table, Avg_OC_Ratio ~ log(Avg_TPM))
ols_regress(OC_logTPM_all_LM)
```

```{r OC_logTPM_all_LM_diag, eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(OC_logTPM_all_LM)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(OC_logTPM_all_LM)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(OC_logTPM_all_LM))
```

```{r logOC_logTPM_all_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
logOC_logTPM_all_LM <- lm(data = Avg_TPM_summary_table, log(Avg_OC_Ratio) ~ log(Avg_TPM))
ols_regress(logOC_logTPM_all_LM)
```

```{r TPM_OC_Sites_graphs, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=6, out.width="50%", fig.cap="The relationship between seston total particulate matter (TPM) and seston organic content (OC) across all sites and all trials. \\label{figurelabel}"}

TPM_OC_Deanza <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Deanza")),
                        aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Deanza") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_NPSM <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Shellmaker")), 
                     aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Shellmaker") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_SR <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "San Rafael")),
                   aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "San Rafael") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_MB <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Morro Bay")), 
                   aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Morro Bay") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_bysite_graph <- grid.arrange(TPM_OC_Deanza, TPM_OC_NPSM, TPM_OC_SR, TPM_OC_MB, nrow = 2)
plot(TPM_OC_bysite_graph)
```

```{r SR_TPM_OC_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
TPM_SR <- Avg_TPM_summary_table %>% filter(Site == "San Rafael")

OC_TPM_SR_LM <- lm(data = TPM_SR, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_SR_LM)
```

```{r MB_TPM_OC_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
TPM_MB <- Avg_TPM_summary_table %>% filter(Site == "Morro Bay")

OC_TPM_MB_LM <- lm(data = TPM_MB, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_MB_LM)
```

```{r NPSM_TPM_OC_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
TPM_NPSM <- Avg_TPM_summary_table %>% filter(Site == "Shellmaker")

OC_TPM_NPSM_LM <- lm(data = TPM_NPSM, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_NPSM_LM)
```

```{r NPD_TPM_OC_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

OC_TPM_NPD_LM <- lm(data = TPM_NPD, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_NPD_LM)
```

```{r NPD_TPM_OC_LMlog, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

OC_logTPM_NPD_LM <- lm(data = TPM_NPD, Avg_OC_Ratio ~ log(Avg_TPM))
ols_regress(OC_logTPM_NPD_LM)
```

```{r NPD_TPM_OC_LMloglog, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

logOC_logTPM_NPD_LM <- lm(data = TPM_NPD, log(Avg_OC_Ratio) ~ log(Avg_TPM))
ols_regress(logOC_logTPM_NPD_LM)
```

```{r Filter_Temp, eval=FALSE, fig.height=5, fig.width=14, cache=TRUE, include=FALSE}

FR_pos_Temp <- ggplot(Filtration_pos_data, aes(Temp_C_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Temp <- ggplot(Filtration_pos_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'Positive ChlRmd') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_pos_Temp, Chl_Rmd_pos_Temp, nrow = 1)
```

```{r FRpos_Temp_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
FRPos_temp_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(FRPos_temp_lm)
```

```{r ChlRmdpos_Temp_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_temp_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(ChlRmdPos_temp_lm)
```

```{r ChlRmdpos_Temp_diag, eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_temp_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_temp_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_temp_lm))
```


```{r NPD_Filter_Temp, eval=FALSE, fig.height=10, fig.width=12, cache=TRUE, include=FALSE}

NPD_Chl_RmdPos_Temp <- ggplot(Deanza_PosFilter_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'Deanza Positive Filter Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

# Predict Y ~ log(x) model
NPD_ChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Temp_C_Up))
Temp_newrange <- data.frame(Temp_C_Up = seq(from = 18, to = 21, by = 0.25))
Templog_Pred <- data.frame(pred_ChlRmd = predict(NPD_ChlRmdPos_logtemp_lm, newdata = Temp_newrange))
pred_Templog_df <- data.frame(Temp_newrange, Templog_Pred)

NPD_ChlRmdPos_logTemp_graph <- ggplot((Deanza_PosFilter_data), aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Templog_df, aes(x = Temp_C_Up, y = pred_ChlRmd)) +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'NPD Pos Filtration Trials',
       subtitle = 'y ~ log(x)') +
  guides(fill = FALSE)

# Predict log(Y) ~ log(x) model
NPD_logChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, log(pcnt_Chl_rmvd) ~ log(Temp_C_Up))
Temploglog_Pred <- data.frame(pred_ChlRmd = exp(predict(NPD_logChlRmdPos_logtemp_lm, newdata = Temp_newrange)))
pred_Temploglog_df <- data.frame(Temp_newrange, Temploglog_Pred)

NPD_ChlRmdPos_loglogTemp_graph <- ggplot((Deanza_PosFilter_data), aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Temploglog_df, aes(x = Temp_C_Up, y = pred_ChlRmd)) +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'NPD Pos Filtration Trials',
       subtitle = 'log(y) ~ log(x)') +
  guides(fill = FALSE)

# Predict Y ~ x + x^2 model
NPD_ChlRmdPos_temp2_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ poly(Temp_C_Up, degree = 2, raw = T))
Temp2_Pred <- data.frame(pred_ChlRmd = predict(NPD_ChlRmdPos_temp2_lm, newdata = Temp_newrange))
pred_Temp2_df <- data.frame(Temp_newrange, Temp2_Pred)

NPD_ChlRmdPos_Temp2_graph <- ggplot((Deanza_PosFilter_data), aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Temp2_df, aes(x = Temp_C_Up, y = pred_ChlRmd)) +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'NPD Pos Filtration Trials',
       subtitle = 'y ~ x + x^2') +
  guides(fill = FALSE)

grid.arrange(NPD_Chl_RmdPos_Temp, NPD_ChlRmdPos_logTemp_graph,
             NPD_ChlRmdPos_loglogTemp_graph, NPD_ChlRmdPos_Temp2_graph, nrow = 2)
```

```{r NPD_ChlRmdpos_Temp_LM, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdPos_temp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(NPD_ChlRmdPos_temp_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Temp_C_Up))
ols_regress(NPD_ChlRmdPos_logtemp_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_logChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, log(pcnt_Chl_rmvd) ~ log(Temp_C_Up))
ols_regress(NPD_logChlRmdPos_logtemp_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdPos_temp2_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ poly(Temp_C_Up, degree = 2, raw = T))
ols_regress(NPD_ChlRmdPos_temp2_lm)
```

```{r Filter_Salinity, eval=FALSE, fig.height=5, fig.width=14, cache=TRUE, include=FALSE}

FR_pos_Sal <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'Positive FR only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Sal <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_pos_Sal, Chl_Rmd_pos_Sal, nrow = 1)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
FRPos_Sal_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Sal_ppt_Up)
ols_regress(FRPos_Sal_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_Sal_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Sal_ppt_Up)
ols_regress(ChlRmdPos_Sal_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_Sal_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_Sal_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_Sal_lm))
```

```{r LogChlRmdPos_LogSalinity_graph, eval=FALSE, fig.height=12, fig.width=12, cache=TRUE, include=FALSE}
### Graph with log-log axes
logChlRmd_pos_logSal_graph <- ggplot(Filtration_pos_data, aes(log(Sal_ppt_Up), log(pcnt_Chl_rmvd))) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = expression('log'[n]*' Salinity Upstream (ppt)'),
       y = expression(paste(log[n], " Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only') +
  stat_poly_eq(formula = x_y_formula, parse = TRUE)

# log-log model
logChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Sal_ppt_Up))
# create range of Salinity values to predict with model
Sal_newrange <- data.frame(Sal_ppt_Up = seq(from = 29, to = 38, by = 0.5))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
loglogSal_Pred <- data.frame(pred_ChlRmd = exp(predict(logChlRmdPos_logSal_lm, newdata = Sal_newrange)))
pred_loglog_Sal_df <- data.frame(Sal_newrange, loglogSal_Pred)

# model coefficents 
#coef(logChlRmdPos_logSal_lm)

## Graph with regualar x & y axes, log-log model
logChlRmd_pos_logSal_graph2 <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglog_Sal_df, aes(x = Sal_ppt_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = expression(paste(" Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only',
       subtitle = "Log(y) ~ Log(x) pretty sure correct line")

# log X transformed model
ChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Sal_ppt_Up))
pred_ChlRmdPos_logSal_df <- data.frame(Sal_newrange,
                                       pred_ChlRmd = predict(ChlRmdPos_logSal_lm, 
                                                             newdata = Sal_newrange))

ChlRmd_pos_logSal_graph <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_ChlRmdPos_logSal_df, aes(x = Sal_ppt_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = expression(paste(" Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only',
       subtitle = "y ~ log(x)")

# Polynomial ^2 transformation
ChlRmdPos_Sal2_lm <- lm(data = Filtration_pos_data, 
                        pcnt_Chl_rmvd ~ poly(Sal_ppt_Up, degree = 2, raw = T))
# predict values with model and new Sal range values
Sal2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_Sal2_lm, newdata = Sal_newrange))
pred_ChlRmdPos_Sal2_df2 <- data.frame(Sal_newrange, Sal2_Pred)

ChlRmd_pos_Sal2_graph <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_ChlRmdPos_Sal2_df2, aes(x = Sal_ppt_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = expression(paste(" Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only',
       subtitle = "y ~  x + x^2")

# Polynomial ^3 transformation
ChlRmdPos_Sal3_lm <- lm(data = Filtration_pos_data, 
                        pcnt_Chl_rmvd ~ poly(Sal_ppt_Up, degree = 3, raw = T))
pred_ChlRmdPos_Sal3_df <- data.frame(pred_ChlRmd = predict(ChlRmdPos_Sal3_lm, newdata = Sal_newrange),
                                       Sal_newrange)

ChlRmd_pos_Sal3_graph <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_ChlRmdPos_Sal3_df, aes(x = Sal_ppt_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = expression(paste(" Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only',
       subtitle = "y ~  x + x^3")

grid.arrange(logChlRmd_pos_logSal_graph, logChlRmd_pos_logSal_graph2, 
             ChlRmd_pos_logSal_graph, ChlRmd_pos_Sal2_graph, ChlRmd_pos_Sal3_graph, nrow = 3)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
logChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Sal_ppt_Up))
ols_regress(logChlRmdPos_logSal_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(logChlRmdPos_logSal_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(logChlRmdPos_logSal_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(logChlRmdPos_logSal_lm))
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Sal_ppt_Up))
ols_regress(ChlRmdPos_logSal_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_logSal_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_logSal_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_logSal_lm))
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
anova(ChlRmdPos_Sal_lm, ChlRmdPos_logSal_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_Sal2_lm <- lm(data = Filtration_pos_data, 
                        pcnt_Chl_rmvd ~ poly(Sal_ppt_Up, degree = 2, raw = T))
ols_regress(ChlRmdPos_Sal2_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_Sal3_lm <- lm(data = Filtration_pos_data, 
                        pcnt_Chl_rmvd ~ poly(Sal_ppt_Up, degree = 3, raw = T))
ols_regress(ChlRmdPos_Sal2_lm)
```

```{r NPD_Filter_Salinity, eval=FALSE, fig.height=5, fig.width=12, cache=TRUE, include=FALSE}
NPD_FRPos_Salinity <- ggplot(Deanza_PosFilter_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'NPD Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Salinity <- ggplot(Deanza_PosFilter_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'NPD Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(NPD_FRPos_Salinity, NPD_ChlRmdPos_Salinity, nrow = 1)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_FRPos_Sal_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Sal_ppt_Up)
ols_regress(NPD_FRPos_Sal_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdPos_Sal_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Sal_ppt_Up)
ols_regress(NPD_ChlRmdPos_Sal_lm)
```

```{r Filter_Chl, eval=FALSE, fig.height=15, fig.width=14, cache=TRUE, include=FALSE}

FR_pos_Chl <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Chl <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

# Y-log model
ChlRmdPos_logChl_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Chl_ug_L_Up))
# create range of Salinity values to predict with model
Chl_newrange <- data.frame(Chl_ug_L_Up = seq(from = 0, to = 8, by = 0.5))
logChl_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_logChl_lm, newdata = Chl_newrange))
pred_logChl_df <- data.frame(Chl_newrange, logChl_Pred)

ChlRmdpos_Chllog_graph <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_logChl_df, aes(x = Chl_ug_L_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'Y ~ log(x)')

# log-log model
ChlRmdPos_loglogChl_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Chl_ug_L_Up))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
loglogChl_Pred <- data.frame(pred_ChlRmd = exp(predict(ChlRmdPos_loglogChl_lm, newdata = Chl_newrange)))
pred_loglogChl_df <- data.frame(Chl_newrange, loglogChl_Pred)

ChlRmdpos_Chlloglog_graph <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglogChl_df, aes(x = Chl_ug_L_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'log(y) ~ log(x)')

# Y-x + x^2 model
ChlRmdPos_Chl2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Chl_ug_L_Up, degree = 2, raw = T))
Chl2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_Chl2_lm, newdata = Chl_newrange))
pred_Chl2_df <- data.frame(Chl_newrange, Chl2_Pred)

ChlRmdpos_Chl2_graph <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Chl2_df, aes(x = Chl_ug_L_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'Y ~ x + x^2')

grid.arrange(FR_pos_Chl, Chl_Rmd_pos_Chl, 
             ChlRmdpos_Chllog_graph, ChlRmdpos_Chlloglog_graph, 
             ChlRmdpos_Chl2_graph, nrow = 3)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
FRPos_Chl_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Chl_ug_L_Up)
ols_regress(FRPos_Chl_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_Chl_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Chl_ug_L_Up)
ols_regress(ChlRmdPos_Chl_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(ChlRmdPos_Chl_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_Chl_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_Chl_lm))
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_logChl_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Chl_ug_L_Up))
ols_regress(ChlRmdPos_logChl_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
logChlRmdPos_logChl_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Chl_ug_L_Up))
ols_regress(logChlRmdPos_logChl_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_Chl2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Chl_ug_L_Up, degree = 2, raw = T))
ols_regress(ChlRmdPos_Chl2_lm)
```

```{r NPD_Filter_Chl, eval=FALSE, fig.height=5, fig.width=12, cache=TRUE, include=FALSE}

NPD_FRPos_Chl <- ggplot(Deanza_PosFilter_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label,
       title = "NPD Positive Filtraiton") +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Chl <- ggplot(Deanza_Filter_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = "NPD Positive Filtraiton") +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(NPD_FRPos_Chl, NPD_ChlRmdPos_Chl, nrow = 1)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_FRPos_Chl_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Chl_ug_L_Up)
ols_regress(NPD_FRPos_Chl_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdPos_Chl_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Chl_ug_L_Up)
ols_regress(NPD_ChlRmdPos_Chl_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(NPD_ChlRmdPos_Chl_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(NPD_ChlRmdPos_Chl_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(NPD_ChlRmdPos_Chl_lm))
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdPos_logChl_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Chl_ug_L_Up))
ols_regress(NPD_ChlRmdPos_logChl_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
logChlRmdPos_logChl_lm <- lm(data = Deanza_PosFilter_data, log(pcnt_Chl_rmvd) ~ log(Chl_ug_L_Up))
ols_regress(logChlRmdPos_logChl_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdPos_Chl2_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ poly(Chl_ug_L_Up, degree = 2, raw = T))
ols_regress(NPD_ChlRmdPos_Chl2_lm)
```

```{r Filter_Turbidity, eval=FALSE, fig.height=15, fig.width=14, cache=TRUE, include=FALSE}

FR_pos_Turb <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Turb <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

# Y-log model
ChlRmdPos_logTurb_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Turbidity_NTU_Up))
Turb_newrange <- data.frame(Turbidity_NTU_Up = seq(from = 2, to = 31, by = 1))
logTurb_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_logTurb_lm, newdata = Turb_newrange))
pred_logTurb_df <- data.frame(Turb_newrange, logTurb_Pred)

ChlRmdpos_Turblog_graph <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_logTurb_df, aes(x = Turbidity_NTU_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'y ~ log(x)')

#log-log model
logChlRmdPos_logTurb_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Turbidity_NTU_Up))
loglogTurb_Pred <- data.frame(pred_ChlRmd = exp(predict(logChlRmdPos_logTurb_lm, newdata = Turb_newrange)))
pred_loglogTurb_df <- data.frame(Turb_newrange, loglogTurb_Pred)

ChlRmdpos_Turbloglog_graph <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglogTurb_df, aes(x = Turbidity_NTU_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'log(y) ~ log(x)')

# Y ~ x + x^2 model
ChlRmdPos_Turb2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Turbidity_NTU_Up, degree = 2, raw = T))
Turb2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_Turb2_lm, newdata = Turb_newrange))
pred_Turb2_df <- data.frame(Turb_newrange, Turb2_Pred )

ChlRmdpos_Turb2_graph <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Turb2_df, aes(x = Turbidity_NTU_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'Y ~ x + x^2') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")

grid.arrange(FR_pos_Turb, Chl_Rmd_pos_Turb,
             ChlRmdpos_Turblog_graph, ChlRmdpos_Turbloglog_graph,
             ChlRmdpos_Turb2_graph, nrow = 3)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
FRPos_Turb_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Turbidity_NTU_Up)
ols_regress(FRPos_Turb_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_Turb_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Turbidity_NTU_Up)
ols_regress(ChlRmdPos_Turb_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_logTurb_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Turbidity_NTU_Up))
ols_regress(ChlRmdPos_logTurb_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
logChlRmdPos_logTurb_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Turbidity_NTU_Up))
ols_regress(logChlRmdPos_logTurb_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
ChlRmdPos_Turb2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Turbidity_NTU_Up, degree = 2, raw = T))
ols_regress(ChlRmdPos_Turb2_lm)
```

```{r NPD_Filter_Turbidity, eval=FALSE, fig.height=5, fig.width=12, cache=TRUE, include=FALSE}

NPD_FRPos_Turb <- ggplot(Deanza_PosFilter_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'Deanza - Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Turb <- ggplot(Deanza_PosFilter_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Deanza - Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")



grid.arrange(NPD_FRPos_Turb, NPD_ChlRmdPos_Turb, nrow = 1)

```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_FRPos_Turb_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Turbidity_NTU_Up)
ols_regress(NPD_FRPos_Turb_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
NPD_ChlRmdPos_Turb_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Turbidity_NTU_Up)
ols_regress(NPD_ChlRmdPos_Turb_lm)
```

```{r Oly_DTW_Shell_length, fig.height=5, fig.width=6, cache=TRUE, include=FALSE}

# Determine what quadrat samples have missing data (NAs)
NPD_biv_bio_summary <- NPD_density %>% 
  group_by(excavation_sample) %>% 
  summarize(avg_DTW = mean(tissue_dry_weight_g))

# what are the unique species in dataset
#unique(NPD_density$species)

# Still contains missing data --> which quadrats to use for analyses
NPD_bivalve_data_clean <- NPD_density %>% 
  filter(!excavation_sample %in% c("Q10", "Q4", "Q8")) %>% 
  mutate(species = ifelse(grepl("adula", ignore.case = T, species), "Adula diegensis",
                          ifelse(grepl("muscul.", ignore.case = T, species), "Musculista senhousia",
                                 ifelse(grepl("myt", ignore.case = T, species), "Mytilus galloprovincialis",
                                        ifelse(grepl(".lurida", ignore.case = T, species), "Ostrea lurida",
                                               ifelse(grepl("mussel", ignore.case = T, species), "Unknown mussel",
                                                      ifelse(grepl(".spinosum", ignore.case = T, species), "Crucibulum spinosum",
                                                       "Pattern Not Found"))))))) %>% 
  # Filter out unclassified/ empty species & samples less than 0g (processing error, doesn't make sense)
  filter(!species %in% c("Pattern Not Found", "Crucibulum spinosum"))


#Olympia DTW predicted by Shell Length - Newport, CA
# All excavation quadrat samples processed to date aggregated 
NPD_oly <- NPD_bivalve_data_clean %>% 
  filter(species == "Ostrea lurida") %>% 
  drop_na() %>% 
  as_tibble() 

Oly_shell_DTW <- ggplot(NPD_oly, aes(length_mm, tissue_dry_weight_g)) +
  geom_smooth(method = lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'With outlier (bad data)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top") +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

plot(Oly_shell_DTW)
```

```{r Oly_DTW_SH_outlier_rmd, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=6, out.width="50%", fig.cap="The relationship between *O. lurida* shell length and its dry tissue weight (DTW) in Newport Bay, California at the Deanza restoration site. \\label{figurelabel}"}
# Remove outlier and negative DTW value
NPD_oly_outRmd <- NPD_oly %>%
  mutate(DTW_outlier = find_outlier(NPD_oly$tissue_dry_weight_g)) %>% 
  filter(DTW_outlier == FALSE & tissue_dry_weight_g >= 0) 

# Graph with outliers removed
Oly_shell_DTW_rm_out <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  geom_smooth(method=lm, formula = x_y_formula, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
 # scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Outlier removed (outside mean +- 2.2 SD)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom") +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

plot(Oly_shell_DTW_rm_out)
```

```{r Linear_model_DTW_length, eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
Oly_DTW_lm <- lm(data = NPD_oly_outRmd, tissue_dry_weight_g ~ length_mm)

ols_regress(Oly_DTW_lm)
```

### ***Log Transform DTW***
```{r Oly_DTW_SH_out_rmd_Trans, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=6, out.width="50%", fig.cap="The relationship between *O. lurida* shell length and its dry tissue weight (DTW) in Newport Bay, California at the Deanza restoration site. Possible transformations. \\label{figurelabel}"}

### y ~ log(x) model ####
Oly_LogxDTW_lm <- lm(data = NPD_oly_outRmd, tissue_dry_weight_g ~ log(length_mm))
# range of Shell length values
SH_newrange <- data.frame(length_mm = seq(from = 0, to = 53, by = 1))
# create new dataframe with model predicted values from new data range above
pred_logxDTW_SH <- data.frame(DTW_pred = predict(Oly_LogxDTW_lm, newdata = SH_newrange), length_mm = SH_newrange)

# graph with model predicted values to draw line
Oly_SH_logxDTW <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  geom_line(data = pred_logxDTW_SH, aes(x = length_mm, y = DTW_pred)) +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'y ~ log(x)') +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

### log(y) ~ x model ####
Oly_LogDTW_lm <- lm(data = NPD_oly_outRmd, log(tissue_dry_weight_g) ~ length_mm)
pred_logDTW_SH <- data.frame(DTW_pred = exp(predict(Oly_LogDTW_lm, newdata = SH_newrange)), length_mm = SH_newrange)

Oly_shell_DTW_logline <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  geom_line(data = pred_logDTW_SH, aes(x = length_mm, y = DTW_pred)) +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'log(y) ~ x') +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

### log(y) ~ log(x) model ###
Oly_LogDTW_logSH_lm <- lm(data = NPD_oly_outRmd, log(tissue_dry_weight_g) ~ log(length_mm))
pred_loglogDTW_SH <- data.frame(DTW_pred = exp(predict(Oly_LogDTW_logSH_lm, newdata = SH_newrange)), 
                                length_mm = SH_newrange)

Oly_shell_logDTW <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  geom_line(data = pred_loglogDTW_SH, aes(x = length_mm, y = DTW_pred)) +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = ' Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'log(y) ~ log(x)') +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

### Y ~ x + x^2
Oly_DTW2_lm <- lm(data = NPD_oly_outRmd, tissue_dry_weight_g ~ poly(length_mm, degree = 2, raw = T))
SH_newrange <- data.frame(length_mm = seq(from = 2, to = 52, by = 1))
pred_DTW2_SH_df <- data.frame(tissue_dry_weight_g = predict(Oly_DTW2_lm, newdata = SH_newrange), SH_newrange)

Oly_SH_DTW2_graph <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  geom_line(data = pred_DTW2_SH_df, aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Y ~ x + x^2') +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

OlySH_DTW_Trans_graphs <- grid.arrange(Oly_SH_logxDTW, Oly_shell_DTW_logline, 
                                        Oly_shell_logDTW, Oly_SH_DTW2_graph, nrow = 2)

plot(OlySH_DTW_Trans_graphs)

```

```{r eval=FALSE, include=FALSE}
Oly_LogxDTW_lm <- lm(data = NPD_oly_outRmd, tissue_dry_weight_g ~ log(length_mm))
ols_regress(Oly_LogxDTW_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
Oly_LogDTW_lm <- lm(data = NPD_oly_outRmd, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(Oly_LogDTW_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
Oly_LogDTW_logSH_lm <- lm(data = NPD_oly_outRmd, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(Oly_LogDTW_logSH_lm)
```

```{r eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(Oly_LogDTW_logSH_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(Oly_LogDTW_logSH_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(Oly_LogDTW_logSH_lm))
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
Oly_DTW2_lm <- lm(data = NPD_oly_outRmd, tissue_dry_weight_g ~ poly(length_mm, degree = 2, raw = T))
ols_regress(Oly_DTW2_lm)
```

```{r Oly_TWW_DTW, eval=FALSE, fig.height=5, fig.width=6, cache=TRUE, include=FALSE}
Oly_TWW_DTW<- ggplot(NPD_oly, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = 'Total Wet Weight (g)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW x TWW - Newport, CA') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")
plot(Oly_TWW_DTW)
```

```{r Oly_TWW_DTW_outRmd, echo=FALSE, fig.keep = 'all', dev = 'pdf', fig.align="default", fig.asp=0.618, fig.show="hold", fig.width=6, out.width="50%", fig.cap="The relationship between *O. lurida* total wet weight (TWW) and its dry tissue weight (DTW) in Newport Bay, California at the Deanza restoration site. Blue lines represent the relationship found by Gray and Langdon (2018) in Yaquina Bay, Oregon Olympia oysters (DTW = 0.0044*TWW - 0.043) \\label{figurelabel}"}

# Make sure only using positive TWW values, negative values indicate processing error
NPD_oly_TWW <- NPD_oly_outRmd %>% filter(total_wet_weight_g > 0)
# Gray & Langdon 2017 DTW x TWW Olympia model to add to graph
Gray17_DTW_TWW_lm <- function(x) {0.0044*x - 0.043}

# use DTW outlier data to plot graph
Oly_TWW_DTW_rm_out <- ggplot(NPD_oly_TWW, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide=FALSE) +
  stat_function(fun = Gray17_DTW_TWW_lm, colour = "blue") +
  xlim(0, 7) +
  theme_classic() +
  labs(x = 'Total wet weight (g)',
       y = 'Dry Tissue Weight (g)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

### log(y) ~ x
Oly_TWW_DTW_log_LM <- lm(data = NPD_oly_TWW, log(tissue_dry_weight_g) ~ total_wet_weight_g)
TWW_newrange <- data.frame(total_wet_weight_g = seq(from = 0, to = 7, by = 0.01))
pred_DTW_TWW_log_df <- data.frame(tissue_dry_weight_g = exp(predict(Oly_TWW_DTW_log_LM, newdata = TWW_newrange)),
                              TWW_newrange)

Oly_logTWW_DTW_graph <- ggplot(NPD_oly_TWW, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_line(data = pred_DTW_TWW_log_df, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide=FALSE) + 
  stat_function(fun = Gray17_DTW_TWW_lm, colour = "blue") +
  xlim(0, 7) +
  theme_classic() +
  labs(x ="Total wet weight (g)",
       y = 'Dry Tissue Weight (g)')

### log(y) ~ log(x)
Oly_TWW_DTW_loglog_LM <- lm(data = NPD_oly_TWW, log(tissue_dry_weight_g) ~ log(total_wet_weight_g))
pred_DTW_TWW_loglog_df <- data.frame(tissue_dry_weight_g = exp(predict(Oly_TWW_DTW_loglog_LM, newdata = TWW_newrange)),
                              TWW_newrange)

Oly_loglogTWW_DTW_graph <- ggplot(NPD_oly_TWW, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_line(data = pred_DTW_TWW_loglog_df, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide=FALSE) + 
  stat_function(fun = Gray17_DTW_TWW_lm, colour = "blue") +
  xlim(0, 7) +
  theme_classic() +
  labs(x ="Total wet weight (g)",
       y = 'Dry Tissue Weight (g)')

### y ~ x + x^2
Oly_TWW2_DTW_LM <- lm(data = NPD_oly_TWW, 
                        tissue_dry_weight_g ~ poly(total_wet_weight_g, degree = 2, raw = T))
pred_DTW2_TWW_log_df <- data.frame(tissue_dry_weight_g = predict(Oly_TWW2_DTW_LM, newdata = TWW_newrange),
                              TWW_newrange)

Oly_TWW2_DTW_graph <- ggplot(NPD_oly_TWW, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_line(data = pred_DTW2_TWW_log_df, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide=FALSE) + 
  stat_function(fun = Gray17_DTW_TWW_lm, colour = "blue") +
  xlim(0, 7) +
  theme_classic() +
  labs(x ="Total wet weight (g)",
       y = 'Dry Tissue Weight (g)')
       
Oly_TWW_DTW_outRmd_graph <- grid.arrange(Oly_TWW_DTW_rm_out, Oly_logTWW_DTW_graph,
                                          Oly_loglogTWW_DTW_graph, Oly_TWW2_DTW_graph, nrow = 2)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
Oly_TWW_DTW_lm_rm_out <- lm(data = NPD_oly_outRmd,
                         tissue_dry_weight_g ~ total_wet_weight_g)

ols_regress(Oly_TWW_DTW_lm_rm_out)
```

```{r eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
par(mfrow=c(2,2))
plot(Oly_TWW_DTW_lm_rm_out)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(Oly_TWW_DTW_lm_rm_out)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(Oly_TWW_DTW_lm_rm_out))
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
Oly_TWW_DTW_log_LM <- lm(data = NPD_oly_TWW, log(tissue_dry_weight_g) ~ total_wet_weight_g)
ols_regress(Oly_TWW_DTW_log_LM )
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
Oly_TWW_DTW_loglog_LM <- lm(data = NPD_oly_TWW, 
                         log(tissue_dry_weight_g) ~ log(total_wet_weight_g))
ols_regress(Oly_TWW_DTW_loglog_LM)
```

```{r eval=FALSE, fig.height=6, fig.width=6, cache=TRUE, include=FALSE}
Oly_TWW2_DTW_LM <- lm(data = NPD_oly_TWW, 
                        tissue_dry_weight_g ~ poly(total_wet_weight_g, degree = 2, raw = T))
ols_regress(Oly_TWW2_DTW_LM)
```

```{r NPD_Bivalve_SH_DTW, fig.height=6, fig.width=15, cache=TRUE, include=FALSE}
##### Estimate Biomass per site here with equations
NPD_bivalve_biomass_graph <-  NPD_bivalve_data_clean %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g, color = species)) +
  geom_point() +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  facet_wrap(~species) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = "Newport Deanza Bivalve Biomass - Raw data") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

# Remove outlier and negative DTW value
NPD_bivalve_outrmd <- NPD_bivalve_data_clean %>%
  mutate(DTW_outlier = find_outlier(NPD_bivalve_data_clean$tissue_dry_weight_g)) %>% 
  filter(DTW_outlier == FALSE & tissue_dry_weight_g >= 0) 

NPD_bivalve_outrmd_graph <- NPD_bivalve_outrmd %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g, group = species, color = species)) +
  geom_point() +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  facet_wrap(~species) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = "Newport Deanza Bivalve Biomass - Positive DTW only - Outlier Rmd") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

grid.arrange(NPD_bivalve_biomass_graph, NPD_bivalve_outrmd_graph, nrow = 1)
```

### ***NPD Adula***
```{r eval=FALSE, fig.height=5, fig.width=12, cache=TRUE, include=FALSE}
NPD_Adula <- NPD_bivalve_outrmd %>% 
  filter(species %in% c("Adula diegensis"))

NPD_Adula_Posbiomass_graph <- NPD_Adula %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Adula diegensis")," - Positive DTW only"))) +
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

# Predict new values with 

NPD_Adula_Posbiomass_loggraph <- NPD_Adula %>% 
  ggplot(aes(x = log(length_mm), y = log(tissue_dry_weight_g))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Ln Shell length (mm)",
       y = "Ln Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Adula diegensis")," - Positive Ln DTW only"))) +
  theme_classic() +
  stat_poly_eq(aes(label = stat(adj.rr.label)), formula = x_y_formula, 
               parse = TRUE)

grid.arrange(NPD_Adula_Posbiomass_graph, NPD_Adula_Posbiomass_loggraph, nrow = 1)
```

### ***LM - Adula DTW ~ SH***
```{r eval=FALSE, include=FALSE}
NPD_Adula_lm <- lm(data = NPD_Adula, tissue_dry_weight_g ~ length_mm)
ols_regress(NPD_Adula_lm)
```

### ***LM - Adula logDTW ~ SH***
```{r eval=FALSE, include=FALSE}
NPD_Adula_logDTW_lm <- lm(data = NPD_Adula, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(NPD_Adula_logDTW_lm)
```

### ***LM - Adula logDTW ~ logSH***
```{r eval=FALSE, include=FALSE}
NPD_Adula_logDTW_logSH_lm <- lm(data = NPD_Adula, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(NPD_Adula_logDTW_logSH_lm)
```

### ***Y ~ x + x^2 ***
```{r eval=FALSE, include=FALSE}
NPD_Adula_DTW_SH2_lm <- lm(data = NPD_Adula, tissue_dry_weight_g ~ poly(length_mm, degree = 2, raw = T))
ols_regress(NPD_Adula_DTW_SH2_lm)
```

### ***NPD Musculista*** 
```{r eval=FALSE, fig.height=5, fig.width=12, cache=TRUE, include=FALSE}
NPD_Musculista <- NPD_bivalve_outrmd %>% 
  filter(species %in% c("Musculista senhousia"))

NPD_Musculista_Posbiomass_graph <- NPD_Musculista %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Musculista senhousia")," - Positive DTW only"))) +
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

NPD_Musculista_Posbiomass_loggraph <- NPD_Musculista %>% 
  ggplot(aes(x = length_mm, y = log(tissue_dry_weight_g))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Ln Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Musculista senhousia")," - Positive Ln DTW only"))) +
  theme_classic() +
  stat_poly_eq(aes(label = stat(adj.rr.label)), formula = x_y_formula, 
               parse = TRUE)

grid.arrange(NPD_Musculista_Posbiomass_graph, NPD_Musculista_Posbiomass_loggraph, nrow=1)
```

### ***LM - Musculista DTW ~ SH***
```{r eval=FALSE, include=FALSE}
NPD_Musculista_lm <- lm(data = NPD_Musculista, tissue_dry_weight_g ~ length_mm)
ols_regress(NPD_Musculista_lm)
```

### ***LM - Musculista logDTW ~ SH***
```{r eval=FALSE, include=FALSE}
NPD_Musculista_logDTW_lm <- lm(data = NPD_Musculista, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(NPD_Musculista_logDTW_lm)
```

### ***LM - Musculista logDTW ~ logSH***
```{r eval=FALSE, include=FALSE}
NPD_Musculista_logDTW_logSH_lm <- lm(data = NPD_Musculista, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(NPD_Musculista_logDTW_logSH_lm)
```

### ***NPD Mytilus***
```{r eval=FALSE, fig.height=5, fig.width=12, cache=TRUE, include=FALSE}

NPD_Mytilus <- NPD_bivalve_outrmd %>% 
  filter(species %in% c("Mytilus galloprovincialis"))

NPD_Mytilus_Posbiomass_graph <- NPD_Mytilus %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Mytilus galloprovincialis")," - Positive DTW only"))) +
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

NPD_Mytilus_Posbiomass_loggraph <- NPD_Mytilus %>% 
  ggplot(aes(x = length_mm, y = log(tissue_dry_weight_g))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Ln Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Mytilus galloprovincialis")," - Positive Ln DTW only"))) +
  theme_classic() +
  stat_poly_eq(aes(label = stat(adj.rr.label)), formula = x_y_formula, 
               parse = TRUE)

grid.arrange(NPD_Mytilus_Posbiomass_graph, NPD_Mytilus_Posbiomass_loggraph, nrow = 1)
```

### ***LM - Mytilus DTW ~ SH***
```{r eval=FALSE, include=FALSE}
NPD_Mytilus_lm <- lm(data = NPD_Mytilus, tissue_dry_weight_g ~ length_mm)
ols_regress(NPD_Mytilus_lm)
```

### ***LM - Mytilus logDTW ~ SH***
```{r eval=FALSE, include=FALSE}
NPD_Mytilus_logDTW_lm <- lm(data = NPD_Mytilus, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(NPD_Mytilus_logDTW_lm)
```

### ***LM - Mytilus logDTW ~ logSH***
```{r eval=FALSE, include=FALSE}
NPD_Mytilus_logDTW_logSH_lm <- lm(data = NPD_Mytilus, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(NPD_Mytilus_logDTW_logSH_lm)
```

### ***LM - Unknown mussel***
```{r eval=FALSE, fig.height=5, fig.width=12, cache=TRUE, include=FALSE}
NPD_Unknown <- NPD_bivalve_outrmd %>% 
  filter(species %in% c("Unknown mussel"))

NPD_Unknown_Posbiomass_graph <- NPD_Unknown %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Unknown mussel")," - Positive DTW only"))) +
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

NPD_Unknown_Posbiomass_loggraph <- NPD_Unknown %>% 
  ggplot(aes(x = length_mm, y = log(tissue_dry_weight_g))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Ln Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Unknown mussel")," - Positive Ln DTW only"))) +
  theme_classic()  +
  stat_poly_eq(aes(label = stat(adj.rr.label)), formula = x_y_formula, 
               parse = TRUE)

grid.arrange(NPD_Unknown_Posbiomass_graph, NPD_Unknown_Posbiomass_loggraph, nrow =1)

```

### ***LM - Unknown mussel DTW ~ SH***
```{r eval=FALSE, include=FALSE}
NPD_Unknown_lm <- lm(data = NPD_Unknown, tissue_dry_weight_g ~ length_mm)
ols_regress(NPD_Unknown_lm)
```

### ***LM - Unknown mussel logDTW ~ SH***
```{r eval=FALSE, include=FALSE}
NPD_Unknown_logDTW_lm <- lm(data = NPD_Unknown, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(NPD_Unknown_logDTW_lm)
```

### ***LM - Unknown mussel logDTW ~ logSH***
```{r eval=FALSE, include=FALSE}
NPD_Unknown_logDTW_logSH_lm <- lm(data = NPD_Unknown, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(NPD_Unknown_logDTW_logSH_lm)
```

### ***Biomass estimate - Remove outliers***
```{r Newport_Bivalve_biomass_outlier, eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
# remove outliers from data
NPD_Posbiomass_outlier <- NPD_Posbiomass_data %>% 
  mutate(DTW_outlier = find_outlier(NPD_Posbiomass_data$tissue_dry_weight_g)) %>% 
  filter(DTW_outlier == FALSE)

NPD_Posbiomass_outlierrmd_graph <- NPD_Posbiomass_outlier %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g, color = species)) +
  geom_smooth(method = lm) +
  geom_point() +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  facet_wrap(~species) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = "Newport Deanza Bivalve Biomass",
       subtitle = "Positive DTW, outliers removed") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic")) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_Posbiomass_outlierrmd_graph
```

### ***NPD Bivalve Biomass***
```{r eval=FALSE, include=FALSE}
Bivalve_Biomass_graph <- ggplot(NPD_Posbiomass_outlier, aes(Site)) + 
  geom_col(aes(x = Site, y = tissue_dry_weight_g, fill = species)) +
  theme_classic() +
  scale_fill_manual(values = Species_colors) +
  #scale_y_continuous(breaks = seq(0, max(NPD_Posbiomass_outlier$tissue_dry_weight_g), by = 500)) +
  labs(y = "Dry Tissue Weight (g)")

Bivalve_Biomass_graph
# Order species by DTW not alphabetical order
```


Density & Biomass

### ***Bivalve Density***
```{r Bivalve_Density, eval=FALSE, fig.height=6, fig.width=8, cache=TRUE, include=FALSE}
# read in bivalve density data from cleaned data file
Bivalve_Den_data <- fread(file.path(Bivalve_output_directory, "Bivalve_Density_summary.csv"))

# replace NAs with 0s
Bivalve_Den_data[is.na(Bivalve_Den_data)] <- 0

Bivalve_Den_data <- Bivalve_Den_data %>% 
  # move species from individual columns to a single column with new density column to contain data
  pivot_longer(c(Adula_diegensis_m2, Musculista_senhousia_m2, Mytilus_galloprovincialis_m2,
                 Ostrea_lurida_m2, Crassostrea_gigas_m2, Argopecten_ventricosa_m2, 
                 Geukensia_demissa_m2, Crassostrea_gigas_m2), 
               names_to = "Species", 
               values_to =  "individuals_m2") %>% 
  # remove "_m2" from species names in Species column
  mutate(Species = str_replace(Species, "_m2", ""),
         Species = str_replace(Species, "_", " "))

#Reorder levels of Site factor - display North to South
order_by_site <- c("San Rafael", "Morro Bay", "Shellmaker", "Deanza") 
Bivalve_Den_data <- arrange(transform(Bivalve_Den_data, Site = factor(Site,levels = order_by_site)), Site)


#unique(Bivalve_Den_data$Species) # list each individual bivalve species
# Assign species to specific color
Species_colors <- c("Adula diegensis" = "#8D8680",
                    "Argopecten ventricosa" = "#CCC3C5",
                    "Crassostrea gigas" = "#6D6340",
                    "Geukensia demissa" = "#524D4F",
                    "Musculista senhousia" = "#B0915B",
                    "Mytilus galloprovincialis" = "#7E4B41",
                    "Ostrea lurida" = "#9986A5",
                    "Unknown mussel" = "black")

# Stacked bar graph
Bivalve_Den_graph <- ggplot(Bivalve_Den_data, aes(Site)) + 
  geom_col(aes(x = Site, y = individuals_m2, fill = Species)) +
  geom_text(aes(label = round(Bivalve_den_m2,0), y = Bivalve_den_m2), 
            vjust = -0.5) +
  theme_classic() +
  scale_fill_manual(values = Species_colors) +
  scale_y_continuous(breaks = seq(0, max(Bivalve_Den_data$Bivalve_den_m2), by = 500)) +
  labs(y = expression("Individuals per m"^2))
  
Bivalve_Den_graph
```

Up & Down

### ***Facet Plots***
```{r Bar_Graphs_up_vs_down, eval=FALSE, cache=TRUE, include=FALSE}
Bar_up_down_data <- Master_analysis_table %>%
 # select(Experiment, Date, Site, Chl_ug_L_Up, Chl_ug_L_Down) %>%
  rename(Upstream = Chl_ug_L_Up, Downstream = Chl_ug_L_Down) %>%  
  gather(Upstream, Downstream, key = Position, value = Chl_ug_L) %>% 
  mutate(Position = fct_relevel(Position, 'Upstream', 'Downstream')) %>% 
  mutate(Site = fct_relevel(Site, 'Deanza', 'Shellmaker', 'San Rafael', 'Morro Bay')) %>% 
  mutate(Site_exp_date = paste(Site, Experiment, Date, sep = ' ')) %>% 
  mutate(Exp_Date = paste(Experiment, Date, sep = ' ')) %>% 
  arrange(Site, mdy(Date))

#Bar_up_down_data$Position <- as.factor(Bar_up_down_data$Position)

Paired_bar_chl_graph <- ggplot(data = Bar_up_down_data, aes(x = Site_exp_date, y = Chl_ug_L, fill = Position)) +
    geom_bar(stat="identity", position = "dodge") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    facet_grid(~ Site, scales = "free", space = "free") + #'free' allows axis b/w sites uneaven
    geom_bar(data = (Bar_up_down_data %>%
                       filter(!Experiment %in% c('Filtration'))),
             color = "grey22",
             stat="identity",
             position = "dodge") +
    labs(x = 'Experiment', y = 'Chlorophyl (ug/L)')

plot(Paired_bar_chl_graph)
```

### ***Graphs using grid.arrange()***
```{r Bar_Graphs_up_vs_down_grid.arrange, eval=FALSE, cache=TRUE, include=FALSE}
############## Try 2 ####### make separate graphs, combine using grid.arrange()

##### Can't figure out how to properly label x axis. Works with Exp_Date, but can't shorten without messing up data:label pairs. Can't spend more time on this right now. come back if time -AM 2020_3_3

NPD_bar_data <- Bar_up_down_data %>% 
  filter(Site == "Deanza") %>% 
  mutate(graph_Label = ifelse(grepl("^Filtration", Exp_Date), str_replace(Exp_Date, "Filtration ", ""),
                             str_replace(Exp_Date, "^Neg Control .", "")))

NPD_bar_graph <- ggplot(data = NPD_bar_data, aes(x = Exp_Date, y = Chl_ug_L, 
                                                 fill = Position)) +
    geom_col(position = position_dodge(width = 0.9, preserve = "single")) +
    geom_col(data = (NPD_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.x = element_blank(),
          legend.position = c(0.9, 0.8),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(y = 'Chlorophyll a (ug/L)', title = "Newport Deanza") +
  # This labels the x-axis
    #scale_x_discrete(labels = Exp_Date) +
    ylim(0, 8)

NPSM_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'Shellmaker')

NPSM_bar_graph <- ggplot(data = NPSM_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (NPSM_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "Newport Shellmaker") +
    # scale_x_discrete(labels = NPSM_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE) 

MB_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'Morro Bay')

MB_bar_graph <- ggplot(data = MB_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (MB_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "Morro Bay") +
   # scale_x_discrete(labels = MB_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE)

SR_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'San Rafael')

SR_bar_graph <- ggplot(data = SR_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (SR_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "San Rafael") +
    #scale_x_discrete(labels = SR_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE)

Chl_graphs <- list(NPD_bar_graph, NPSM_bar_graph, SR_bar_graph, MB_bar_graph) 
all_chl_graphs <- grid.arrange(grobs = Chl_graphs,
             widths = c(1,1,1,1,1,1,1,1,1,1,1,1,1,1),
             layout_matrix = rbind(c(NA,1,1,1,1,1,1,1,1,1,1,1,1, NA),
                                   c(2,2,2,2,2,3,3,3,3,3,4,4,4,4)))
plot(all_chl_graphs)
#ggsave("Insitu_Filter_up_vs_down_all_sites.png", all_chl_graphs)
```


Table

```{r Final_Summary_table, eval=FALSE, fig.height=5, fig.width=6, cache=TRUE, include=FALSE}
# Organize & clean summary table data
Final_table <- Master_analysis_table %>% 
    mutate(Date = mdy(Date),
         Temp_C_Up = round(Temp_C_Up, digits = 2),
         Sal_ppt_Up = round(Sal_ppt_Up, digits = 1),
         Turbidity_NTU_Up = round(Turbidity_NTU_Up, digits = 1),
         Avg_TPM = round(Avg_TPM, digits = 4),
         Avg_OC_Ratio = round(Avg_OC_Ratio, digits = 4),
         Chl_ug_L_Up = round(Chl_ug_L_Up, digits = 1),
         Chl_ug_L_Down = round(Chl_ug_L_Down, digits = 1),
         avg_depth_m = avg_depth_cm*100,
         avg_m_hr = round(avg_m_hr, digits = 0),
         pcnt_Chl_rmvd = round(pcnt_Chl_rmvd, digits = 1),
         L_hr_m2 = round(L_hr_m2, digits = 0)) %>% 
  dplyr::select(Site, Date, Experiment, Temp_C_Up, Sal_ppt_Up, Turbidity_NTU_Up, Avg_TPM, 
          Avg_OC_Ratio, Chl_ug_L_Up, Chl_ug_L_Down, avg_depth_cm, d_bw_sondes_m, avg_m_hr, 
          pcnt_Chl_rmvd, L_hr_m2) %>% 
  arrange(site_by_lat, desc(Date))
# Make date formated as character to display properly
Final_table$Date <- as.character(Final_table$Date)

# create xtable
sumtable_side_LaTex <- xtable(Final_table, caption = "Summary Table of all field days")
# print LaTex code for sideways table
print(sumtable_side_LaTex, floating = TRUE, floating.environment = "sidewaystable")
  
```

```{r T_test_table, eval=FALSE, fig.height=5, fig.width=6, cache=TRUE, include=FALSE}

T_test_Table <- Master_analysis_table %>%
  mutate(Date = mdy(Date),
         pcnt_Chl_rmvd = round(pcnt_Chl_rmvd, digits = 1),
         Mean_Chl_diff = round(Mean_Chl_diff, digits = 2),
         StDev_Chl_diff = round(StDev_Chl_diff, digits = 2),
         StEr_Chl_diff = round(StEr_Chl_diff, digits = 2),
         statistic = round(statistic, digits = 2), # t-statistic 
         p.value = round(p.value, digits = 2),
         parameter = round(parameter, digits = 2),
         conf.low = round(conf.low, digits = 2)) %>% 
  dplyr::select(Site, Date, Experiment, pcnt_Chl_rmvd, Mean_Chl_diff, StDev_Chl_diff, StEr_Chl_diff,
                statistic, p.value, parameter, conf.low) %>% 
  group_by(Site) %>% 
  arrange(Date, .by_group = T)
# Make date formated as character to display properly
T_test_Table$Date <- as.character(T_test_Table$Date)

```

MLR

### ***Chl Rmd Filtration Forward Stepwise Selection***
```{r LM_PrctChl_pos_add, fig.height=5, fig.width=6, cache=TRUE, include=FALSE}
# Positive Percent Chl removed trials only
MLR_PrctChl_fwd <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~
                         # Field notes Qualitative variables
                         #Wind + G_upstream + Algae + #Daylight +  Sonde_fell + Boat_wake +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + #Turbidity_NTU_Up + 
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)

summary(MLR_PrctChl_fwd)
```

### ***Positive Filtration ~ ChlRmd Multiple Regression with selected variables***
```{r fig.height=5, fig.width=6, cache=TRUE, include=FALSE}
LM2_PrctChl_pos_add <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ 
                          NPSM + Avg_OC_Ratio)

summary(LM2_PrctChl_pos_add)
# diagnosis of colinearity
#ols_coll_diag(LM_PrctChl_pos_add)
```

### ***Positive Filtration ~ ChlRmd Multiple Regression with selected variables***
```{r fig.height=10, fig.width=6, cache=TRUE, include=FALSE}
# detailed multiple regression summary - ANOVA results
ols_regress(LM2_PrctChl_pos_add)
```

### ***FR - Positive Filtration Stepwise Multiple Regression***
```{r LM_FR_pos, cache=TRUE, include=FALSE}

# Positive Percent Chl removed trials only
LM_FR_pos <- lm(data = Filtration_pos_data, L_hr_m2 ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + # Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)

ols_step_both_p(LM_FR_pos)
```

### ***Chl Rmd - Deanza - Positive Filtration***
```{r LM_ChlRmd_NPD_PosFilter, eval=FALSE, cache=TRUE, include=FALSE}
LM_ChlRmd_NPD_PosFilter <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + # Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)
# not enough degrees of freedom for full model
ols_step_both_p(LM_ChlRmd_NPD_PosFilter)
```

### ***FR - Deanza - Positive Filtration***
```{r LM_FR_NPD_Posfilter, eval=FALSE, cache=TRUE, include=FALSE}
LM_FR_NPD_Posfilter <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + #Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)
# not enough degrees of freedom for full model
ols_step_both_p(LM_FR_NPD_Posfilter)
```
