---
title: "In situ Filtration Analysis Models & Graphs"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: yeti
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
################### Packages ###########################
library(dplyr)
library(tidyr)
library(data.table)
library(magrittr)
library(lubridate) # dealing with time and dates
library(ggplot2)
library(ggthemes) # theme_classic() for graphs
library(stringr)
library(hms)
library(viridisLite)
library(forcats)
library(gridExtra)
library(ggpmisc) # package for adding line equation and R^2 to plots
library(viridis) # Color palette - Options: magma , inferno, plasma, viridis, cividis
library(scales)
library(cowplot) # for arranging multiple plots into a single figure
library(wesanderson)
library(olsrr) # ols_step_backward_p() "builds regression model from a set of candidate predictor variables" 
# replaces ols_step_backward()
library(MASS) # collection of datasets and functions
library(ISLR) # Dataset in Intro to statistical learning

# source functions 
source("functions.R")
# define output directory
output_directory = "./output"
# create output directories (same as Insitu_Filtraiton_Analysis_script.Rmd)
createOutputDirectories()

##################### Read in Data from  project output ##########################
Master_analysis_table <- fread(file.path('./output/4_Filtration_Calculations/Filtration_Summary', "Master_Filtration_analysis_table.csv"))
Avg_TPM_summary_table <- fread(file.path('./output/5_TPM_OC_Summary', "Avg_TPM_summary_table.csv"))
Density_directory = "./Data/bivalve_density_community"
NPD_density = fread(file.path(Density_directory, "Insitu_Filter_NPD_bivalve_biomass_data.csv"))

##################### Data #########################################
# Remove San Diego filtration trial - not applicable to this analysis - different experimental set up
Master_analysis_table <- Master_analysis_table %>% 
  filter(!Site %in% c("San Diego"))

# Order Sites by Latitude
site_by_lat <- c("San Rafael", "Morro Bay", "Shellmaker", "Deanza") 

# transform Site variable to factor and arange by Latitude
Master_analysis_table <- arrange(transform(Master_analysis_table, Site = factor(Site,levels = site_by_lat)), Site)

 # Filtration trials only - exclude Negative controls
Filtration_only_data <- Master_analysis_table %>% 
  filter(Experiment %in% c("Filtration"))

# Filtration trials only - exclude Negative controls & Percent Chl removed greater than 0
### Important Note ## When Percent Chl removed is positive, so is L/hr/m^2 and vice visa. 
# Filtering by pcnt_Chl_rmvd effectively filters both values the same, so further analysis 
# withFiltration_pos_data serves both purposes. 
Filtration_pos_data <- Filtration_only_data %>% 
  filter(pcnt_Chl_rmvd > 0)

# Deanza data only - all trials
Deanza_data_all <- Master_analysis_table %>% 
  filter(Site %in% c("Deanza"))
# Deanza only - Filtraiton trials only
Deanza_Filter_data <- Deanza_data_all %>% 
  filter(Experiment %in% c("Filtration"))
# Deanza only- Positive Filtration only
Deanza_PosFilter_data <- Deanza_Filter_data %>% 
  filter(pcnt_Chl_rmvd > 0)

### Average TPM Data ######################
Avg_TPM_summary_table <- arrange(transform(Avg_TPM_summary_table, Site = factor(Site, levels = site_by_lat)), Site)

############### model formulas ###############
# linear model formula
x_y_formula <- y ~ x 
# Quadratic model
x2_y_formula <- y ~ poly(x, degree = 2)
# Exponential model
logy_x_formula <- log(y) ~ x
# logx
y_logx_fomula <- y ~ log(x)
# double log
logy_logx_formula <- log(y) ~ log(x)

############### Site Color Assignments ###############
viridis(4)
Site_colors <- c("San Rafael" = "#440154FF",
                 "Morro Bay" = "#31688EFF",
                 "Shellmaker" = "#35B779FF",
                 "Deanza" = "#FDE725FF")

############### Bivalve Species Color Assignments ###############
# wes_palettes # lists all current palattes 
# Color palette for Species - Royal2, Darjeeling2, Cavalcanti1, BottleRocket2, IsleofDogs1
density_palette <- rev(wes_palette("IsleofDogs1", 7, type = c("continuous")))
Species_colors <- c("Adula diegensis" = "#8D8680",
                    "Argopecten ventricosa" = "#CCC3C5",
                    "Crassostrea gigas" = "#6D6340",
                    "Geukensia demissa" = "#524D4F",
                    "Musculista senhousia" = "#B0915B",
                    "Mytilus galloprovincialis" = "#7E4B41",
                    "Ostrea lurida" = "#9986A5",
                    "Unknown mussel" = "black")

################# Labels for graphs  #########################
Hab_FR_Label <- expression('Habitat Filtration Rate (L/hr/m'^2*')')
Prt_Chl_Label <- expression(paste('Percent Chlorophyll ', alpha, ' Removed'))
Chl_ugL_Label <- expression(paste("Chlorophyll ", alpha, " (", mu, "g/L) "))
TPM_Label <- expression(paste('Total Particulate Matter (', mu,"g/L)"))
PIM_Label <- expression(paste('Particulate Inorganic Matter (', mu,"g/L)"))

###################### Functions ####################################
# function for number of samples - display on graph
n_mean_stats <- function(x){
  return(tibble(y = max(x) * 0.95, 
                    label = paste("n = ",length(x), "\n",
                                  'mean =', round(mean(x), 1), '\n')
                )
         )
}
# function for number of samples - 3 decimal places
n_mean_stats3 <- function(x){
  return(tibble(y = max(x) * 0.95, 
                    label = paste("n = ",length(x), "\n",
                                  'mean =', round(mean(x), 3), '\n')
                )
         )
}

# function to calculate average, standard deviation, outlier data. 
find_outlier <- function(data){
  average <- mean(data)
  stdev <- sd(data)
  # Outlier data defined by outside 2.2 standard deviations from the mean 
  outlier <- ifelse((data < (average - 2.2 * stdev) | (data > (average + 2.2 * stdev))),
         TRUE, FALSE)
}
```

Filtration Ranges
=====================================

### ***Filtration by site (Filtration Trials only)***
```{r FR_ChlRmd_Filter, fig.height=5, fig.width=14, cache=TRUE}
# Filtration_only_data defined in setup

FR_box <- ggplot((Filtration_only_data), aes(Site, L_hr_m2)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Hab_FR_Label)

Chl_Rmd_box <- ggplot(Filtration_only_data, aes(Site, pcnt_Chl_rmvd)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Prt_Chl_Label)

grid.arrange(FR_box, Chl_Rmd_box, nrow = 1)

```

### ***Filtration by site (Positive values only)*** 
```{r FR_ChlRmd_TPM_posFilter, fig.height=5, fig.width=14, cache=TRUE}
# Filtration_pos_data defined in setup

FR_TPM_box_pos <- ggplot((Filtration_pos_data), aes(Site, L_hr_m2)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Hab_FR_Label,
       title = 'Positive L/hr/m^2 only')

Chl_Rmd_box_pos <- ggplot((Filtration_pos_data), aes(Site, pcnt_Chl_rmvd)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Prt_Chl_Label,
       title = 'Positive % Chl Rmd only')

grid.arrange(FR_TPM_box_pos, Chl_Rmd_box_pos, nrow = 1)
```

TPM
=====================================

### ***Filtration vs TPM (Positive Filtration Trials only)***
```{r , fig.height=5, fig.width=14, cache=TRUE}
FRPos_TPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label,
       title = 'Pos Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_RmdPos_TPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FRPos_TPM_graph, Chl_RmdPos_TPM_graph, nrow = 1)
```

### ***FR Pos ~ TPM Linear Model***
```{r, fig.height=6, fig.width=6, cache=TRUE}
FRPos_TPM_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Avg_TPM)
#summary(FR_TPM_lm)
ols_regress(FRPos_TPM_lm)
```

> Not significant

### ***ChlRmd Y ~ X Linear Model***
```{r, fig.height=6, fig.width=6, cache=TRUE}
ChlRmdPos_TPM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Avg_TPM)
#summary(ChlRmdPos_TPM_lm)
ols_regress(ChlRmdPos_TPM_lm)
```

> Not significant predictor

### ***ChlRmd Y ~ X Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_TPM_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_TPM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_TPM_lm)
```

### ***ChlRmd vs TPM Transformations***
```{r , fig.height=10, fig.width=12, cache=TRUE}
Chl_RmdPos_TPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

# log-log model predicitons
logChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_TPM))
# create range of Salinity values to predict with model
TPM_newrange <- data.frame(Avg_TPM = seq(from = 0, to = 0.04, by = 0.001))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
loglogTPM_Pred <- data.frame(pred_ChlRmd = exp(predict(logChlRmdPos_logTPM_lm, newdata = TPM_newrange)))
pred_loglog_TPM_df <- data.frame(TPM_newrange, loglogTPM_Pred)
  

logChlRmdPos_logTPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglog_TPM_df, aes(x = Avg_TPM, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'log(Y) ~ log(X)') +
  guides(fill = FALSE)

# Y-log model predicitons
ChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Avg_TPM))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
logTPM_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_logTPM_lm, newdata = TPM_newrange))
pred_logTPM_df <- data.frame(TPM_newrange, logTPM_Pred)

ChlRmdPos_logTPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_line(data = pred_logTPM_df, aes(x = Avg_TPM, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'Y ~ log(X)') +
  guides(fill = FALSE)

# Y~x + x^2 model predicitons
ChlRmdPos_TPM2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Avg_TPM, degree = 2, raw = T))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
TPM2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_TPM2_lm, newdata = TPM_newrange))
pred_TPM2_df <- data.frame(TPM_newrange, TPM2_Pred)

ChlRmdPos_TPM2_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_line(data = pred_TPM2_df, aes(x = Avg_TPM, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'Y ~ x + x^2') +
  guides(fill = FALSE) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x2_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")

grid.arrange(Chl_RmdPos_TPM_graph, logChlRmdPos_logTPM_graph, 
             ChlRmdPos_logTPM_graph, ChlRmdPos_TPM2_graph, nrow = 2)
```

### ***Log ~ Log Linear Model***
```{r, fig.height=6, fig.width=6, cache=TRUE}
logChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_TPM))
#summary(ChlRmdPos_TPM_lm)
ols_regress(logChlRmdPos_logTPM_lm)
```

> Not huge difference between regular and log transformed.

### ***Log ~ Log Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(logChlRmdPos_logTPM_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(logChlRmdPos_logTPM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(logChlRmdPos_logTPM_lm)
```

### ***Y ~ log(x)***
```{r, fig.height=6, fig.width=6, cache=TRUE}
ChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Avg_TPM))
#summary(ChlRmdPos_logTPM_lm)
ols_regress(ChlRmdPos_logTPM_lm)
```

### ***Y ~ x + x^2***
```{r, fig.height=6, fig.width=6, cache=TRUE}
ChlRmdPos_TPM2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Avg_TPM, degree = 2, raw = T))
#summary(ChlRmdPos_TPM_lm)
ols_regress(ChlRmdPos_TPM2_lm)
```

> x^2 almost significant predictory p-value: 0.08

### ***Y ~ x + x^2 Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_TPM2_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(logChlRmdPos_logTPM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(logChlRmdPos_logTPM_lm)
```

### ***Deanza only Positive Filtration vs TPM***
```{r NPD_FRPos_TPM_graph, fig.height=5, fig.width=12, cache=TRUE}
NPD_FRPos_TPM_graph <- ggplot((Deanza_PosFilter_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  # geom_abline(aes(intercept=0, slope=1)) +
  #scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_TPM_graph <- ggplot((Deanza_PosFilter_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  # geom_abline(aes(intercept=0, slope=1)) +
  #scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(NPD_FRPos_TPM_graph, NPD_ChlRmdPos_TPM_graph, nrow = 1)
```

### ***Deanza Positive Filter - FR ~ TPM***
```{r, fig.height=6, fig.width=6, cache=T}
NPD_PosFR_TPM_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Avg_TPM)
ols_regress(NPD_PosFR_TPM_lm)
```

> Not significant predictor

### ***Deanza Postive Filter - ChlRmd ~ TPM***
```{r, fig.height=6, fig.width=6, cache=T}
NPD_PosChlRmd_TPM_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Avg_TPM)
ols_regress(NPD_PosChlRmd_TPM_lm)
```

> Did not do further transformations, didn't look like obvious pattern to investigate

### ***Y ~ X Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(NPD_PosChlRmd_TPM_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(NPD_PosChlRmd_TPM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(NPD_PosChlRmd_TPM_lm)
```

PIM
=====================================

### ***Filter Positive vs PIM***
```{r FRPos vs PIM, fig.height=5, fig.width=14, cache=TRUE}
FRPos_PIM_graph <- ggplot(Filtration_pos_data, aes(Avg_PIM, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = PIM_Label,
       y = Hab_FR_Label,
       title = 'Positive Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_RmdPos_PIM_graph <- ggplot(Filtration_pos_data, aes(Avg_PIM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = PIM_Label,
       y = Prt_Chl_Label,
       title = 'Positive Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FRPos_PIM_graph, Chl_RmdPos_PIM_graph, nrow = 1)
```

### ***FR Pos ~ PIM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_PIM_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Avg_PIM)
ols_regress(FRPos_PIM_lm)
```

> Not significant

### ***ChlRmd Pos ~ PIM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_PIM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Avg_PIM)
ols_regress(ChlRmdPos_PIM_lm)
```

> Not significant

### ***Y ~ X Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_PIM_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_PIM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_PIM_lm)
```

### ***Deanza FR Positive ~ PIM***
```{r Deanza_Filter_Pos_PIM, fig.height=5, fig.width=12, cache=TRUE}
NPD_FRPos_PIM_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_PIM, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = PIM_Label,
       y = Hab_FR_Label,
       title = 'Deanza Positive Filtration') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_PIM_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_PIM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = PIM_Label,
       y = Prt_Chl_Label,
       title = 'Deanza Positive Filtration') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(NPD_FRPos_PIM_graph, NPD_ChlRmdPos_PIM_graph, nrow = 1)
```

### ***NPD FRPos ~ PIM LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FRpos_PIM_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Avg_PIM)
ols_regress(NPD_FRpos_PIM_lm)
```

> Not significant

### ***NPD ChlRmdPos ~ PIM LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdpos_PIM_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Avg_PIM)
ols_regress(NPD_ChlRmdpos_PIM_lm)
```

> Significant p-value: 0.045

### ***Y ~ X Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(NPD_ChlRmdpos_PIM_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(NPD_ChlRmdpos_PIM_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(NPD_ChlRmdpos_PIM_lm)
```

OC 
=====================================

### ***Filter Positive vs OC***
```{r FRPos vs OC, fig.height=5, fig.width=14, cache=TRUE}
FRPos_OC_graph <- ggplot(Filtration_pos_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_RmdPos_OC_graph <- ggplot(Filtration_pos_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FRPos_OC_graph, Chl_RmdPos_OC_graph, nrow = 1)
```

### ***FR Pos by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_OC_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Avg_OC_Ratio)
ols_regress(FRPos_OC_lm)
```

> Not significant predictor 

### ***ChlRmd Pos by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_OC_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Avg_OC_Ratio)
ols_regress(ChlRmdPos_OC_lm)
```

> Significant Avg_OC_Ratio p-value: 0.040

### ***Y ~ X Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_OC_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_OC_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_OC_lm)
```

### ***Transformations - Positive ChlRmd vs OC***
```{r LogChlRmdPos_OC, fig.height=5, fig.width=6, cache=TRUE}
logChl_RmdPos_logOC_graph <- ggplot(Filtration_pos_data, 
                                    aes(log(Avg_OC_Ratio), log(pcnt_Chl_rmvd))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = expression(paste(log[n],' Organic Content of Seston (fraction)')),
       y = expression(paste(log[n], " Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Filtration Trials') +
  guides(fill = FALSE)

# log-log model predicitons
logChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_OC_Ratio))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
OC_newrange <- data.frame(Avg_OC_Ratio = seq(from = 0.6, to = 1, by = 0.025))
loglogOC_Pred <- data.frame(pred_ChlRmd = exp(predict(logChlRmdPos_logOC_lm, newdata = OC_newrange)))
pred_loglogOC_df <- data.frame(OC_newrange, loglogOC_Pred)

ChlRmdPos_loglogOC_graph <- ggplot((Filtration_pos_data), aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglogOC_df, aes(x = Avg_OC_Ratio, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'log(y) ~ log(x)') +
  guides(fill = FALSE)

# Y-log model predicitons
ChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Avg_OC_Ratio))
logOC_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_logOC_lm, newdata = OC_newrange))
pred_logOC_df <- data.frame(OC_newrange, logOC_Pred)

ChlRmdPos_logOC_graph <- ggplot((Filtration_pos_data), aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_line(data = pred_logOC_df, aes(x = Avg_OC_Ratio, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'y ~ log(x)') +
  guides(fill = FALSE)

# Y-x + x^2 model predicitons
ChlRmdPos_OC2_lm <- lm(data = Filtration_pos_data, 
                         pcnt_Chl_rmvd ~ poly(Avg_OC_Ratio, degree = 2, raw = T))
OC2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_OC2_lm, newdata = OC_newrange))
pred_OC2_df <- data.frame(OC_newrange, OC2_Pred)

ChlRmdPos_OC2_graph <- ggplot((Filtration_pos_data), aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_line(data = pred_OC2_df, aes(x = Avg_OC_Ratio, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials',
       subtitle = 'y ~ x + x^2') +
  guides(fill = FALSE)

grid.arrange(logChl_RmdPos_logOC_graph, ChlRmdPos_loglogOC_graph,
             ChlRmdPos_logOC_graph, ChlRmdPos_OC2_graph, nrow = 2)

```

### ***logChlRmd Pos ~ logOC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_OC_Ratio))
ols_regress(logChlRmdPos_logOC_lm)
```

> Not a big difference between regular and log transformed model. p-value: 0.046

### ***ChlRmd Pos ~ logOC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Avg_OC_Ratio))
ols_regress(ChlRmdPos_logOC_lm)
```

> Y ~ X model better rthan logY ~logX p-value: 0.041

### ***ChlRmd Pos ~ OC^2 Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_OC2_lm <- lm(data = Filtration_pos_data, 
                       pcnt_Chl_rmvd ~ poly(Avg_OC_Ratio, degree = 2, raw = T))
ols_regress(ChlRmdPos_OC2_lm)
```

> Y ~ x + x^2 p-value: 0.87

### ***Deanza FR Positive ~ OC***
```{r Deanza_Filter_Pos_OC, fig.height=5, fig.width=12, cache=TRUE}
FRPos_OC_NPD_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'Newport Deanza Positive Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_RmdPos_OC_NPD_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'Newport Deanza Positive Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FRPos_OC_NPD_graph, Chl_RmdPos_OC_NPD_graph, nrow = 1)
```

### ***Deanza FR Positive by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_OC_NPD_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Avg_OC_Ratio)
ols_regress(FRPos_OC_NPD_lm)
```

> Not significant

### ***Deanza ChlRmd Positive by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_OC_NPD_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Avg_OC_Ratio)
ols_regress(ChlRmdPos_OC_NPD_lm)
```

> Not significant. p-value: 0.112

### ***Y ~ X Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_OC_NPD_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_OC_NPD_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_OC_NPD_lm)
```

### ***Log Deanza ChlRmd Positive by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_logOC_NPD_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Avg_OC_Ratio))
ols_regress(ChlRmdPos_logOC_NPD_lm)
```

> Only slight improvement by log(OC). p-value: 0.106

### ***ANOVA b/w regular and log(x) models***
```{r}
anova(ChlRmdPos_OC_NPD_lm, ChlRmdPos_logOC_NPD_lm)
```

> Not significant difference between models

### ***Log Deanza ChlRmd Positive by logOC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logChlRmdPos_logOC_NPD_lm <- lm(data = Deanza_PosFilter_data, log(pcnt_Chl_rmvd) ~ log(Avg_OC_Ratio))
ols_regress(logChlRmdPos_logOC_NPD_lm)
```

> worse model than single x-axis transformation. p-value: 0.156 

Temperature
=====================================

### ***Temperature***
```{r Filter_Temp, fig.height=5, fig.width=14, cache=TRUE, echo=FALSE}

FR_pos_Temp <- ggplot(Filtration_pos_data, aes(Temp_C_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Temp <- ggplot(Filtration_pos_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'Positive ChlRmd') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_pos_Temp, Chl_Rmd_pos_Temp, nrow = 1)
```

### ***FR Positive ~ Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_temp_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(FRPos_temp_lm)
```

> Not significant

### ***ChlRmd Positive ~ Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_temp_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(ChlRmdPos_temp_lm)
```

> Not significant

### ***ChlRmd Pos ~ Temp Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_temp_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_temp_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_temp_lm))
```

### ***Deanza Filtration - Temperature***
```{r NPD_Filter_Temp, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}

NPD_Chl_RmdPos_Temp <- ggplot(Deanza_PosFilter_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'Deanza Positive Filter Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

# Predict Y ~ log(x) model
NPD_ChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Temp_C_Up))
Temp_newrange <- data.frame(Temp_C_Up = seq(from = 18, to = 21, by = 0.25))
Templog_Pred <- data.frame(pred_ChlRmd = predict(NPD_ChlRmdPos_logtemp_lm, newdata = Temp_newrange))
pred_Templog_df <- data.frame(Temp_newrange, Templog_Pred)

NPD_ChlRmdPos_logTemp_graph <- ggplot((Deanza_PosFilter_data), aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Templog_df, aes(x = Temp_C_Up, y = pred_ChlRmd)) +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'NPD Pos Filtration Trials',
       subtitle = 'y ~ log(x)') +
  guides(fill = FALSE)

# Predict log(Y) ~ log(x) model
NPD_logChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, log(pcnt_Chl_rmvd) ~ log(Temp_C_Up))
Temploglog_Pred <- data.frame(pred_ChlRmd = exp(predict(NPD_logChlRmdPos_logtemp_lm, newdata = Temp_newrange)))
pred_Temploglog_df <- data.frame(Temp_newrange, Temploglog_Pred)

NPD_ChlRmdPos_loglogTemp_graph <- ggplot((Deanza_PosFilter_data), aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Temploglog_df, aes(x = Temp_C_Up, y = pred_ChlRmd)) +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'NPD Pos Filtration Trials',
       subtitle = 'log(y) ~ log(x)') +
  guides(fill = FALSE)

# Predict Y ~ x + x^2 model
NPD_ChlRmdPos_temp2_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ poly(Temp_C_Up, degree = 2, raw = T))
Temp2_Pred <- data.frame(pred_ChlRmd = predict(NPD_ChlRmdPos_temp2_lm, newdata = Temp_newrange))
pred_Temp2_df <- data.frame(Temp_newrange, Temp2_Pred)

NPD_ChlRmdPos_Temp2_graph <- ggplot((Deanza_PosFilter_data), aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Temp2_df, aes(x = Temp_C_Up, y = pred_ChlRmd)) +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'NPD Pos Filtration Trials',
       subtitle = 'y ~ x + x^2') +
  guides(fill = FALSE)

grid.arrange(NPD_Chl_RmdPos_Temp, NPD_ChlRmdPos_logTemp_graph,
             NPD_ChlRmdPos_loglogTemp_graph, NPD_ChlRmdPos_Temp2_graph, nrow = 2)
```


### ***Deanza ChlRmd Positive ~ Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_temp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(NPD_ChlRmdPos_temp_lm)
```

> Close to significant p-value: 0.062

### ***Deanza ChlRmd Positive ~ Log Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Temp_C_Up))
ols_regress(NPD_ChlRmdPos_logtemp_lm)
```

> Log transforming x-axis does not help fit. p-value: 0.062

### ***Deanza log ChlRmd Positive ~ Log Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_logChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, log(pcnt_Chl_rmvd) ~ log(Temp_C_Up))
ols_regress(NPD_logChlRmdPos_logtemp_lm)
```

> Log transforming both axes does not help fit. p-value: 0.081

### ***Deanza Y ~ x + x^2 LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_temp2_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ poly(Temp_C_Up, degree = 2, raw = T))
ols_regress(NPD_ChlRmdPos_temp2_lm)
```


Salinity
=====================================

### ***Filtration - Salinity***
```{r Filter_Salinity, fig.height=5, fig.width=14, cache=TRUE, echo=FALSE}

FR_pos_Sal <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'Positive FR only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Sal <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_pos_Sal, Chl_Rmd_pos_Sal, nrow = 1)
```

### ***FR Pos ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_Sal_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Sal_ppt_Up)
ols_regress(FRPos_Sal_lm)
```

> Not significant

### ***ChlRmd Pos ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Sal_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Sal_ppt_Up)
ols_regress(ChlRmdPos_Sal_lm)
```

> Salinity almost significant predictor of ChlRmd (Positive Filter) p-value: 0.075

### ***ChlRmd Pos ~ Salinity Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_Sal_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_Sal_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_Sal_lm))
```

### ***Log ChlRmd Pos - Log Salinity***
```{r LogChlRmdPos_LogSalinity_graph, fig.height=12, fig.width=12, cache=TRUE}
### Graph with log-log axes
logChlRmd_pos_logSal_graph <- ggplot(Filtration_pos_data, aes(log(Sal_ppt_Up), log(pcnt_Chl_rmvd))) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = expression('log'[n]*' Salinity Upstream (ppt)'),
       y = expression(paste(log[n], " Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only') +
  stat_poly_eq(formula = x_y_formula, parse = TRUE)

# log-log model
logChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Sal_ppt_Up))
# create range of Salinity values to predict with model
Sal_newrange <- data.frame(Sal_ppt_Up = seq(from = 29, to = 38, by = 0.5))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
loglogSal_Pred <- data.frame(pred_ChlRmd = exp(predict(logChlRmdPos_logSal_lm, newdata = Sal_newrange)))
pred_loglog_Sal_df <- data.frame(Sal_newrange, loglogSal_Pred)

# model coefficents 
#coef(logChlRmdPos_logSal_lm)

## Graph with regualar x & y axes, log-log model
logChlRmd_pos_logSal_graph2 <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglog_Sal_df, aes(x = Sal_ppt_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = expression(paste(" Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only',
       subtitle = "Log(y) ~ Log(x) pretty sure correct line")

# log X transformed model
ChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Sal_ppt_Up))
pred_ChlRmdPos_logSal_df <- data.frame(Sal_newrange,
                                       pred_ChlRmd = predict(ChlRmdPos_logSal_lm, 
                                                             newdata = Sal_newrange))

ChlRmd_pos_logSal_graph <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_ChlRmdPos_logSal_df, aes(x = Sal_ppt_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = expression(paste(" Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only',
       subtitle = "y ~ log(x)")

# Polynomial ^2 transformation
ChlRmdPos_Sal2_lm <- lm(data = Filtration_pos_data, 
                        pcnt_Chl_rmvd ~ poly(Sal_ppt_Up, degree = 2, raw = T))
# predict values with model and new Sal range values
Sal2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_Sal2_lm, newdata = Sal_newrange))
pred_ChlRmdPos_Sal2_df2 <- data.frame(Sal_newrange, Sal2_Pred)

ChlRmd_pos_Sal2_graph <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_ChlRmdPos_Sal2_df2, aes(x = Sal_ppt_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = expression(paste(" Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only',
       subtitle = "y ~  x + x^2")

# Polynomial ^3 transformation
ChlRmdPos_Sal3_lm <- lm(data = Filtration_pos_data, 
                        pcnt_Chl_rmvd ~ poly(Sal_ppt_Up, degree = 3, raw = T))
pred_ChlRmdPos_Sal3_df <- data.frame(pred_ChlRmd = predict(ChlRmdPos_Sal3_lm, newdata = Sal_newrange),
                                       Sal_newrange)

ChlRmd_pos_Sal3_graph <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_ChlRmdPos_Sal3_df, aes(x = Sal_ppt_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = expression(paste(" Percent Chlorophyll ", alpha, " Removed")),
       title = 'Positive Chl Removed Only',
       subtitle = "y ~  x + x^3")

grid.arrange(logChlRmd_pos_logSal_graph, logChlRmd_pos_logSal_graph2, 
             ChlRmd_pos_logSal_graph, ChlRmd_pos_Sal2_graph, ChlRmd_pos_Sal3_graph, nrow = 3)
```

### ***log ~ log LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Sal_ppt_Up))
ols_regress(logChlRmdPos_logSal_lm)
```

> How to pull out equation for regression? p-value 0.019

### ***log ~ log Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(logChlRmdPos_logSal_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(logChlRmdPos_logSal_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(logChlRmdPos_logSal_lm))
```

### ***Y ~ log LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Sal_ppt_Up))
ols_regress(ChlRmdPos_logSal_lm)
```

> p-value: 0.072

### ***Y ~ log Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_logSal_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_logSal_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_logSal_lm))
```

### ***ANOVA Y ~ X VS Y ~ log(X)***
```{r, fig.height=6, fig.width=6, cache =TRUE}
anova(ChlRmdPos_Sal_lm, ChlRmdPos_logSal_lm)
```

> Models are not significantly different

### ***Y ~ X + X^2 LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Sal2_lm <- lm(data = Filtration_pos_data, 
                        pcnt_Chl_rmvd ~ poly(Sal_ppt_Up, degree = 2, raw = T))
ols_regress(ChlRmdPos_Sal2_lm)
```

> p-value: 0.075

### ***Y ~ X + X^3 LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Sal3_lm <- lm(data = Filtration_pos_data, 
                        pcnt_Chl_rmvd ~ poly(Sal_ppt_Up, degree = 3, raw = T))
ols_regress(ChlRmdPos_Sal2_lm)
```

### ***Deanza only Filtration - Salinity***
```{r NPD_Filter_Salinity, fig.height=5, fig.width=12, cache=TRUE, echo=FALSE}
NPD_FRPos_Salinity <- ggplot(Deanza_PosFilter_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'NPD Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Salinity <- ggplot(Deanza_PosFilter_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'NPD Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(NPD_FRPos_Salinity, NPD_ChlRmdPos_Salinity, nrow = 1)
```

### ***Deanza Pos FR ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FRPos_Sal_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Sal_ppt_Up)
ols_regress(NPD_FRPos_Sal_lm)
```

> Not significant - no obvious transformations

### ***Deanza Pos ChlRmd ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_Sal_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Sal_ppt_Up)
ols_regress(NPD_ChlRmdPos_Sal_lm)
```

> Not significant - no obvious transformations

Chlorophyll
=====================================

### ***Filtration - Chlorophyll***
```{r Filter_Chl, fig.height=15, fig.width=14, cache=TRUE, echo=FALSE}

FR_pos_Chl <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Chl <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

# Y-log model
ChlRmdPos_logChl_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Chl_ug_L_Up))
# create range of Salinity values to predict with model
Chl_newrange <- data.frame(Chl_ug_L_Up = seq(from = 0, to = 8, by = 0.5))
logChl_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_logChl_lm, newdata = Chl_newrange))
pred_logChl_df <- data.frame(Chl_newrange, logChl_Pred)

ChlRmdpos_Chllog_graph <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_logChl_df, aes(x = Chl_ug_L_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'Y ~ log(x)')

# log-log model
ChlRmdPos_loglogChl_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Chl_ug_L_Up))
# predict alone gives log(y) values, exponentiate y to get regular values with exp()
loglogChl_Pred <- data.frame(pred_ChlRmd = exp(predict(ChlRmdPos_loglogChl_lm, newdata = Chl_newrange)))
pred_loglogChl_df <- data.frame(Chl_newrange, loglogChl_Pred)

ChlRmdpos_Chlloglog_graph <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglogChl_df, aes(x = Chl_ug_L_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'log(y) ~ log(x)')

# Y-x + x^2 model
ChlRmdPos_Chl2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Chl_ug_L_Up, degree = 2, raw = T))
Chl2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_Chl2_lm, newdata = Chl_newrange))
pred_Chl2_df <- data.frame(Chl_newrange, Chl2_Pred)

ChlRmdpos_Chl2_graph <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Chl2_df, aes(x = Chl_ug_L_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'Y ~ x + x^2')

grid.arrange(FR_pos_Chl, Chl_Rmd_pos_Chl, 
             ChlRmdpos_Chllog_graph, ChlRmdpos_Chlloglog_graph, 
             ChlRmdpos_Chl2_graph, nrow = 3)
```

### ***FR Pos ~ Chl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_Chl_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Chl_ug_L_Up)
ols_regress(FRPos_Chl_lm)
```

> Not significant

### ***ChlRmd Pos ~ Chl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Chl_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Chl_ug_L_Up)
ols_regress(ChlRmdPos_Chl_lm)
```

> Chl almost significant predictor of Chl Rmd (Pos Filter). p-value: 0.089

### ***Y ~ X Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(ChlRmdPos_Chl_lm)

# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(ChlRmdPos_Chl_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(ChlRmdPos_Chl_lm))
```

### ***ChlRmd Pos ~ logChl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_logChl_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Chl_ug_L_Up))
ols_regress(ChlRmdPos_logChl_lm)
```

> x-axis log transformation does not help fit. p-value: 0.242

### ***logChlRmd Pos ~ logChl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logChlRmdPos_logChl_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Chl_ug_L_Up))
ols_regress(logChlRmdPos_logChl_lm)
```

> log transformation of both axes does not help fit. p-value: 0.236

### ***Y ~ x + x^2 LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Chl2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Chl_ug_L_Up, degree = 2, raw = T))
ols_regress(ChlRmdPos_Chl2_lm)
```


### ***Newport Deanza Filtration***
```{r NPD_Filter_Chl, fig.height=5, fig.width=12, cache=TRUE, echo=FALSE}

NPD_FRPos_Chl <- ggplot(Deanza_PosFilter_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label,
       title = "NPD Positive Filtraiton") +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Chl <- ggplot(Deanza_Filter_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = "NPD Positive Filtraiton") +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(NPD_FRPos_Chl, NPD_ChlRmdPos_Chl, nrow = 1)
```

### ***Deanza FR Pos ~ Chl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FRPos_Chl_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Chl_ug_L_Up)
ols_regress(NPD_FRPos_Chl_lm)
```

> not significant. No obvious transformation to make

### ***Deanza ChlRmd Pos ~ Chl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_Chl_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Chl_ug_L_Up)
ols_regress(NPD_ChlRmdPos_Chl_lm)
```

> not significant. No obvious transformation to make. p-value: 0.224

### ***Y ~ X Diagnostics***
```{r, fig.height=6, fig.width=8, cache =TRUE}
par(mfrow=c(2,2))
plot(NPD_ChlRmdPos_Chl_lm)
# Leverage Statistics - plots index of parameter elements against their leverage on the model
# plot(hatvalues(NPD_ChlRmdPos_Chl_lm)) 
# identifies the index of the largest element of a vector
# which.max(hatvalues(NPD_ChlRmdPos_Chl_lm))
```

### ***Deanza ChlRmd Pos ~ logChl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_logChl_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Chl_ug_L_Up))
ols_regress(NPD_ChlRmdPos_logChl_lm)
```

> Log transforming x-axis didn't improve fit. p-value: 0.244

### ***Deanza logChlRmd Pos ~ logChl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logChlRmdPos_logChl_lm <- lm(data = Deanza_PosFilter_data, log(pcnt_Chl_rmvd) ~ log(Chl_ug_L_Up))
ols_regress(logChlRmdPos_logChl_lm)
```

> Log transforming both axes didn't improve fit. p-value: 0.217

### ***Y ~ x + x^2 LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_Chl2_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ poly(Chl_ug_L_Up, degree = 2, raw = T))
ols_regress(NPD_ChlRmdPos_Chl2_lm)
```

> polynomial transformation does not help fit

Turbidity
=====================================

### ***Filtration - Turbidity***
```{r Filter_Turbidity, fig.height=15, fig.width=14, cache=TRUE, echo=FALSE}

FR_pos_Turb <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Turb <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

# Y-log model
ChlRmdPos_logTurb_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Turbidity_NTU_Up))
Turb_newrange <- data.frame(Turbidity_NTU_Up = seq(from = 2, to = 31, by = 1))
logTurb_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_logTurb_lm, newdata = Turb_newrange))
pred_logTurb_df <- data.frame(Turb_newrange, logTurb_Pred)

ChlRmdpos_Turblog_graph <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_logTurb_df, aes(x = Turbidity_NTU_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'y ~ log(x)')

#log-log model
logChlRmdPos_logTurb_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Turbidity_NTU_Up))
loglogTurb_Pred <- data.frame(pred_ChlRmd = exp(predict(logChlRmdPos_logTurb_lm, newdata = Turb_newrange)))
pred_loglogTurb_df <- data.frame(Turb_newrange, loglogTurb_Pred)

ChlRmdpos_Turbloglog_graph <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_loglogTurb_df, aes(x = Turbidity_NTU_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'log(y) ~ log(x)')

# Y ~ x + x^2 model
ChlRmdPos_Turb2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Turbidity_NTU_Up, degree = 2, raw = T))
Turb2_Pred <- data.frame(pred_ChlRmd = predict(ChlRmdPos_Turb2_lm, newdata = Turb_newrange))
pred_Turb2_df <- data.frame(Turb_newrange, Turb2_Pred )

ChlRmdpos_Turb2_graph <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_line(data = pred_Turb2_df, aes(x = Turbidity_NTU_Up, y = pred_ChlRmd)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only',
       subtitle = 'Y ~ x + x^2') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")

grid.arrange(FR_pos_Turb, Chl_Rmd_pos_Turb,
             ChlRmdpos_Turblog_graph, ChlRmdpos_Turbloglog_graph,
             ChlRmdpos_Turb2_graph, nrow = 3)
```

### ***FR Pos ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_Turb_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Turbidity_NTU_Up)
ols_regress(FRPos_Turb_lm)
```

> Not significant

### ***ChlRmd Pos ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Turb_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Turbidity_NTU_Up)
ols_regress(ChlRmdPos_Turb_lm)
```

> Not significant

### ***ChlRmd Pos ~ logTurbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_logTurb_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ log(Turbidity_NTU_Up))
ols_regress(ChlRmdPos_logTurb_lm)
```

> log transforming Turb doesn't help fit. p-value: 0.398 R^2: 0.072

### ***logChlRmd Pos ~ logTurbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logChlRmdPos_logTurb_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Turbidity_NTU_Up))
ols_regress(logChlRmdPos_logTurb_lm)
```

> log transforming both axes doesn't help fit. p-value: 0.188 R^2: 0.166

### ***Y ~ x + x^2 LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Turb2_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ poly(Turbidity_NTU_Up, degree = 2, raw = T))
ols_regress(ChlRmdPos_Turb2_lm)
```

> Polynomial transformation isn't sig better p-value: 0.68

### ***Deanza Filtration - Turbidity***
```{r NPD_Filter_Turbidity, fig.height=5, fig.width=12, cache=TRUE, echo=FALSE}

NPD_FRPos_Turb <- ggplot(Deanza_PosFilter_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'Deanza - Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Turb <- ggplot(Deanza_PosFilter_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Deanza - Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")



grid.arrange(NPD_FRPos_Turb, NPD_ChlRmdPos_Turb, nrow = 1)

```

### ***Deanza FR Pos ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FRPos_Turb_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Turbidity_NTU_Up)
ols_regress(NPD_FRPos_Turb_lm)
```

> Not significant. Almost. p-value: 0.086, R^2: 0.562

### ***Deanza ChlRmd Pos ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_Turb_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Turbidity_NTU_Up)
ols_regress(NPD_ChlRmdPos_Turb_lm)
```

> Not significant

TPM X OC
=====================================

### ***TPM by OC***
```{r TPM_OC, fig.width=14, fig.height=10, cache=TRUE}
TPM_OC <- ggplot(data = Avg_TPM_summary_table, aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "All Trials") + 
  theme_classic() +
  #geom_text(aes(label=Date), nudge_x = 0.007, nudge_y = 0, check_overlap = T)
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_box <- ggplot((Avg_TPM_summary_table), aes(Site, Avg_TPM)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats3, geom = "text") + # mean isn't working 
  labs(x = 'Site',
       y = TPM_Label,
       title = "Total Particulate Matter by Site")

OC_box <- ggplot((Avg_TPM_summary_table), aes(Site, Avg_OC_Ratio)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats3, geom = "text") + 
  labs(x = 'Site',
       y = "Average Organic Content Ratio",
       title = "Seston Organic Content Ratio by Site")

grid.arrange(OC_box, TPM_box, TPM_OC, nrow = 2)
```

> All Filtration and Neg Control Trials included. Samples independent of kind of trial. Not sure why mean function isn't working on TPM boxplot

### ***All TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
OC_TPM_all_LM <- lm(data = Avg_TPM_summary_table, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_all_LM)
```

> Significant. p-value: 0.032, R^2: 0.164

### ***Log TPM All trials - OC***
```{r logTPM_OC, fig.width=7, fig.height=5, cache=TRUE}
logTPM_OC <- ggplot(data = Avg_TPM_summary_table, aes(x = log(Avg_TPM), y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  labs(x = expression(paste(Log[n], " Total Particulate Matter (", mu, "g/L)")), 
       y = "Average Organic Content Ratio", 
       title = "All Trials") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(logTPM_OC)

```

### ***All logTMP ~ OC***
```{r OC_logTPM_all_LM, fig.height=6, fig.width=6, cache =TRUE}
OC_logTPM_all_LM <- lm(data = Avg_TPM_summary_table, Avg_OC_Ratio ~ log(Avg_TPM))
ols_regress(OC_logTPM_all_LM)
```

> significant. p-value: 0.004, R^2: 0.279

### ***All logTMP ~ logOC***
```{r logOC_logTPM_all_LM, fig.height=6, fig.width=6, cache =TRUE}
logOC_logTPM_all_LM <- lm(data = Avg_TPM_summary_table, log(Avg_OC_Ratio) ~ log(Avg_TPM))
ols_regress(logOC_logTPM_all_LM)
```

> significant. p-value: 0.010, R^2: 0.202

### ***TPM vs OC by sites***
```{r TPM_OC_Sites, fig.height=10, fig.width=12, cache=TRUE}
TPM_OC_Deanza <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Deanza")),
                        aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Deanza") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_NPSM <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Shellmaker")), 
                     aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Shellmaker") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_SR <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "San Rafael")),
                   aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "San Rafael") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_MB <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Morro Bay")), 
                   aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Morro Bay") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(TPM_OC_Deanza, TPM_OC_NPSM, TPM_OC_SR, TPM_OC_MB, nrow = 2)
```

### ***San Rafael TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_SR <- Avg_TPM_summary_table %>% filter(Site == "San Rafael")

OC_TPM_SR_LM <- lm(data = TPM_SR, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_SR_LM)
```

> not significant

### ***Morro Bay TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_MB <- Avg_TPM_summary_table %>% filter(Site == "Morro Bay")

OC_TPM_MB_LM <- lm(data = TPM_MB, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_MB_LM)
```

> not significant

### ***Shellmaker TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_NPSM <- Avg_TPM_summary_table %>% filter(Site == "Shellmaker")

OC_TPM_NPSM_LM <- lm(data = TPM_NPSM, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_NPSM_LM)
```

> not significant

### ***Deanza TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

OC_TPM_NPD_LM <- lm(data = TPM_NPD, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_NPD_LM)
```

> not significant, almost. p-value: 0.94

### ***Deanza logTMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

OC_logTPM_NPD_LM <- lm(data = TPM_NPD, Avg_OC_Ratio ~ log(Avg_TPM))
ols_regress(OC_logTPM_NPD_LM)
```

> significant. p-value: 0.027

### ***Deanza logTMP ~ logOC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

logOC_logTPM_NPD_LM <- lm(data = TPM_NPD, log(Avg_OC_Ratio) ~ log(Avg_TPM))
ols_regress(logOC_logTPM_NPD_LM)
```

> more significant. p-value: 0.013

DTW X Shell length
=====================================

### ***Newport Olympia Shell length vs DTW***
```{r Oly_DTW_Shell_length, fig.height=5, fig.width=6, cache=TRUE}

# Determine what quadrat samples have missing data (NAs)
NPD_biv_bio_summary <- NPD_density %>% 
  group_by(excavation_sample) %>% 
  summarize(avg_DTW = mean(tissue_dry_weight_g))

# what are the unique species in dataset
unique(NPD_density$species)

# Still contains missing data --> which quadrats to use for analyses
NPD_bivalve_data_clean <- NPD_density %>% 
  filter(!excavation_sample %in% c("Q10", "Q4", "Q8")) %>% 
  mutate(species = ifelse(grepl("adula", ignore.case = T, species), "Adula diegensis",
                          ifelse(grepl("muscul.", ignore.case = T, species), "Musculista senhousia",
                                 ifelse(grepl("myt", ignore.case = T, species), "Mytilus galloprovincialis",
                                        ifelse(grepl(".lurida", ignore.case = T, species), "Ostrea lurida",
                                               ifelse(grepl("mussel", ignore.case = T, species), "Unknown mussel",
                                                      ifelse(grepl(".spinosum", ignore.case = T, species), "Crucibulum spinosum",
                                                       "Pattern Not Found"))))))) %>% 
  # Filter out unclassified/ empty species & samples less than 0g (processing error, doesn't make sense)
  filter(!species %in% c("Pattern Not Found", "Crucibulum spinosum"))


#Olympia DTW predicted by Shell Length - Newport, CA
# All excavation quadrat samples processed to date aggregated 
NPD_oly <- NPD_bivalve_data_clean %>% 
  filter(species == "Ostrea lurida") %>% 
  drop_na() %>% 
  as_tibble() 

Oly_shell_DTW <- ggplot(NPD_oly, aes(length_mm, tissue_dry_weight_g)) +
  geom_smooth(method = lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'With outlier (bad data)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top") +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

plot(Oly_shell_DTW)
```

> Outlier probably sample processing error or error in data entry. Negative DTW data point, doesn't make sense. remove?

### ***DTW Shell length Outlier analysis***
```{r Oly_DTW_SH_outLier_removed, fig.height=5, fig.width=6, cache=TRUE}
# Remove outlier and negative DTW value
NPD_oly_outRmd <- NPD_oly %>%
  mutate(DTW_outlier = find_outlier(NPD_oly$tissue_dry_weight_g)) %>% 
  filter(DTW_outlier == FALSE & tissue_dry_weight_g >= 0) ### Is this right? Should this be and OR statement

# Graph with outliers removed
Oly_shell_DTW_rm_out <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  geom_smooth(method=lm, formula = x_y_formula, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
 # scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Outlier removed (outside mean +- 2.2 SD)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom") +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

plot(Oly_shell_DTW_rm_out)
```

> Shell length explains 49% of Dry Tissue Weight. Compare this relationship [Gray unpublished cited in Blake & zu Ermgassen 2015] (Yaquina Bay) --> DTW = 6x10e-6 * SH^3.06. Negative DTW data point doesn't make senese

### ***Linear model without outlier***
```{r Linear_model_DTW_length, fig.height=6, fig.width=6, cache=TRUE}
Oly_DTW_lm <- lm(data = NPD_oly_outRmd,
                         tissue_dry_weight_g ~ length_mm)

ols_regress(Oly_DTW_lm)
```

> significant predictor. p-value: 0.000, R^2: 0.49

### ***Log Transform DTW***
```{r, fig.height=5, fig.width=12, cache=TRUE}
Oly_shell_logDTW <- ggplot(NPD_oly_outRmd, aes(length_mm, log(tissue_dry_weight_g))) +
  geom_smooth(method=lm, formula = x_y_formula, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = expression('Log'[n]*' Dry Tissue Weight (g)'),
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Outlier removed (outside mean +- 2.2 SD)') +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

### Trying to add model line to regular axes using predicted data
Oly_LogDTW_lm <- lm(data = NPD_oly_outRmd,
                    log(tissue_dry_weight_g) ~ length_mm)
pred_logDTW_SH <- data.frame(DTW_pred = exp(predict(Oly_LogDTW_lm)), SH = NPD_oly_outRmd$length_mm)

Oly_shell_DTW_logline <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  #geom_smooth(method=lm, formula = x_y_formula, se=TRUE, level=0.95, color = 'grey50') +
  geom_line(data = pred_logDTW_SH, aes(x = SH, y = DTW_pred)) +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Outlier removed (outside mean +- 2.2 SD)') +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

grid.arrange(Oly_shell_logDTW, Oly_shell_DTW_logline, nrow = 1)

```

> ggpmisc package only works for linear and polynomial equations. Not logrithmic 

### ***Log transform DTW***
```{r, fig.height=6, fig.width=6, cache=TRUE}
Oly_LogDTW_lm <- lm(data = NPD_oly_outRmd,
                    log(tissue_dry_weight_g) ~ length_mm)

ols_regress(Oly_LogDTW_lm)
```

> R^2: 0.67, length significant predictor of log(DTW) p-value: 0.000

### ***ANOVA Lm VS log(DTW)~SH***
```{r}
anova(Oly_DTW_lm, Oly_LogDTW_lm )
```

> Warning Message: models with response "log(tissue_dry_weight_g)" removed because response differs from model 1

### ***Log DTW, Log SH***
```{r, fig.height=5, fig.width=6, cache=TRUE}
Oly_logshell_logDTW <- ggplot(NPD_oly_outRmd, aes(log(length_mm), log(tissue_dry_weight_g))) +
  geom_smooth(method=lm, formula = x_y_formula, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = F) +
  theme_classic() +
  labs(x = expression("log"[n]*' Shell Length (mm)'),
       y = expression('Log'[n]*' Dry Tissue Weight (g)'),
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Outlier removed (outside mean +- 2.2 SD)') +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

plot(Oly_logshell_logDTW)
```

### ***Log transform DTW & shell length***
```{r, fig.height=6, fig.width=6, cache=TRUE}
Oly_LogDTW_logSH_lm <- lm(data = NPD_oly_outRmd,
                    log(tissue_dry_weight_g) ~ log(length_mm))

ols_regress(Oly_LogDTW_logSH_lm)
```

> R^2 0.72. p-value: 0.000. Slightly better fit than just y-axis transformation. Interpret the x coefficient as the percent increase in y for every 1% increase in x (log-log)

### ***
```{r}


```

### ***Total Wet Weight vs Dry Tissue Weight***
```{r, fig.height=5, fig.width=6, cache=TRUE}
Oly_TWW_DTW<- ggplot(NPD_oly, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = 'Total wet weight (g)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Total Wet Weight - Newport, CA') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")
plot(Oly_TWW_DTW)
```

### ***TWW vs DTW (remove outlier)***
```{r, fig.height=5, fig.width=6, cache=TRUE}
# use DTW outlier data to plot graph
Oly_TWW_DTW_rm_out <- ggplot(NPD_oly_outRmd, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide=FALSE) +
  theme_classic() +
  labs(x = 'Total wet weight (g)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Total Wet Weight - Newport, CA') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(Oly_TWW_DTW_rm_out)
```

> Gray and Langdon (2017): "Unless explicitly mentioned, DTW of experimental oysters was estimated using the species-specific allometric relationship between DTW and total wet weight (TWW), which were determined in preliminary analysis (O. lurida: DTW = 0.0044TWW  0.043, R2 =0.93, F1,32 =78.80, p value <0.0001; C. gigas: DTW = 0.039TWW  0.06, R2 =0.89, F1,29 = 225.97, p value <0.0001).

### ***Linear model without outlier***
```{r, fig.height=6, fig.width=6, cache=TRUE}
Oly_TWW_DTW_lm_rm_out <- lm(data = NPD_oly_outRmd,
                         tissue_dry_weight_g ~ total_wet_weight_g)

ols_regress(Oly_TWW_DTW_lm_rm_out)
```

> significant. p-value: 0.000, R^2 0.602

### ***Log TWW vs Log DTW*** 
```{r, fig.height=5, fig.width=6, cache=TRUE}
# use DTW outlier data to plot graph
Oly_logTWW_DTW <- ggplot(NPD_oly_outRmd, aes(log(total_wet_weight_g), log(tissue_dry_weight_g))) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  scale_fill_manual(values = Species_colors) + 
  theme_classic() +
  labs(x = expression('Log'[n]*" Total wet weight (g)"),
       y = expression('Log'[n]*'Dry Tissue Weight (g)'),
       title = 'Olympia Oyster DTW predicted by Total Wet Weight - Newport, CA') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(Oly_logTWW_DTW)
```

### ***Log DTW X  Log TWW LM***
```{r, fig.height=6, fig.width=6, cache=TRUE}
Oly_TWW_DTW_log_LM <- lm(data = NPD_oly_outRmd %>% filter(total_wet_weight_g > 0), 
                         log(tissue_dry_weight_g) ~ log(total_wet_weight_g))
ols_regress(Oly_TWW_DTW_log_LM)
```

> significnt. p-value: 0.00, R^2: 0.846

### ***DTW X  Log TWW LM***
```{r, fig.height=6, fig.width=6, cache=TRUE}
Oly_logTWW_DTW_LM <- lm(data = NPD_oly_outRmd %>% filter(total_wet_weight_g > 0), 
                         tissue_dry_weight_g ~ log(total_wet_weight_g))
ols_regress(Oly_logTWW_DTW_LM)
```

> significant. p-value: 0.00, R^2: 0.493. Not as good as transforming both axes

### ***NPD Bivalve SH DTW***
```{r NPD_Bivalve_SH_DTW, fig.height=6, fig.width=15, cache=TRUE}
##### Estimate Biomass per site here with equations

NPD_bivalve_biomass_graph <- NPD_bivalve_data_clean %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g, color = species)) +
  geom_point() +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  facet_wrap(~species) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = "Newport Deanza Bivalve Biomass - Raw data") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

# Remove negative DTW (doesn't make sense to have negative #s, probably processing error)
NPD_Posbiomass_data <- NPD_bivalve_data_clean %>% 
  filter(tissue_dry_weight_g > 0)

NPD_Posbiomass_graph <- NPD_Posbiomass_data %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g, group = species, color = species)) +
  geom_point() +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  facet_wrap(~species) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = "Newport Deanza Bivalve Biomass - Positive DTW only") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic"))

grid.arrange(NPD_bivalve_biomass_graph, NPD_Posbiomass_graph, nrow = 1)
```

### ***NPD Adula***
```{r, fig.height=5, fig.width=6, cache=TRUE}
NPD_Adula <- NPD_Posbiomass_data %>% 
  filter(species %in% c("Adula diegensis"))

NPD_Adula_Posbiomass_graph <- NPD_Adula %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Adula diegensis")," - Positive DTW only"))) +
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

NPD_Adula_Posbiomass_loggraph <- NPD_Adula %>% 
  ggplot(aes(x = log(length_mm), y = log(tissue_dry_weight_g))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Ln Shell length (mm)",
       y = "Ln Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Adula diegensis")," - Positive Ln DTW only"))) +
  theme_classic() +
  stat_poly_eq(aes(label = stat(adj.rr.label)), formula = x_y_formula, 
               parse = TRUE)

grid.arrange(NPD_Adula_Posbiomass_graph, NPD_Adula_Posbiomass_loggraph, nrow = 1)
```

### ***LM - Adula DTW ~ SH***
```{r}
NPD_Adula_lm <- lm(data = NPD_Adula, tissue_dry_weight_g ~ length_mm)
ols_regress(NPD_Adula_lm)
```

> SH significant predictor of DTW. p-value: 0.00, R^2: 0.64

### ***LM - Adula logDTW ~ SH***
```{r}
NPD_Adula_logDTW_lm <- lm(data = NPD_Adula, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(NPD_Adula_logDTW_lm)
```

> R^2 slightly better: 0.76

### ***LM - Adula logDTW ~ logSH***
```{r}
NPD_Adula_logDTW_logSH_lm <- lm(data = NPD_Adula, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(NPD_Adula_logDTW_logSH_lm)
```

> R^2 even better: 0.809

### ***NPD Musculista*** 
```{r}
NPD_Musculista <- NPD_Posbiomass_data %>% 
  filter(species %in% c("Musculista senhousia"))

NPD_Musculista_Posbiomass_graph <- NPD_Musculista %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Musculista senhousia")," - Positive DTW only"))) +
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

NPD_Musculista_Posbiomass_loggraph <- NPD_Musculista %>% 
  ggplot(aes(x = length_mm, y = log(tissue_dry_weight_g))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Ln Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Musculista senhousia")," - Positive Ln DTW only"))) +
  theme_classic() +
  stat_poly_eq(aes(label = stat(adj.rr.label)), formula = x_y_formula, 
               parse = TRUE)

grid.arrange(NPD_Musculista_Posbiomass_graph, NPD_Musculista_Posbiomass_loggraph, nrow=1)
```

### ***LM - Musculista DTW ~ SH***
```{r}
NPD_Musculista_lm <- lm(data = NPD_Musculista, tissue_dry_weight_g ~ length_mm)
ols_regress(NPD_Musculista_lm)
```

> Significant p-value: 0.00 R^2 0.432

### ***LM - Musculista logDTW ~ SH***
```{r}
NPD_Musculista_logDTW_lm <- lm(data = NPD_Musculista, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(NPD_Musculista_logDTW_lm)
```

> significant p-value: 0.00, R^2: 0.584

### ***LM - Musculista logDTW ~ logSH***
```{r}
NPD_Musculista_logDTW_logSH_lm <- lm(data = NPD_Musculista, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(NPD_Musculista_logDTW_logSH_lm)
```

> significant p-value: 0.00, R^2: 0.587, not much better than y-axis transformation

### ***NPD Mytilus***
```{r}

NPD_Mytilus <- NPD_Posbiomass_data %>% 
  filter(species %in% c("Mytilus galloprovincialis"))

NPD_Mytilus_Posbiomass_graph <- NPD_Mytilus %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Mytilus galloprovincialis")," - Positive DTW only"))) +
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

NPD_Mytilus_Posbiomass_loggraph <- NPD_Mytilus %>% 
  ggplot(aes(x = length_mm, y = log(tissue_dry_weight_g))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Ln Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Mytilus galloprovincialis")," - Positive Ln DTW only"))) +
  theme_classic() +
  stat_poly_eq(aes(label = stat(adj.rr.label)), formula = x_y_formula, 
               parse = TRUE)

grid.arrange(NPD_Mytilus_Posbiomass_graph, NPD_Mytilus_Posbiomass_loggraph, nrow = 1)
```

### ***LM - Mytilus DTW ~ SH***
```{r}
NPD_Mytilus_lm <- lm(data = NPD_Mytilus, tissue_dry_weight_g ~ length_mm)
ols_regress(NPD_Mytilus_lm)
```

> Significant p-value: 0.00, R^2: 0.718

### ***LM - Mytilus logDTW ~ SH***
```{r}
NPD_Mytilus_logDTW_lm <- lm(data = NPD_Mytilus, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(NPD_Mytilus_logDTW_lm)
```

> significant p-value: 0.00 R^2: 0.904

### ***LM - Mytilus logDTW ~ logSH***
```{r}
NPD_Mytilus_logDTW_logSH_lm <- lm(data = NPD_Mytilus, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(NPD_Mytilus_logDTW_logSH_lm)
```

> significant p-value: 0.00, R^2: 0.815

### ***LM - Unknown mussel***
```{r}
NPD_Unknown <- NPD_Posbiomass_data %>% 
  filter(species %in% c("Unknown mussel"))

NPD_Unknown_Posbiomass_graph <- NPD_Unknown %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Unknown mussel")," - Positive DTW only"))) +
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "left",
               label.y = "top")

NPD_Unknown_Posbiomass_loggraph <- NPD_Unknown %>% 
  ggplot(aes(x = length_mm, y = log(tissue_dry_weight_g))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = species)) +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  labs(x = "Shell length (mm)",
       y = "Ln Dry Tissue Weight (g)",
       title = expression(paste("NPD ", italic("Unknown mussel")," - Positive Ln DTW only"))) +
  theme_classic()  +
  stat_poly_eq(aes(label = stat(adj.rr.label)), formula = x_y_formula, 
               parse = TRUE)

grid.arrange(NPD_Unknown_Posbiomass_graph, NPD_Unknown_Posbiomass_loggraph, nrow =1)

```

### ***LM - Unknown mussel DTW ~ SH***
```{r}
NPD_Unknown_lm <- lm(data = NPD_Unknown, tissue_dry_weight_g ~ length_mm)
ols_regress(NPD_Unknown_lm)
```

> Not significant p-value: 0.063, R^2: 0.532

### ***LM - Unknown mussel logDTW ~ SH***
```{r}
NPD_Unknown_logDTW_lm <- lm(data = NPD_Unknown, log(tissue_dry_weight_g) ~ length_mm)
ols_regress(NPD_Unknown_logDTW_lm)
```

> significant p-value: 0.024, R^2: 0.673

### ***LM - Unknown mussel logDTW ~ logSH***
```{r}
NPD_Unknown_logDTW_logSH_lm <- lm(data = NPD_Unknown, log(tissue_dry_weight_g) ~ log(length_mm))
ols_regress(NPD_Unknown_logDTW_logSH_lm)
```

> not better, p-value: 0.036, R^2: 0.618

### ***Biomass estimate - Remove outliers***
```{r Newport_Bivalve_biomass_outlier, fig.height=6, fig.width=8, cache=TRUE}
# remove outliers from data
NPD_Posbiomass_outlier <- NPD_Posbiomass_data %>% 
  mutate(DTW_outlier = find_outlier(NPD_Posbiomass_data$tissue_dry_weight_g)) %>% 
  filter(DTW_outlier == FALSE)

NPD_Posbiomass_outlierrmd_graph <- NPD_Posbiomass_outlier %>% 
  ggplot(aes(x = length_mm, y = tissue_dry_weight_g, color = species)) +
  geom_smooth(method = lm) +
  geom_point() +
  scale_color_manual(values = Species_colors, guide = FALSE) +
  facet_wrap(~species) +
  labs(x = "Shell length (mm)",
       y = "Dry Tissue Weight (g)",
       title = "Newport Deanza Bivalve Biomass",
       subtitle = "Positive DTW, outliers removed") +
  theme_classic() +
  theme(strip.text = element_text(face = "italic")) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_Posbiomass_outlierrmd_graph
```

### ***NPD Bivalve Biomass***
```{r}
Bivalve_Biomass_graph <- ggplot(NPD_Posbiomass_outlier, aes(Site)) + 
  geom_col(aes(x = Site, y = tissue_dry_weight_g, fill = species)) +
  theme_classic() +
  scale_fill_manual(values = Species_colors) +
  #scale_y_continuous(breaks = seq(0, max(NPD_Posbiomass_outlier$tissue_dry_weight_g), by = 500)) +
  labs(y = "Dry Tissue Weight (g)")

Bivalve_Biomass_graph
# Order species by DTW not alphabetical order
```


Density & Biomass
=====================================

### ***Bivalve Density***
```{r Bivalve_Density, fig.height=6, fig.width=8, cache=TRUE}
# read in bivalve density data from cleaned data file
Bivalve_Den_data <- fread(file.path(Bivalve_output_directory, "Bivalve_Density_summary.csv"))

# replace NAs with 0s
Bivalve_Den_data[is.na(Bivalve_Den_data)] <- 0

Bivalve_Den_data <- Bivalve_Den_data %>% 
  # move species from individual columns to a single column with new density column to contain data
  pivot_longer(c(Adula_diegensis_m2, Musculista_senhousia_m2, Mytilus_galloprovincialis_m2,
                 Ostrea_lurida_m2, Crassostrea_gigas_m2, Argopecten_ventricosa_m2, 
                 Geukensia_demissa_m2, Crassostrea_gigas_m2), 
               names_to = "Species", 
               values_to =  "individuals_m2") %>% 
  # remove "_m2" from species names in Species column
  mutate(Species = str_replace(Species, "_m2", ""),
         Species = str_replace(Species, "_", " "))

#Reorder levels of Site factor - display North to South
order_by_site <- c("San Rafael", "Morro Bay", "Shellmaker", "Deanza") 
Bivalve_Den_data <- arrange(transform(Bivalve_Den_data, Site = factor(Site,levels = order_by_site)), Site)


unique(Bivalve_Den_data$Species) # list each individual bivalve species
# Assign species to specific color
Species_colors <- c("Adula diegensis" = "#8D8680",
                    "Argopecten ventricosa" = "#CCC3C5",
                    "Crassostrea gigas" = "#6D6340",
                    "Geukensia demissa" = "#524D4F",
                    "Musculista senhousia" = "#B0915B",
                    "Mytilus galloprovincialis" = "#7E4B41",
                    "Ostrea lurida" = "#9986A5",
                    "Unknown mussel" = "black")

# Stacked bar graph
Bivalve_Den_graph <- ggplot(Bivalve_Den_data, aes(Site)) + 
  geom_col(aes(x = Site, y = individuals_m2, fill = Species)) +
  geom_text(aes(label = round(Bivalve_den_m2,0), y = Bivalve_den_m2), 
            vjust = -0.5) +
  theme_classic() +
  scale_fill_manual(values = Species_colors) +
  scale_y_continuous(breaks = seq(0, max(Bivalve_Den_data$Bivalve_den_m2), by = 500)) +
  labs(y = expression("Individuals per m"^2))
  
Bivalve_Den_graph
```

> Data for each site is from a single survey

Up & Down
=====================================

### ***Facet Plots***
```{r Bar_Graphs_up_vs_down, cache=TRUE}
Bar_up_down_data <- Master_analysis_table %>%
 # select(Experiment, Date, Site, Chl_ug_L_Up, Chl_ug_L_Down) %>%
  rename(Upstream = Chl_ug_L_Up, Downstream = Chl_ug_L_Down) %>%  
  gather(Upstream, Downstream, key = Position, value = Chl_ug_L) %>% 
  mutate(Position = fct_relevel(Position, 'Upstream', 'Downstream')) %>% 
  mutate(Site = fct_relevel(Site, 'Deanza', 'Shellmaker', 'San Rafael', 'Morro Bay')) %>% 
  mutate(Site_exp_date = paste(Site, Experiment, Date, sep = ' ')) %>% 
  mutate(Exp_Date = paste(Experiment, Date, sep = ' ')) %>% 
  arrange(Site, mdy(Date))

#Bar_up_down_data$Position <- as.factor(Bar_up_down_data$Position)

Paired_bar_chl_graph <- ggplot(data = Bar_up_down_data, aes(x = Site_exp_date, y = Chl_ug_L, fill = Position)) +
    geom_bar(stat="identity", position = "dodge") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    facet_grid(~ Site, scales = "free", space = "free") + #'free' allows axis b/w sites uneaven
    geom_bar(data = (Bar_up_down_data %>%
                       filter(!Experiment %in% c('Filtration'))),
             color = "grey22",
             stat="identity",
             position = "dodge") +
    labs(x = 'Experiment', y = 'Chlorophyl (ug/L)')

plot(Paired_bar_chl_graph)
```

### ***Graphs using grid.arrange()***
```{r Bar_Graphs_up_vs_down_grid.arrange, cache=TRUE}
############## Try 2 ####### make separate graphs, combine using grid.arrange()

##### Can't figure out how to properly label x axis. Works with Exp_Date, but can't shorten without messing up data:label pairs. Can't spend more time on this right now. come back if time -AM 2020_3_3

NPD_bar_data <- Bar_up_down_data %>% 
  filter(Site == "Deanza") %>% 
  mutate(graph_Label = ifelse(grepl("^Filtration", Exp_Date), str_replace(Exp_Date, "Filtration ", ""),
                             str_replace(Exp_Date, "^Neg Control .", "")))

NPD_bar_graph <- ggplot(data = NPD_bar_data, aes(x = Exp_Date, y = Chl_ug_L, 
                                                 fill = Position)) +
    geom_col(position = position_dodge(width = 0.9, preserve = "single")) +
    geom_col(data = (NPD_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.x = element_blank(),
          legend.position = c(0.9, 0.8),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(y = 'Chlorophyll a (ug/L)', title = "Newport Deanza") +
  # This labels the x-axis
    #scale_x_discrete(labels = Exp_Date) +
    ylim(0, 8)

NPSM_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'Shellmaker')

NPSM_bar_graph <- ggplot(data = NPSM_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (NPSM_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "Newport Shellmaker") +
    # scale_x_discrete(labels = NPSM_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE) 

MB_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'Morro Bay')

MB_bar_graph <- ggplot(data = MB_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (MB_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "Morro Bay") +
   # scale_x_discrete(labels = MB_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE)

SR_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'San Rafael')

SR_bar_graph <- ggplot(data = SR_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (SR_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "San Rafael") +
    #scale_x_discrete(labels = SR_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE)

Chl_graphs <- list(NPD_bar_graph, NPSM_bar_graph, SR_bar_graph, MB_bar_graph) 
all_chl_graphs <- grid.arrange(grobs = Chl_graphs,
             widths = c(1,1,1,1,1,1,1,1,1,1,1,1,1,1),
             layout_matrix = rbind(c(NA,1,1,1,1,1,1,1,1,1,1,1,1, NA),
                                   c(2,2,2,2,2,3,3,3,3,3,4,4,4,4)))
plot(all_chl_graphs)
#ggsave("Insitu_Filter_up_vs_down_all_sites.png", all_chl_graphs)
```

Multiple Regression
=====================================

### ***Chl Rmd - Positive Filtration Stepwise Multiple Regression***
```{r LM_PrctChl_pos_add, fig.height=5, fig.width=6, cache=TRUE}

# Positive Percent Chl removed trials only
LM_PrctChl_pos_add <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + #Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)

ols_step_both_p(LM_PrctChl_pos_add)
```

> Not enough degrees of freedom to run full model. Stepwise selects variable with significant p-values. Try adding in log transformed Salinity. 

### ***Positive Filtration ~ ChlRmd Multiple Regression with selected variables***
```{r, fig.height=5, fig.width=6, cache=TRUE}
LM2_PrctChl_pos_add <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ 
                          NPSM + Avg_OC_Ratio)

summary(LM2_PrctChl_pos_add)
# diagnosis of colinearity
#ols_coll_diag(LM_PrctChl_pos_add)
```

> Site and OC Ratio significant model to predict positive ChlRmd. 

### ***Positive Filtration ~ ChlRmd Multiple Regression with selected variables***
```{r, fig.height=10, fig.width=6, cache=TRUE}
# detailed multiple regression summary - ANOVA results
ols_regress(LM2_PrctChl_pos_add)
```

> Site and OC Ratio significant model to predict postivie ChlRmd. 

### ***FR - Positive Filtration Stepwise Multiple Regression***
```{r LM_FR_pos, cache=TRUE}

# Positive Percent Chl removed trials only
LM_FR_pos <- lm(data = Filtration_pos_data, L_hr_m2 ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + # Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)

ols_step_both_p(LM_FR_pos)
```

> NPSM is the only variable added in after stepwise. Not enough DF to run full model

### ***Chl Rmd - Deanza - Positive Filtration***
```{r LM_ChlRmd_NPD_PosFilter, cache=TRUE}
LM_ChlRmd_NPD_PosFilter <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + # Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)
# not enough degrees of freedom for full model
ols_step_both_p(LM_ChlRmd_NPD_PosFilter)
```

> Not enough data to run all combinations. Lots of errors. Distance between sondes, Turbidity, Temp

### ***FR - Deanza - Positive Filtration***
```{r LM_FR_NPD_Posfilter, eval=FALSE, cache=TRUE, include=FALSE}
LM_FR_NPD_Posfilter <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + #Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)
# not enough degrees of freedom for full model
ols_step_both_p(LM_FR_NPD_Posfilter)
```

> lots of errors, won't run, no output
