---
title: "In situ Filtration Analysis Graphs"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: yeti
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
################### Packages ###########################
library(dplyr)
library(tidyr)
library(data.table)
library(magrittr)
library(lubridate) # dealing with time and dates
library(ggplot2)
library(ggthemes) # theme_classic() for graphs
library(stringr)
library(hms)
library(viridisLite)
library(forcats)
library(gridExtra)
library(ggpmisc) # package for adding line equation and R^2 to plots
library(viridis) # Color palette - Options: magma , inferno, plasma, viridis, cividis
library(scales)
library(cowplot) # for arranging multiple plots into a single figure
library(wesanderson)
library(olsrr) # ols_step_backward_p() "builds regression model from a set of candidate predictor variables" 
# replaces ols_step_backward()

# source functions 
source("functions.R")
# define output directory
output_directory = "./output"
# create output directories (same as Insitu_Filtraiton_Analysis_script.Rmd)
createOutputDirectories()

##################### Read in Data from  project output ##########################
Master_analysis_table <- fread(file.path('./output/4_Filtration_Calculations/Filtration_Summary', "Master_Filtration_analysis_table.csv"))
Avg_TPM_summary_table <- fread(file.path('./output/5_TPM_OC_Summary', "Avg_TPM_summary_table.csv"))
Density_directory = "./Data/bivalve_density_community"
NPD_density = fread(file.path(Density_directory, "Insitu_Filter_NPD_bivalve_biomass_data.csv"))

##################### Data #########################################
# Remove San Diego filtration trial - not applicable to this analysis - different experimental set up
Master_analysis_table <- Master_analysis_table %>% 
  filter(!Site %in% c("San Diego"))

# Order Sites by Latitude
site_by_lat <- c("San Rafael", "Morro Bay", "Shellmaker", "Deanza") 

# transform Site variable to factor and arange by Latitude
Master_analysis_table <- arrange(transform(Master_analysis_table, Site = factor(Site,levels = site_by_lat)), Site)

 # Filtration trials only - exclude Negative controls
Filtration_only_data <- Master_analysis_table %>% 
  filter(Experiment %in% c("Filtration"))

# Filtration trials only - exclude Negative controls & Percent Chl removed greater than 0
### Important Note ## When Percent Chl removed is positive, so is L/hr/m^2 and vice visa. 
# Filtering by pcnt_Chl_rmvd effectively filters both values the same, so further analysis 
# withFiltration_pos_data serves both purposes. 
Filtration_pos_data <- Filtration_only_data %>% 
  filter(pcnt_Chl_rmvd > 0)

# Deanza data only - all trials
Deanza_data_all <- Master_analysis_table %>% 
  filter(Site %in% c("Deanza"))
# Deanza only - Filtraiton trials only
Deanza_Filter_data <- Deanza_data_all %>% 
  filter(Experiment %in% c("Filtration"))
# Deanza only- Positive Filtration only
Deanza_PosFilter_data <- Deanza_Filter_data %>% 
  filter(pcnt_Chl_rmvd > 0)

### Average TPM Data ######################
Avg_TPM_summary_table <- arrange(transform(Avg_TPM_summary_table, Site = factor(Site, levels = site_by_lat)), Site)

############### model formulas ###############
# linear model formula
x_y_formula <- y ~ x 
# Quadratic model
x2_y_formula <- y ~ x^2
# Exponential model
logy_x_formula <- log(y) ~ x 

############### Site Color Assignments ###############
viridis(4)
Site_colors <- c("San Rafael" = "#440154FF",
                 "Morro Bay" = "#31688EFF",
                 "Shellmaker" = "#35B779FF",
                 "Deanza" = "#FDE725FF")

################# Labels for graphs  #########################
Hab_FR_Label <- expression('Habitat Filtration Rate (L/hr/m'^2*')')
Prt_Chl_Label <- expression(paste('Percent Chlorophyll ', alpha, ' Removed'))
Chl_ugL_Label <- expression(paste("Chlorophyll ", alpha, " (", mu, "g/L) "))
TPM_Label <- expression(paste('Total Particulate Matter (', mu,"g/L)"))

###################### Functions ####################################
# function for number of samples - display on graph
n_mean_stats <- function(x){
  return(tibble(y = max(x) * 0.95, 
                    label = paste("n = ",length(x), "\n",
                                  'mean =', round(mean(x), 1), '\n')
                )
         )
}
# function for number of samples - 3 decimal places
n_mean_stats3 <- function(x){
  return(tibble(y = max(x) * 0.95, 
                    label = paste("n = ",length(x), "\n",
                                  'mean =', round(mean(x), 3), '\n')
                )
         )
}

# function to calculate average, standard deviation, outlier data. 
find_outlier <- function(data){
  average <- mean(data)
  stdev <- sd(data)
  # Outlier data defined by outside 2.2 standard deviations from the mean 
  outlier <- ifelse((data < (average - 2.2 * stdev) | (data > (average + 2.2 * stdev))),
         TRUE, FALSE)
}
```

Multiple Regression
=====================================
### ***Chl Removed - All Data (Filtration and Negative Control)***
```{r LM_Prct_Chl_All, fig.height=15, fig.width=6, cache=TRUE}

LM_PrctChl_All <- lm(data = Master_analysis_table, pcnt_Chl_rmvd ~
                      # site logic variables - SR not included - would break model
                       NPD + NPSM + MB + 
                       Filter_trial + Wind + G_upstream + Daylight + Sonde_fell + 
                       Boat_wake + Algae +
                      # Quantatative variables
                       Temp_C_Up + Sal_ppt_Up +  Turbidity_NTU_Up + Chl_ug_L_Up +
                       avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio ) 
                      # Bivavle density is essentially the same as site, not sure if needed. 
                      # May be appropriate NPD vs NPSM  
                      # Bivalve_den_m2)

# multiple regression summary
summary(LM_PrctChl_All)
```

### ***All Trials All Data ~ ChlRmd Multiple Linear Regression***
```{r, fig.height=15, fig.width=6, cache=TRUE}
# detailed multiple regression
ols_regress(LM_PrctChl_All)
```

### *** All Trials All Data ~ ChlRmd Stepwise Multiple Linear Regression***
```{r, fig.height=15, fig.width=6, cache=TRUE}
# stepwise regression - enter and remove based on p-values
ols_step_both_p(LM_PrctChl_All)
# ols_step_backward_p(LM_PrctChl_All) # Not sure the difference from ols_step_both_p
# diagnosis of colinearity
# ols_coll_diag(LM_PrctChl_All)

```
 
> Why does stepwise removal of candidate predictor variables not match significance results of full multiple regression? 

### ***FR - All Data (Filtration and Negative Control)***
```{r LM_FR_All, fig.height=15, fig.width=6, cache=TRUE}

LM_FR_All <- lm(data = Master_analysis_table, L_hr_m2 ~
                        # site logic variables - SR not included - would break model
                       NPD + NPSM + MB + Filter_trial +
                       Wind + G_upstream +  Daylight + Sonde_fell +  Boat_wake + Algae +
                        # Quantatative variables
                       Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                       avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio ) 
                      # Bivavle density is essentially the same as site, not sure if needed. 
                      # May be appropriate NPD vs NPSM  
                      # Bivalve_den_m2)

# multiple regression summary
summary(LM_FR_All)
```

### ***Filtration Trials ~ FR multiple regression***
```{r, fig.height=20, fig.width=6, cache=TRUE}
# detailed multiple regression summary - ANOVA results
ols_regress(LM_FR_All)
```

### ***Filtration Trials ~ FR Stepwise multiple regression***
```{r, fig.height=15, fig.width=6, cache=TRUE}
# Stepwise regression
ols_step_both_p(LM_FR_All)
# # diagnosis of colinearity
#ols_coll_diag(LM_FR_All)
```

### ***Chl Removed - Filtraiton Trials Only***
```{r LM_PrctChl_Filter_only, fig.height=15, fig.width=6, cache=TRUE}
# Filtration Trials only - no Negative Controls
LM_PrctChl_Filter <- lm(data = Filtration_only_data, pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM +  MB + 
                         # Field notes logic variables
                         Wind + G_upstream + Daylight +
                         Sonde_fell + Boat_wake +  Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)

# multiple regression summary
summary(LM_PrctChl_Filter)
```

### ***Filtration Trials ~ ChlRmd multiple linear regression***
```{r, fig.height=20, fig.width=6, cache=TRUE}
# detailed multiple regression summary - ANOVA results
ols_regress(LM_PrctChl_Filter)
```


### ***Filtraiton Trials ~ ChlRmd Stepwise Linear Regression***
```{r, fig.height=15, fig.width=6, cache=TRUE}
# Stepwise regression
ols_step_both_p(LM_PrctChl_Filter)
# diagnosis of colinearity
# ols_coll_diag(LM_PrctChl_Filter)
```

### ***FR - Filtraiton Trials Only***
```{r LM_FR_Filter, fig.height=15, fig.width=6, cache=TRUE}
# Filtration Trials only - no Negative Controls
LM_FR_Filter <- lm(data = Filtration_only_data, L_hr_m2 ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight + Sonde_fell + Boat_wake +  Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)

# multiple regression summary
summary(LM_FR_Filter)
```

```{r, fig.height=20, fig.width=6, cache=TRUE}
# detailed multiple regression summary - ANOVA results
ols_regress(LM_FR_Filter)
```

```{r, fig.height=15, fig.width=6, cache=TRUE}
# Stepwise regression
ols_step_both_p(LM_FR_Filter)
# diagnosis of colinearity
#ols_coll_diag(LM_FR_Filter)
```

### Chl Rmd - Positive Filtration
```{r LM_PrctChl_pos_add, fig.height=15, fig.width=6, cache=TRUE}

# Positive Percent Chl removed trials only
LM_PrctChl_pos_add <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)

summary(LM_PrctChl_pos_add)
```

```{r, fig.height=15, fig.width=6, cache=TRUE}
# detailed multiple regression summary - ANOVA results
ols_regress(LM_PrctChl_pos_add)
```

```{r, fig.height=15, fig.width=6, cache=TRUE}
# Stepwise regression
ols_step_both_p(LM_PrctChl_pos_add)
# Add NPSM & Avg_OC_Ratio into model
```

```{r, fig.height=15, fig.width=6, cache=TRUE}
LM2_PrctChl_pos_add <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ 
                          NPSM + Avg_OC_Ratio)

summary(LM2_PrctChl_pos_add)
# diagnosis of colinearity
#ols_coll_diag(LM_PrctChl_pos_add)
```

```{r, fig.height=20, fig.width=6, cache=TRUE}
# detailed multiple regression summary - ANOVA results
ols_regress(LM2_PrctChl_pos_add)
```

### FR - Positive Filtration
```{r LM_FR_pos, fig.height=15, fig.width=6, cache=TRUE}

# Positive Percent Chl removed trials only
LM_FR_pos <- lm(data = Filtration_pos_data, L_hr_m2 ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)

summary(LM_FR_pos)
```

```{r, fig.height=20, fig.width=6, cache=TRUE}
# detailed multiple regression summary - ANOVA results
ols_regress(LM_FR_pos)
```

```{r, fig.height=15, fig.width=6, cache=TRUE}
# Stepwise regression
ols_step_both_p(LM_FR_pos)
# diagnosis of colinearity
#ols_coll_diag(LM_FR_pos)
```

> NPSM is the only variable added in after stepwise 

### ***Chl Rmd - Deanza - Filtration Trials***
```{r LM_ChlRmd_NPD_filter, fig.height=15, fig.width=6, cache=TRUE}
LM_ChlRmd_NPD_all <- lm(data = Deanza_Filter_data, pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)
# not enough degrees of freedom 
```

```{r, fig.height=15, fig.width=6, cache=TRUE}
ols_step_both_p(LM_ChlRmd_NPD_all)
# diagnosis of colinearity
#ols_coll_diag(LM_ChlRmd_NPD_all)
```

```{r LM2_ChlRmd_NPD_all, fig.height=15, fig.width=6, cache=TRUE}
LM2_ChlRmd_NPD_all <- lm(data = Deanza_data_all, pcnt_Chl_rmvd ~ Sal_ppt_Up)
summary(LM2_ChlRmd_NPD_all)
```

```{r, fig.height=20, fig.width=6, cache=TRUE}
ols_regress(LM2_ChlRmd_NPD_all)
```

> Not sure stepwise regression is working here

### ***FR - Deanza - Filtration Trials***
```{r LM_FR_NPD_filter, fig.height=15, fig.width=6, cache=TRUE}
LM_FR_NPD_filter <- lm(data = Deanza_Filter_data, L_hr_m2 ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)
# not enough degrees of freedom
```

```{r, fig.height=15, fig.width=6, cache=TRUE}
ols_step_both_p(LM_FR_NPD_filter)
# diagnosis of colinearity
#ols_coll_diag(LM_FR_NPD_filter)
```

### ***Chl Rmd - Deanza - Positive Filtration***
```{r LM_ChlRmd_NPD_PosFilter, fig.height=15, fig.width=6, cache=TRUE}
LM_ChlRmd_NPD_PosFilter <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)
# not enough degrees of freedom 
```

```{r, fig.height=15, fig.width=6, cache=TRUE}
ols_step_both_p(LM_ChlRmd_NPD_PosFilter)
# diagnosis of colinearity
#ols_coll_diag(LM_ChlRmd_NPD_PosFilter)
```

### ***FR - Deanza - Positive Filtration***
```{r LM_FR_NPD_Posfilter, fig.height=15, fig.width=6, cache=TRUE}
LM_FR_NPD_Posfilter <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~
                         # site logic variables - SR not included - break model to include all sites
                         NPD + NPSM + MB + 
                         # Field notes logic variables
                         Wind + G_upstream +  Daylight +  Sonde_fell + Boat_wake + Algae +
                         # Quantatative variables
                         Temp_C_Up + Sal_ppt_Up + Turbidity_NTU_Up + Chl_ug_L_Up +
                         avg_depth_cm + d_bw_sondes_m + avg_m_hr + Avg_OC_Ratio)
# not enough degrees of freedom
```

```{r eval=FALSE, fig.height=15, fig.width=6, cache=TRUE, include=FALSE}
ols_step_both_p(LM_FR_NPD_Posfilter)
# diagnosis of colinearity
#ols_coll_diag(LM_FR_NPD_Posfilter)

##### Lots of errors #########
```

Filter & TPM
=====================================

### ***Filtration by site (Filtration Trials only)***
```{r FR_ChlRmd_Filter, fig.height=5, fig.width=12, cache=TRUE}
# Filtration_only_data defined in setup

FR_box <- ggplot((Filtration_only_data), aes(Site, L_hr_m2)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Hab_FR_Label)

Chl_Rmd_box <- ggplot(Filtration_only_data, aes(Site, pcnt_Chl_rmvd)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Prt_Chl_Label)

grid.arrange(FR_box, Chl_Rmd_box, nrow = 1)

```

### ***Filtration by site (Positive values only)*** 
```{r FR_ChlRmd_TPM_posFilter, fig.height=5, fig.width=12, cache=TRUE}
# Filtration_pos_data defined in setup

FR_TPM_box_pos <- ggplot((Filtration_pos_data), aes(Site, L_hr_m2)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Hab_FR_Label,
       title = 'Positive L/hr/m^2 only')

Chl_Rmd_box_pos <- ggplot((Filtration_pos_data), aes(Site, pcnt_Chl_rmvd)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Prt_Chl_Label,
       title = 'Positive % Chl Rmd only')

grid.arrange(FR_TPM_box_pos, Chl_Rmd_box_pos, nrow = 1)
```

### ***Filtration by TPM (Filtration Trials only)***
```{r, Filter by TPM filter only, fig.height=5, fig.width=12, cache=TRUE}
FR_TPM_graph <- ggplot((Filtration_only_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_TPM_graph <- ggplot((Filtration_only_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_TPM_graph, Chl_Rmd_TPM_graph, nrow = 1)
```

### ***FR ~ TPM Linear Model***
```{r LM FR x TPM, fig.height=6, fig.width=6, cache=TRUE}
FR_TPM_lm <- lm(data = Filtration_only_data, L_hr_m2 ~ Avg_TPM)
#summary(FR_TPM_lm)
ols_regress(FR_TPM_lm)
```

### ***ChlRmd ~ TPM Linear Model***
```{r LM ChlRmd x TPM, fig.height=6, fig.width=6, cache=TRUE}
ChlRmd_TPM_lm <- lm(data = Filtration_only_data, pcnt_Chl_rmvd ~ Avg_TPM)
#summary(ChlRmd_TPM_lm)
ols_regress(ChlRmd_TPM_lm)
```

### ***Filtration vs TPM (Positive Filtration Trials only)***
```{r , fig.height=5, fig.width=12, cache=TRUE}
FRPos_TPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label,
       title = 'Pos Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_RmdPos_TPM_graph <- ggplot((Filtration_pos_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'Pos Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FRPos_TPM_graph, Chl_RmdPos_TPM_graph, nrow = 1)
```

### ***FR Pos ~ TPM Linear Model***
```{r, fig.height=6, fig.width=6, cache=TRUE}
FRPos_TPM_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Avg_TPM)
#summary(FR_TPM_lm)
ols_regress(FRPos_TPM_lm)
```

### ***Log FR Pos ~ Log TPM Linear Model***
```{r, fig.height=6, fig.width=6, cache=TRUE}
logFRPos_logTPM_lm <- lm(data = Filtration_pos_data, log(L_hr_m2) ~ log(Avg_TPM))
#summary(FR_TPM_lm)
ols_regress(logFRPos_logTPM_lm)
```

> Doesn't not help R^2 or significance.

### ***ChlRmd Pos ~ TPM Linear Model***
```{r, fig.height=6, fig.width=6, cache=TRUE}
ChlRmdPos_TPM_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Avg_TPM)
#summary(ChlRmdPos_TPM_lm)
ols_regress(ChlRmdPos_TPM_lm)
```

### ***Log ChlRmd Pos ~ Log TPM Linear Model***
```{r, fig.height=6, fig.width=6, cache=TRUE}
logChlRmdPos_logTPM_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_TPM))
#summary(ChlRmdPos_TPM_lm)
ols_regress(logChlRmdPos_logTPM_lm)
```

> Not huge difference between regular and log transformed. Keep trying transformations? 

### ***Deanza only Filtration vs TPM***
```{r NPD_FR_TPM_graph, fig.height=5, fig.width=12, cache=TRUE}
NPD_FR_TPM_graph <- ggplot((Deanza_Filter_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  # geom_abline(aes(intercept=0, slope=1)) +
  #scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmd_TPM_graph <- ggplot((Deanza_Filter_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  # geom_abline(aes(intercept=0, slope=1)) +
  #scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(NPD_FR_TPM_graph, NPD_ChlRmd_TPM_graph, nrow = 1)
```

### ***Deanza Filter - FR ~ TPM***
```{r, fig.height=6, fig.width=6}
NPD_FR_TPM_lm <- lm(data = Deanza_Filter_data, L_hr_m2 ~ Avg_TPM)
ols_regress(NPD_FR_TPM_lm)
```

### ***Deanza Filter - ChlRmd ~ TPM***
```{r, fig.height=6, fig.width=6}
NPD_ChlRmd_TPM_lm <- lm(data = Deanza_Filter_data, pcnt_Chl_rmvd ~ Avg_TPM)
ols_regress(NPD_ChlRmd_TPM_lm)
```

> Did not do further transformations, didn't look like obvious pattern to investigate

### ***Deanza only Positive Filtration vs TPM***
```{r NPD_FRPos_TPM_graph, fig.height=5, fig.width=12, cache=TRUE}
NPD_FRPos_TPM_graph <- ggplot((Deanza_PosFilter_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  # geom_abline(aes(intercept=0, slope=1)) +
  #scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_TPM_graph <- ggplot((Deanza_PosFilter_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  # geom_abline(aes(intercept=0, slope=1)) +
  #scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label) +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(NPD_FRPos_TPM_graph, NPD_ChlRmdPos_TPM_graph, nrow = 1)
```

### ***Deanza Positive Filter - FR ~ TPM***
```{r, fig.height=6, fig.width=6, cache=T}
NPD_PosFR_TPM_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Avg_TPM)
ols_regress(NPD_PosFR_TPM_lm)
```

### ***Deanza Postive Filter - ChlRmd ~ TPM***
```{r, fig.height=6, fig.width=6, cache=T}
NPD_PosChlRmd_TPM_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Avg_TPM)
ols_regress(NPD_PosChlRmd_TPM_lm)
```

> Did not do further transformations, didn't look like obvious pattern to investigate

OC 
=====================================

### ***Filtration vs OC***
```{r FR vs OC, fig.height=5, fig.width=12, cache=TRUE}
FR_OC_graph <- ggplot(Filtration_only_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_OC_graph <- ggplot(Filtration_only_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FR_OC_graph, Chl_Rmd_OC_graph, nrow = 1)
```

### ***FR by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FR_OC_lm <- lm(data = Filtration_only_data, L_hr_m2 ~ Avg_OC_Ratio)
ols_regress(FR_OC_lm)
```

### ***ChlRmd by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmd_OC_lm <- lm(data = Filtration_only_data, pcnt_Chl_rmvd ~ Avg_OC_Ratio)
ols_regress(ChlRmd_OC_lm)
```

### ***Filter Positive vs OC***
```{r FRPos vs OC, fig.height=5, fig.width=12, cache=TRUE}
FRPos_OC_graph <- ggplot(Filtration_pos_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_RmdPos_OC_graph <- ggplot(Filtration_pos_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FRPos_OC_graph, Chl_RmdPos_OC_graph, nrow = 1)
```

### ***FR Pos by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_OC_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Avg_OC_Ratio)
ols_regress(FRPos_OC_lm)
```

### ***ChlRmd Pos by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_OC_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Avg_OC_Ratio)
ols_regress(ChlRmdPos_OC_lm)
```

> Significant Avg_OC_Ratio * ChlRmd

### ***Log Transformation - Positive ChlRmd vs OC***
```{r LogChlRmdPos_OC, fig.height=5, fig.width=12, cache=TRUE}
logChl_RmdPos_logOC_graph <- ggplot(Filtration_pos_data, aes(log(Avg_OC_Ratio), log(pcnt_Chl_rmvd))) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'nlog Organic Content of Seston (fraction)',
       y = paste("nlog", Prt_Chl_Label),
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
```

### ***ChlRmd Pos by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logChlRmdPos_logOC_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Avg_OC_Ratio))
ols_regress(logChlRmdPos_logOC_lm)
```

> Not a big difference between regular and log transformed model

### ***Deanza Filter Only - FR by OC***
```{r Deanza_Filter_OC, fig.height=5, fig.width=12, cache=TRUE}
FR_OC_NPD_graph <- ggplot(Deanza_Filter_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'Newport Deanza Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_OC_NPD_graph <- ggplot(Deanza_Filter_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'Newport Deanza Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FR_OC_NPD_graph, Chl_Rmd_OC_NPD_graph, nrow = 1)
```

### ***Deanza FR ~ OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FR_OC_NPD_lm <- lm(data = Deanza_Filter_data, L_hr_m2 ~ Avg_OC_Ratio)
ols_regress(FR_OC_NPD_lm)
```

### ***Deanza ChlRmd ~ OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmd_OC_NPD_lm <- lm(data = Deanza_Filter_data, pcnt_Chl_rmvd ~ Avg_OC_Ratio)
ols_regress(ChlRmd_OC_NPD_lm)
```

### ***Deanza FR Positive ~ OC***
```{r Deanza_Filter_Pos_OC, fig.height=5, fig.width=12, cache=TRUE}
FRPos_OC_NPD_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'Newport Deanza Positive Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_RmdPos_OC_NPD_graph <- ggplot(Deanza_PosFilter_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'Newport Deanza Positive Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FRPos_OC_NPD_graph, Chl_RmdPos_OC_NPD_graph, nrow = 1)
```

### ***Deanza FR Positive by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_OC_NPD_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Avg_OC_Ratio)
ols_regress(FRPos_OC_NPD_lm)
```

### ***Deanza ChlRmd Positive by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_OC_NPD_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Avg_OC_Ratio)
ols_regress(ChlRmdPos_OC_NPD_lm)
```

### ***Log Deanza ChlRmd Positive by OC Linear Model***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_logOC_NPD_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Avg_OC_Ratio))
ols_regress(ChlRmdPos_logOC_NPD_lm)
```

> Only slight improvement by log(OC)

Temperature
=====================================

### ***Temperature ***
```{r Filter_Temp, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}
FR_Temp <- ggplot(Filtration_only_data, aes(Temp_C_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_Temp <- ggplot(Filtration_only_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

FR_pos_Temp <- ggplot(Filtration_pos_data, aes(Temp_C_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Temp <- ggplot(Filtration_pos_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'Positive ChlRmd') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_Temp, Chl_Rmd_Temp, FR_pos_Temp, Chl_Rmd_pos_Temp, nrow = 2)
```

### ***FR ~ Temp LM (All Filter)***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FR_temp_lm <- lm(data = Filtration_only_data, L_hr_m2 ~ Temp_C_Up)
ols_regress(FR_temp_lm)
```

### ***ChlRmd ~ Temp LM (All Filter)***
```{r,fig.height=6, fig.width=6, cache =TRUE}
ChlRmd_temp_lm <- lm(data = Filtration_only_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(ChlRmd_temp_lm)
```

### ***FR Positive ~ Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_temp_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(FRPos_temp_lm)
```

### ***ChlRmd Positive ~ Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_temp_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(ChlRmdPos_temp_lm)
```

### ***Deanza Filtration - Temperature***
```{r NPD_Filter_Temp, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}
NPD_FR_Temp <- ggplot(Deanza_Filter_data, aes(Temp_C_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Hab_FR_Label,
       title = 'Deanza Filter Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_Chl_Rmd_Temp <- ggplot(Deanza_Filter_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'Deanza Filter Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_FRPos_Temp <- ggplot(Deanza_PosFilter_data, aes(Temp_C_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Hab_FR_Label,
       title = 'Deanza Positive Filter Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_Chl_RmdPos_Temp <- ggplot(Deanza_PosFilter_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'Deanza Positive Filter Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(NPD_FR_Temp, NPD_Chl_Rmd_Temp , NPD_FRPos_Temp, NPD_Chl_RmdPos_Temp, nrow = 2)
```

### ***Deanza FR ~ Temp LM (All Filter)***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FR_temp_lm <- lm(data = Deanza_Filter_data, L_hr_m2 ~ Temp_C_Up)
ols_regress(NPD_FR_temp_lm)
```

### ***Deanza ChlRmd ~ Temp LM (All Filter)***
```{r,fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmd_temp_lm <- lm(data = Deanza_Filter_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(NPD_ChlRmd_temp_lm)
```

### ***Deanza FR Positive ~ Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FRPos_temp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(NPD_FRPos_temp_lm)
```

### ***Deanza ChlRmd Positive ~ Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_temp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Temp_C_Up)
ols_regress(NPD_ChlRmdPos_temp_lm)
```

### ***Deanza ChlRmd Positive ~ Log Temp LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_logtemp_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ log(Temp_C_Up))
ols_regress(NPD_ChlRmdPos_logtemp_lm)
```

> Log transforming does not help fit

Salinity
=====================================

### ***Filtration - Salinity***
```{r Filter_Salinity, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}
FR_Sal <- ggplot(Filtration_only_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_Sal <- ggplot(Filtration_only_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

FR_pos_Sal <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'Positive FR only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Sal <- ggplot(Filtration_pos_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_Sal, Chl_Rmd_Sal, FR_pos_Sal, Chl_Rmd_pos_Sal, nrow = 2)
```

### ***FR ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FR_Sal_lm <- lm(data = Filtration_only_data, L_hr_m2 ~ Sal_ppt_Up)
ols_regress(FR_Sal_lm)
```

### ***ChlRmd ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmd_Sal_lm <- lm(data = Filtration_only_data, pcnt_Chl_rmvd ~ Sal_ppt_Up)
ols_regress(ChlRmd_Sal_lm)
```

### ***FR Pos ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_Sal_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Sal_ppt_Up)
ols_regress(FRPos_Sal_lm)
```

### ***ChlRmd Pos ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Sal_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Sal_ppt_Up)
ols_regress(ChlRmdPos_Sal_lm)
```

> Salinity almost significant predictor of ChlRmd (Positive Filter)

###***Log ChlRmd Pos - Log Salinity***
```{r}
logChlRmd_pos_logSal_graph <- ggplot(Filtration_pos_data, aes(log(Sal_ppt_Up), log(pcnt_Chl_rmvd))) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = expression('log'[n]*'Salinity Upstream (ppt)'),
       y = paste("log " , Prt_Chl_Label),
       title = 'Positive Chl Removed Only') +
  stat_poly_eq(formula = x_y_formula, parse = TRUE)

plot(logChlRmd_pos_logSal_graph)
```

### ***ChlRmd Pos ~ log Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logChlRmdPos_logSal_lm <- lm(data = Filtration_pos_data, log(pcnt_Chl_rmvd) ~ log(Sal_ppt_Up))
ols_regress(logChlRmdPos_logSal_lm)
```

> Log(Y) = Log(k) + Log(X^k) - How to pull out equation for regression? 

### ***Deanza only Filtration - Salinity***
```{r NPD_Filter_Salinity, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}
NPD_FR_Salinity <- ggplot(Deanza_Filter_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'NPD Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmd_Salinity <- ggplot(Deanza_Filter_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'NPD Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
NPD_FRPos_Salinity <- ggplot(Deanza_PosFilter_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'NPD Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Salinity <- ggplot(Deanza_PosFilter_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'NPD Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(NPD_FR_Salinity, NPD_ChlRmd_Salinity, 
             NPD_FRPos_Salinity, NPD_ChlRmdPos_Salinity, nrow = 2)
```

### ***Deanza FR ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FR_Sal_lm <- lm(data = Deanza_Filter_data, L_hr_m2 ~ Sal_ppt_Up)
ols_regress(NPD_FR_Sal_lm)
```

### ***Deanza ChlRmd ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmd_Sal_lm <- lm(data = Deanza_Filter_data, pcnt_Chl_rmvd ~ Sal_ppt_Up)
ols_regress(NPD_ChlRmd_Sal_lm)
```

### ***Deanza Pos FR ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FRPos_Sal_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Sal_ppt_Up)
ols_regress(NPD_FRPos_Sal_lm)
```

### ***Deanza Pos ChlRmd ~ Salinity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_Sal_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Sal_ppt_Up)
ols_regress(NPD_ChlRmdPos_Sal_lm)
```

Chlorophyll
=====================================

### ***Filtration - Chlorophyll***
```{r Filter_Chl, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}
FR_Chl <- ggplot(Filtration_only_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_Chl <- ggplot(Filtration_only_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

FR_pos_Chl <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Chl <- ggplot(Filtration_pos_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_Chl, Chl_Rmd_Chl, FR_pos_Chl, Chl_Rmd_pos_Chl, nrow = 2)
```

### FR ~ Chl LM
```{r, fig.height=6, fig.width=6, cache =TRUE}
FR_Chl_lm <- lm(data = Filtration_only_data, L_hr_m2 ~ Chl_ug_L_Up)
ols_regress(FR_Chl_lm)
```

### ChlRmd ~ Chl LM
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmd_Chl_lm <- lm(data = Filtration_only_data, pcnt_Chl_rmvd ~ Chl_ug_L_Up)
ols_regress(ChlRmd_Chl_lm)
```

### FR Pos ~ Chl LM
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_Chl_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Chl_ug_L_Up)
ols_regress(FRPos_Chl_lm)
```

### ChlRmd Pos ~ Chl LM
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Chl_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Chl_ug_L_Up)
ols_regress(ChlRmdPos_Chl_lm)
```

> Chl almost significant predictor of Chl Rmd (Pos Filter)

```{r NPD_Filter_Chl, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}
NPD_FR_Chl <- ggplot(Deanza_Filter_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label,
       title = "NPD Filtraiton") +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmd_Chl <- ggplot(Deanza_Filter_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = "NPD Filtraiton") +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_FRPos_Chl <- ggplot(Deanza_PosFilter_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label,
       title = "NPD Positive Filtraiton") +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Chl <- ggplot(Deanza_Filter_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = "NPD Positive Filtraiton") +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(NPD_FR_Chl, NPD_ChlRmd_Chl, NPD_FRPos_Chl, NPD_ChlRmdPos_Chl, nrow = 2)
```

### ***Deanza FR ~ Chl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FR_Chl_lm <- lm(data = Deanza_Filter_data, L_hr_m2 ~ Chl_ug_L_Up)
ols_regress(FR_Chl_lm)
```

### ***Deanza ChlRmd ~ Chl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmd_Chl_lm <- lm(data = Deanza_Filter_data, pcnt_Chl_rmvd ~ Chl_ug_L_Up)
ols_regress(ChlRmd_Chl_lm)
```

### ***Deanza FR Pos ~ Chl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FRPos_Chl_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Chl_ug_L_Up)
ols_regress(FRPos_Chl_lm)
```

### ***ChlRmd Pos ~ Chl LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_Chl_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Chl_ug_L_Up)
ols_regress(ChlRmdPos_Chl_lm)
```

Turbidity
=====================================

### ***Filtration - Turbidity***
```{r Filter_Turbidity, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}
FR_Turb <- ggplot(Filtration_only_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_Turb <- ggplot(Filtration_only_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

FR_pos_Turb <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Turb <- ggplot(Filtration_pos_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_Turb, Chl_Rmd_Turb, FR_pos_Turb, Chl_Rmd_pos_Turb, nrow =2)
```

### ***FR ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FR_Turb_lm <- lm(data = Filtration_only_data, L_hr_m2 ~ Turbidity_NTU_Up)
ols_regress(FR_Turb_lm)
```

### ***ChlRmd ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmd_Turb_lm <- lm(data = Filtration_only_data, pcnt_Chl_rmvd ~ Turbidity_NTU_Up)
ols_regress(ChlRmd_Turb_lm)
```

### ***FR Pos ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
FRPos_Turb_lm <- lm(data = Filtration_pos_data, L_hr_m2 ~ Turbidity_NTU_Up)
ols_regress(FRPos_Turb_lm)
```

### ***ChlRmd Pos ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ChlRmdPos_Turb_lm <- lm(data = Filtration_pos_data, pcnt_Chl_rmvd ~ Turbidity_NTU_Up)
ols_regress(ChlRmdPos_Turb_lm)
```

### ***Deanza Filtration - Turbidity***
```{r NPD_Filter_Turbidity, fig.height=10, fig.width=12, cache=TRUE, echo=FALSE}
NPD_FR_Turb <- ggplot(Deanza_Filter_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'Deanza - Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmd_Turb <- ggplot(Deanza_Filter_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Deanza - Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_FRPos_Turb <- ggplot(Deanza_PosFilter_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'Deanza - Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

NPD_ChlRmdPos_Turb <- ggplot(Deanza_PosFilter_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Deanza - Positive Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(NPD_FR_Turb, NPD_ChlRmd_Turb, NPD_FRPos_Turb, NPD_ChlRmdPos_Turb, nrow = 2)

```

### ***Deanza FR ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
ND_FR_Turb_lm <- lm(data = Deanza_Filter_data, L_hr_m2 ~ Turbidity_NTU_Up)
ols_regress(FR_Turb_lm)
```

### ***Deanza ChlRmd~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmd_Turb_lm <- lm(data = Deanza_Filter_data, pcnt_Chl_rmvd ~ Turbidity_NTU_Up)
ols_regress(ND_FR_Turb_lm)
```

### ***Deanza FR Pos ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_FRPos_Turb_lm <- lm(data = Deanza_PosFilter_data, L_hr_m2 ~ Turbidity_NTU_Up)
ols_regress(NPD_FRPos_Turb_lm)
```

### ***Deanza ChlRmd Pos ~ Turbidity LM***
```{r, fig.height=6, fig.width=6, cache =TRUE}
NPD_ChlRmdPos_Turb_lm <- lm(data = Deanza_PosFilter_data, pcnt_Chl_rmvd ~ Turbidity_NTU_Up)
ols_regress(NPD_ChlRmdPos_Turb_lm)
```

TPM X OC
=====================================

### ***TPM by OC***
```{r TPM vs OC, fig.width=8, fig.height=5, cache=TRUE}
TPM_OC <- ggplot(data = Avg_TPM_summary_table, aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  labs(x = TPM_Label, y = "Average Organic Content Ratio", title = "All Trials") + 
  theme_classic() +
  #geom_text(aes(label=Date), nudge_x = 0.007, nudge_y = 0, check_overlap = T)
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_box <- ggplot((Avg_TPM_summary_table), aes(Site, Avg_TPM)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats3, geom = "text") + # mean isn't working 
  labs(x = 'Site',
       y = TPM_Label)

OC_box <- ggplot((Avg_TPM_summary_table), aes(Site, Avg_OC_Ratio)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats3, geom = "text") + 
  labs(x = 'Site',
       y = "Average Organic Content Ratio")

grid.arrange(TPM_OC, TPM_box, OC_box, nrow = 2)
```

> All Filtration and Neg Control Trials included. Samples independent of kind of trial. Not sure why mean function isn't working on TPM boxplot

### ***All TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
OC_TPM_all_LM <- lm(data = Avg_TPM_summary_table, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_all_LM)
```

###***Log TPM All trials - OC***
```{r logTPM_OC, fig.width=8, fig.height=5, cache=TRUE}
logTPM_OC <- ggplot(data = Avg_TPM_summary_table, aes(x = log(Avg_TPM), y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  labs(x = paste("log",TPM_Label), 
       y = "Average Organic Content Ratio", 
       title = "All Trials") + 
  theme_classic() +
  #geom_text(aes(label=Date), nudge_x = 0.007, nudge_y = 0, check_overlap = T)
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(logTPM_OC)

```

### ***All logTMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
OC_logTPM_all_LM <- lm(data = Avg_TPM_summary_table, Avg_OC_Ratio ~ log(Avg_TPM))
ols_regress(OC_logTPM_all_LM)
```

### ***All logTMP ~ logOC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
logOC_logTPM_all_LM <- lm(data = Avg_TPM_summary_table, log(Avg_OC_Ratio) ~ log(Avg_TPM))
ols_regress(logOC_logTPM_all_LM)
```

### ***TPM vs OC by sites***
```{r TPM_OC_Sites, fig.height=10, fig.width=12, cache=TRUE}
TPM_OC_Deanza <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Deanza")),
                        aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Deanza") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_NPSM <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Shellmaker")), 
                     aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Shellmaker") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_SR <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "San Rafael")),
                   aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "San Rafael") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_MB <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Morro Bay")), 
                   aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Morro Bay") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(TPM_OC_Deanza, TPM_OC_NPSM, TPM_OC_SR, TPM_OC_MB, nrow = 2)
```

### ***San Rafael TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_SR <- Avg_TPM_summary_table %>% filter(Site == "San Rafael")

OC_TPM_SR_LM <- lm(data = TPM_SR, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_SR_LM)
```

### ***Morro Bay TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_MB <- Avg_TPM_summary_table %>% filter(Site == "Morro Bay")

OC_TPM_MB_LM <- lm(data = TPM_MB, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_MB_LM)
```

### ***Shellmaker TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_NPSM <- Avg_TPM_summary_table %>% filter(Site == "Shellmaker")

OC_TPM_NPSM_LM <- lm(data = TPM_NPSM, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_NPSM_LM)
```

### ***Deanza TMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

OC_TPM_NPD_LM <- lm(data = TPM_NPD, Avg_OC_Ratio ~ Avg_TPM)
ols_regress(OC_TPM_NPD_LM)
```

### ***Deanza logTMP ~ OC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

OC_logTPM_NPD_LM <- lm(data = TPM_NPD, Avg_OC_Ratio ~ log(Avg_TPM))
ols_regress(OC_logTPM_NPD_LM)
```

### ***Deanza logTMP ~ logOC***
```{r, fig.height=6, fig.width=6, cache =TRUE}
TPM_NPD <- Avg_TPM_summary_table %>% filter(Site == "Deanza")

logOC_logTPM_NPD_LM <- lm(data = TPM_NPD, log(Avg_OC_Ratio) ~ log(Avg_TPM))
ols_regress(logOC_logTPM_NPD_LM)
```

DTW X Shell length
=====================================

### ***Newport Olympia Shell length vs DTW***
```{r Oly_DTW_Shell_length, cache=TRUE, echo=FALSE}
#Olympia DTW predicted by Shell Length - Newport, CA
# All excavation quadrat samples processed to date aggregated 
NPD_oly <- NPD_density %>% 
  filter(species == "O. lurida") %>% 
  drop_na() %>% 
  as_tibble() 

Oly_shell_DTW <- ggplot(NPD_oly, aes(length_mm, tissue_dry_weight_g)) +
  geom_smooth(method = lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'With outlier (bad data)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top") +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

plot(Oly_shell_DTW)
```

> 1) Outlier probably sample processing error or error in data entry. 2) Negative DTW data point, doesn't make sense- remove?

### ***DTW Shell length Outlier analysis (mean -+ SD * 2.2)***
```{r Oly_DTW_Shell_length_outier_removed, cache=TRUE}
# Remove outlier and negative DTW value
NPD_oly_outRmd <- NPD_oly %>%
  mutate(DTW_outlier = find_outlier(NPD_oly$tissue_dry_weight_g)) %>% 
  filter(DTW_outlier == FALSE & tissue_dry_weight_g >= 0)

# Graph with outliers removed
Oly_shell_DTW_rm_out <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  geom_smooth(method=lm, formula = x_y_formula, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +#aes(color = Site)) +
  #scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
 # scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Outlier removed (outside mean +- 2.2 SD)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom") +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

plot(Oly_shell_DTW_rm_out)
```

> Shell length explains 49% of Dry Tissue Weight. Compare this relationship [Gray unpublished cited in Blake & zu Ermgassen 2015] (Yaquina Bay) --> DTW = 6x10e-6 * SH^3.06

> Remove negative DTW data point. Doesn't make sense

### ***Linear model without outlier***
```{r Linear_model_DTW_length, cache=TRUE}
Oly_DTW_lm <- lm(data = NPD_oly_outRmd,
                         tissue_dry_weight_g ~ length_mm)

summary(Oly_DTW_lm)
```

### ***Log Transform DTW Graph***
```{r, cache=TRUE}
Oly_shell_logDTW <- ggplot(NPD_oly_outRmd, aes(length_mm, log(tissue_dry_weight_g))) +
  geom_smooth(method=lm, formula = x_y_formula, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +#aes(color = Site)) +
  #scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
 # scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = 'Shell Length (mm)',
       y = expression('Log'[n]*' Dry Tissue Weight (g)'),
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Outlier removed (outside mean +- 2.2 SD)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom") +
  stat_quadrant_counts(quadrants = 0L, label.x = "left", 
                       aes(label = sprintf("%i observations", stat(count))))

plot(Oly_shell_logDTW)
```

> Is that the correct line equation?? 

### ***Log transform DTW***
```{r, cache=TRUE}
Oly_LogDTW_lm <- lm(data = NPD_oly_outRmd,
                    log(tissue_dry_weight_g) ~ length_mm)

summary(Oly_LogDTW_lm)
```

> Explains 67% of variation. length significant predictor of log(DTW)

### ***Quadratic model x^2***
```{r Quad_model_DTW_length_2, cache=TRUE}
#Quadratic model using length^2
length_2 <- NPD_oly_outRmd$length_mm^2

Oly_DTW_Quad <- lm(data = NPD_oly_outRmd,
                         tissue_dry_weight_g ~ length_mm + length_2)
summary(Oly_DTW_Quad)
```

> Not sure if this is the correct way to build this model. summary shows no significance in either variable. DTW = -1.468e-02 + https://www.theanalysisfactor.com/r-tutorial-4/

### ***Quadratic model Graph***
```{r Quad_model_DTW_graph, cache=TRUE}
NPD_oly_outRmd %<>% 
  mutate(Quad_model = unname(predict(Oly_DTW_Quad)))
  # Could use predict(Oly_DTW_Quad, interval = 'confidence') to create confidence intervals columns
  # column1 = fit, column2 = lwr, column3 = upr 
  # use cbind instead of mutate 
  # cars.predict <- cbind(cars, predict(cars.model, interval = 'confidence'))

Oly_DTW_Quad_graph <- ggplot(NPD_oly_outRmd, aes(length_mm, tissue_dry_weight_g)) +
  geom_point() +
  geom_line(aes(length_mm, Quad_model)) +
  theme_classic() +
  labs(title = 'Olympia Oyster DTW predicted by (Shell Length)^2 - Newport, CA') +
  # label graph with R^2 adj value. won't work with quadratic equation
  stat_poly_eq(aes(label = ..adj.rr.label..), formula = x2_y_formula, 
               parse = TRUE) 
plot(Oly_DTW_Quad_graph)
```

### ***Quadratic model x^3***
```{r Quad_model_DTW_length_3, cache=TRUE}
#Quadratic model using length^2
length_3 <- NPD_oly_outRmd$length_mm^3

Oly_DTW_Quad <- lm(data = NPD_oly_outRmd,
                         tissue_dry_weight_g ~ length_mm + length_3)
summary(Oly_DTW_Quad)
```

> doesn't fit better

### ***Total Wet Weight vs Dry Tissue Weight***
```{r, cache=TRUE}
Oly_TWW_DTW<- ggplot(NPD_oly, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
   geom_point() +
 # scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = 'Total wet weight (g)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Total Wet Weight - Newport, CA') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")
plot(Oly_TWW_DTW)
```

### ***TWW vs DTW (remove outlier)***
```{r, cache=TRUE}
# use DTW outlier data to plot graph
Oly_TWW_DTW_rm_out <- ggplot(NPD_oly_outRmd, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = 'Total wet weight (g)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Total Wet Weight - Newport, CA') +

  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(Oly_TWW_DTW_rm_out)
```

> Gray and Langdon (2017): "Unless explicitly mentioned, DTW of experimental oysters was estimated using the species-specific allometric relationship between DTW and total wet weight (TWW), which were determined in preliminary analysis (O. lurida: DTW = 0.0044TWW  0.043, R2 =0.93, F1,32 =78.80, p value <0.0001; C. gigas: DTW = 0.039TWW  0.06, R2 =0.89, F1,29 = 225.97, p value <0.0001).

### ***Linear model without outlier***
```{r, cache=TRUE}
Oly_TWW_DTW_lm_rm_out <- lm(data = NPD_oly_outRmd,
                         tissue_dry_weight_g ~ total_wet_weight_g)

summary(Oly_TWW_DTW_lm_rm_out)
```

### ***Log(TWW) vs DTW*** 
```{r, cache=TRUE}
# use DTW outlier data to plot graph
Oly_logTWW_DTW <- ggplot(NPD_oly_outRmd, aes(log(total_wet_weight_g), log(tissue_dry_weight_g))) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point() +
  #scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = expression('Log'[n]*" Total wet weight (g)"),
       y = expression('Log'[n]*'Dry Tissue Weight (g)'),
       title = 'Olympia Oyster DTW predicted by Total Wet Weight - Newport, CA') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(Oly_logTWW_DTW)
```

### ***Log DTW X  Log TWW LM***
```{r, cache=TRUE}
Oly_TWW_DTW_log_LM <- lm(data = NPD_oly_outRmd %>% filter(total_wet_weight_g > 0), 
                         log(tissue_dry_weight_g) ~ log(total_wet_weight_g))
summary(Oly_TWW_DTW_log_LM)
```

Up & Down Chl
=====================================

### ***Facet Plots***
```{r Bar_Graphs_up_vs_down, cache=TRUE}
Bar_up_down_data <- Master_analysis_table %>%
  select(Experiment, Date, Site, Chl_ug_L_Up, Chl_ug_L_Down) %>%
  rename(Upstream = Chl_ug_L_Up, Downstream = Chl_ug_L_Down) %>%  
  gather(Upstream, Downstream, key = Position, value = Chl_ug_L) %>% 
  mutate(Position = fct_relevel(Position, 'Upstream', 'Downstream')) %>% 
  mutate(Site = fct_relevel(Site, 'Deanza', 'Shellmaker', 'San Rafael', 'Morro Bay')) %>% 
  mutate(Site_exp_date = paste(Site, Experiment,
                                     Date,
                                     sep = ' ')) %>% 
  mutate(Exp_Date = paste(Experiment, Date, sep = ' ')) %>% 
  arrange(Site, mdy(Date))

#Bar_up_down_data$Position <- as.factor(Bar_up_down_data$Position)

Paired_bar_chl_graph <- ggplot(data = Bar_up_down_data, aes(x = Site_exp_date, y = Chl_ug_L, fill = Position)) +
    geom_bar(stat="identity", position = "dodge") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    facet_grid(~ Site, scales = "free", space = "free") + #'free' allows axis b/w sites uneaven
    geom_bar(data = (Bar_up_down_data %>%
                       filter(!Experiment %in% c('Filtration'))),
             color = "grey22",
             stat="identity",
             position = "dodge") +
    labs(x = 'Experiment', y = 'Chlorophyl (ug/L)')

plot(Paired_bar_chl_graph)
```

### ***Graphs using grid.arrange()***
```{r Bar_Graphs_up_vs_down_grid.arrange, cache=TRUE}
############## Try 2 ####### make separate graphs, combine using grid.arrange()

##### Can't figure out how to properly label x axis. Works with Exp_Date, but can't shorten without messing up data:label pairs. Can't spend more time on this right now. come back if time -AM 2020_3_3

NPD_bar_data <- Bar_up_down_data %>% 
  filter(Site == "Deanza") %>% 
  mutate(graph_Label = ifelse(grepl("^Filtration", Exp_Date), str_replace(Exp_Date, "Filtration ", ""),
                             str_replace(Exp_Date, "^Neg Control .", "")))

NPD_bar_graph <- ggplot(data = NPD_bar_data, aes(x = Exp_Date, y = Chl_ug_L, 
                                                 fill = Position)) +
    geom_col(position = position_dodge(width = 0.9, preserve = "single")) +
    geom_col(data = (NPD_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.x = element_blank(),
          legend.position = c(0.9, 0.8),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(y = 'Chlorophyll a (ug/L)', title = "Newport Deanza") +
  # This labels the x-axis
    #scale_x_discrete(labels = Exp_Date) +
    ylim(0, 8)
NPD_bar_graph

NPSM_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'Shellmaker')

NPSM_bar_graph <- ggplot(data = NPSM_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (NPSM_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "Newport Shellmaker") +
    # scale_x_discrete(labels = NPSM_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE) 

MB_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'Morro Bay')

MB_bar_graph <- ggplot(data = MB_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (MB_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "Morro Bay") +
   # scale_x_discrete(labels = MB_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE)

SR_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'San Rafael')

SR_bar_graph <- ggplot(data = SR_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (SR_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "San Rafael") +
    #scale_x_discrete(labels = SR_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE)

Chl_graphs <- list(NPD_bar_graph, NPSM_bar_graph, SR_bar_graph, MB_bar_graph) 
all_chl_graphs <- grid.arrange(grobs = Chl_graphs,
             widths = c(1,1,1,1,1,1,1,1,1,1,1,1,1,1),
             layout_matrix = rbind(c(NA,1,1,1,1,1,1,1,1,1,1,1,1, NA),
                                   c(2,2,2,2,2,3,3,3,3,3,4,4,4,4)))
plot(all_chl_graphs)
#ggsave("Insitu_Filter_up_vs_down_all_sites.png", all_chl_graphs)
```

Bivalve Density
=====================================

### ***Bivalve Density***
```{r Bivalve_Density, fig.height=6, fig.width=8, cache=TRUE}
# read in bivalve density data from cleaned data file
Bivalve_Den_data <- fread(file.path(Bivalve_output_directory, "Bivalve_Density_summary.csv"))

# replace NAs with 0s
Bivalve_Den_data[is.na(Bivalve_Den_data)] <- 0

Bivalve_Den_data <- Bivalve_Den_data %>% 
  # move species from individual columns to a single column with new density column to contain data
  pivot_longer(c(Adula_diegensis_m2, Musculista_senhousia_m2,Mytilus_galloprovincialis_m2,
                 Ostrea_lurida_m2, Crassostrea_gigas_m2,Argopecten_ventricosa_m2, 
                 Geukensia_demissa_m2, Crassostrea_gigas_m2), 
               names_to = "Species", 
               values_to =  "individuals_m2") %>% 
  # remove "_m2" from species names in Species column
  mutate(Species = str_replace(Species, "_m2", ""))

#Reorder levels of Site factor - display North to South
order_by_site <- c("San Rafael", "Morro Bay", "Shellmaker", "Deanza") 
Bivalve_Den_data <- arrange(transform(Bivalve_Den_data, Site = factor(Site,levels = order_by_site)), Site)

# wes_palettes # lists all current palattes 
# Color palette for Species - Royal2, Darjeeling2, Cavalcanti1, BottleRocket2, IsleofDogs1
Species_colors <- rev(wes_palette("IsleofDogs1", 7, type = c("continuous")))

# Stacked bar graph
Bivalve_Den_graph <- ggplot(Bivalve_Den_data, aes(Site)) + 
  geom_col(aes(x = Site, y = individuals_m2, fill = Species)) +
  geom_text(aes(label = round(Bivalve_den_m2,0), y = Bivalve_den_m2), 
            vjust = -0.5) +
  theme_classic() +
  scale_fill_manual(values = Species_colors) +
  scale_y_continuous(breaks = seq(0, max(Bivalve_Den_data$Bivalve_den_m2), by = 500)) +
  labs(y = expression("Individuals per m"^2))
  
Bivalve_Den_graph
```

> Data for each site is from a single survey

### Biomass estimate by Site
```{r}
##### Estimate Biomass per site here with equations
  
```
