---
title: "In situ Filtration Analysis Graphs"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: yeti
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(data.table)
library(magrittr)
library(lubridate) # dealing with time and dates
library(ggplot2)
library(ggthemes) # theme_classic() for graphs
library(stringr)
library(hms)
library(viridisLite)
library(forcats)
library(gridExtra)
library(ggpmisc) # package for adding line equation and R^2 to plots
library(viridis) # Color palette for Restoration Area - Options: magma , inferno, plasma, viridis, cividis
library(scales)
library(cowplot) # for arranging multiple plots into a single figure
library(wesanderson)

# source functions 
source("functions.R")
# define output directory
output_directory = "./output"
# create output directories (same as Insitu_Filtraiton_Analysis_script.Rmd)
createOutputDirectories()

# Read in Data
Master_analysis_table <- fread(file.path('./output/4_Filtration_Calculations/Filtration_Summary', "Master_Filtration_analysis_table.csv"))
Avg_TPM_summary_table <- fread(file.path('./output/5_TPM_OC_Summary', "Avg_TPM_summary_table.csv"))
Density_directory = "./Data/bivalve_density_community"
NPD_density = fread(file.path(Density_directory, "Insitu_Filter_NPD_bivalve_biomass_data.csv"))

# Remove San Diego filtration trial - not applicable to this analysis - different experimental set up
Master_analysis_table <- Master_analysis_table %>% 
  filter(!Site %in% c("San Diego"))

# Basic linear model formula to display on plots
x_y_formula <- y ~ x 

# Order Sites by Latitude
site_by_lat <- c("San Rafael", "Morro Bay", "Shellmaker", "Deanza") 

# transform Site variable to factor and arange by Latitude
Master_analysis_table <- arrange(transform(Master_analysis_table, Site = factor(Site,levels = site_by_lat)), Site)

# Assign colors to each Site
viridis(4)
Site_colors <- c("San Rafael" = "#440154FF",
                 "Morro Bay" = "#31688EFF",
                 "Shellmaker" = "#35B779FF",
                 "Deanza" = "#FDE725FF")

# Labels for graphs 
Hab_FR_Label <- expression('Habitat Filtration Rate (L/hr/m'^2*')')
Prt_Chl_Label <- expression(paste('Percent Chlorophyll ', alpha, ' Removed'))
Chl_ugL_Label <- expression(paste("Chlorophyll ", alpha, " (", mu, "g/L) "))
TPM_Label <- expression(paste('Total Particulate Matter (', mu,"g/L)"))

# function for number of samples - display on graph
n_mean_stats <- function(x){
  return(tibble(y = max(x) * 0.95, 
                    label = paste("n = ",length(x), "\n",
                                  'mean =', round(mean(x), 1), '\n')
                )
         )
}
```

Chl % Removed - LM
=====================================
### LM - excluding San Rafael logic variable
```{r LM_Prct_Chl_All, fig.height=15, fig.width=6, cache=TRUE}

LM_PrctChl_All <- lm(Master_analysis_table$pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - would break model
                         Master_analysis_table$NPD + Master_analysis_table$NPSM + Master_analysis_table$MB + 
                         # Filtration Trial - T or F
                         Master_analysis_table$Filter_trial +
                         # Field notes logic variables
                         Master_analysis_table$Wind + Master_analysis_table$G_upstream + Master_analysis_table$Daylight +
                         Master_analysis_table$Sonde_fell + Master_analysis_table$Boat_wake + Master_analysis_table$Algae +
                         # Quantatative variables
                         Master_analysis_table$Temp_C_Up + Master_analysis_table$Sal_ppt_Up +
                         Master_analysis_table$Turbidity_NTU_Up + Master_analysis_table$Chl_ug_L_Up +
                         Master_analysis_table$avg_depth_cm + Master_analysis_table$d_bw_sondes_m +
                         Master_analysis_table$avg_m_hr + Master_analysis_table$Avg_OC_Ratio ) 
                         # Bivavle density is essentially the same as site, not sure if needed. May be appropriate NPD vs NPSM  
                         #Master_analysis_table$Bivalve_den_m2)

summary(LM_PrctChl_All)
```
 
> I'm not sure if narrowing down the data to Filtration Trials only and then only significant Filtration trials helps predict. Wouldn't the model be stronger if all the data was included? How about bivalve density - the numbers are the same for each site across trials- essentially the same as Site effect?

### LM - Filtraiton Trials Only
```{r LM_PrctChl_Filter, fig.height=15, fig.width=6, cache=TRUE}
Filtration_only_Analysis <- Master_analysis_table %>% 
  filter(Experiment %in% c("Filtration")) # Filtration trials only - exclude Negative controls

LM_PrctChl_Filter <- lm(Filtration_only_Analysis$pcnt_Chl_rmvd ~
                         # site logic variables - SR not included - would break model to include all sites
                         Filtration_only_Analysis$NPD + Filtration_only_Analysis$NPSM + Filtration_only_Analysis$MB + 
                         # Field notes logic variables
                         Filtration_only_Analysis$Wind + Filtration_only_Analysis$G_upstream + Filtration_only_Analysis$Daylight +
                         Filtration_only_Analysis$Sonde_fell + Filtration_only_Analysis$Boat_wake + Filtration_only_Analysis$Algae +
                         # Quantatative variables
                         Filtration_only_Analysis$Temp_C_Up + Filtration_only_Analysis$Sal_ppt_Up +
                         Filtration_only_Analysis$Turbidity_NTU_Up + Filtration_only_Analysis$Chl_ug_L_Up +
                         Filtration_only_Analysis$avg_depth_cm + Filtration_only_Analysis$d_bw_sondes_m +
                         Filtration_only_Analysis$avg_m_hr + Filtration_only_Analysis$Avg_OC_Ratio)

summary(LM_PrctChl_Filter)
```

### LM - Filtration Trials w/ sig Filtration
```{r LM_PrctChl_sigFilter, fig.height=15, fig.width=6, cache=TRUE}
# Filtration Trials with significant Chl_diff
FilterWithFiltration <- Master_analysis_table %>% 
  filter(p.value <= 0.05 & Filter_trial == TRUE)
  
LM_PrctChl_sigFilter <- lm(FilterWithFiltration$pcnt_Chl_rmvd ~
                         # site logic variables 
                         FilterWithFiltration$NPD + FilterWithFiltration$NPSM + FilterWithFiltration$MB + 
                         # Field notes logic variables
                         FilterWithFiltration$Wind + FilterWithFiltration$G_upstream + FilterWithFiltration$Daylight +
                         FilterWithFiltration$Sonde_fell + FilterWithFiltration$Boat_wake + #FilterWithFiltration$Algae +
                         # Quantatative variables
                         FilterWithFiltration$Temp_C_Up + FilterWithFiltration$Sal_ppt_Up +
                         FilterWithFiltration$Turbidity_NTU_Up + FilterWithFiltration$Chl_ug_L_Up +
                         FilterWithFiltration$avg_depth_cm + FilterWithFiltration$d_bw_sondes_m +
                         FilterWithFiltration$avg_m_hr + FilterWithFiltration$Avg_OC_Ratio)

summary(LM_PrctChl_sigFilter)
```

FR X TPM
=====================================

### Filtration by site (all data)
```{r FR vs TPM, fig.height=5, fig.width=12, cache=TRUE}
Filter_data <- Master_analysis_table %>% 
                     filter(Experiment == "Filtration")

FR_TPM_box <- ggplot((Filter_data), aes(Site, L_hr_m2)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Hab_FR_Label)

Chl_Rmd_TPM_box <- ggplot(Filter_data, aes(Site, pcnt_Chl_rmvd)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Prt_Chl_Label)

grid.arrange(FR_TPM_box, Chl_Rmd_TPM_box, nrow = 1)

```

### Filtration by site (Positive values only) 
```{r FR by site positive only, fig.height=5, fig.width=12, cache=TRUE}
FR_data_pos <- Master_analysis_table %>% 
                     filter(Experiment == "Filtration" &
                            L_hr_m2 > 0)

FR_TPM_box_pos <- ggplot((FR_data_pos), aes(Site, L_hr_m2)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Hab_FR_Label,
       title = 'Positive L/hr/m^2 only')

Chl_Rmd_data_pos <- Master_analysis_table %>% 
                     filter(Experiment == "Filtration" &
                            pcnt_Chl_rmvd > 0)

Chl_Rmd_box_pos <- ggplot((Chl_Rmd_data_pos), aes(Site, pcnt_Chl_rmvd)) +
  geom_boxplot(color = Site_colors) +
  theme_classic() +
  stat_summary(fun.data = n_mean_stats, geom = "text") +
  labs(x = 'Site',
       y = Prt_Chl_Label,
       title = 'Positive % Chl Rmd only')

grid.arrange(FR_TPM_box_pos, Chl_Rmd_box_pos, nrow = 1)
```

### Filtration vs TPM (Filtration Trials only)
```{r, fig.height=5, fig.width=12, cache=TRUE}
FR_TPM_graph <- ggplot((Filter_data), aes(Avg_TPM, L_hr_m2 )) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_TPM_graph <- ggplot((Filter_data), aes(Avg_TPM, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  # geom_abline(aes(intercept=0, slope=1)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = TPM_Label,
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_TPM_graph, Chl_Rmd_TPM_graph, nrow = 1)
```

### FR TPM Linear Model
```{r, cache=TRUE}
FR_TPM_lm <- lm(data = Filter_data, L_hr_m2 ~ Avg_TPM)
summary(FR_TPM_lm)
```

### diagnostic plots
```{r, cache=TRUE}
par(mfrow=c(2,2))
plot(FR_TPM_lm)

```

Filtration X OC 
=====================================

### Filtration vs OC
```{r FR vs OC, fig.height=5, fig.width=12, cache=TRUE}
FR_OC_graph <- ggplot(Filter_data, aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_OC_graph <- ggplot(Filter_data, aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  guides(fill = FALSE) +
  # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FR_OC_graph, Chl_Rmd_OC_graph, nrow = 1)
```

### FR by OC Linear Model
```{r, cache =TRUE}
FR_OC_lm <- lm(data = Filter_data, L_hr_m2 ~ Avg_OC_Ratio)
summary(FR_OC_lm)
```

### Diagnosic Plots
```{r}
par(mfrow=c(2,2))
plot(FR_OC_lm)
```

### Deanza FR by OC
```{r Deanza_Filter_OC, fig.height=5, fig.width=12}
FR_OC_NPD_graph <- ggplot(Filter_data %>% filter(Site == "Deanza"),
                          aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Hab_FR_Label,
       title = 'Newport Deanza Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_OC_NPD_graph <- ggplot(Filter_data %>% filter(Site == "Deanza"),
                          aes(Avg_OC_Ratio, pcnt_Chl_rmvd)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = Prt_Chl_Label,
       title = 'Newport Deanza Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
grid.arrange(FR_OC_NPD_graph, Chl_Rmd_OC_NPD_graph, nrow = 1)
```

### Deanza FR by OC Linear Model
```{r}
FR_OC_NPD_lm <- lm(data = (Filter_data %>% filter(Site == "Deanza")), L_hr_m2 ~ Avg_OC_Ratio)
summary(FR_OC_NPD_lm)
```

### Diagnostic plot
```{r}
par(mfrow=c(2,2))
plot(FR_OC_NPD_lm)
```

### Morro Bay FR by OC
```{r}
FR_OC_MB_graph <- ggplot(Filter_data %>%filter(Site == "Morro Bay"),
                           aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = 'Clearence Rate (L/hr/m^2)',
       title = 'Morro Bay Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
    # line equation on graph
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(FR_OC_MB_graph)
```

### MB FR by OC Linear Model
```{r}
FR_OC_MB_lm <- lm(data = (Filter_data %>% filter(Site == "Morro Bay")), L_hr_m2 ~ Avg_OC_Ratio)
summary(FR_OC_MB_lm)
```

### Diagnositc plots
```{r}
par(mfrow=c(2,2))
plot(FR_OC_NPD_lm)
```

### San Rafael FR by OC
```{r}
# San Rafael only
FR_OC_SR_graph <- ggplot(Master_analysis_table %>% filter(Site == "San Rafael"),
                           aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = 'Clearence Rate (L/hr/m^2)',
       title = 'San Rafael Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

plot(FR_OC_SR_graph)
```

### SR FR by OC Linear Model
```{r}
FR_OC_SR_lm <- lm(data = (Filter_data %>% filter(Site == "San Rafael")), L_hr_m2 ~ Avg_OC_Ratio)
summary(FR_OC_SR_lm)
```

### Diagnostic plots
```{r}
par(mfrow=c(2,2))
plot(FR_OC_SR_lm)
```

### Shellmaker only
```{r}
FR_OC_NPSM_graph <- ggplot(Filter_data %>% filter(Site == "Shellmaker"),
                           aes(Avg_OC_Ratio, L_hr_m2)) +
  geom_smooth(method = lm, se = T, level = 0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) +  
  theme_classic() +
  labs(x = 'Organic Content of Seston (fraction)',
       y = 'Clearence Rate (L/hr/m^2)',
       title = 'Shellmaker Filtration Trials (Linear Model)') +
  guides(fill = FALSE) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(FR_OC_NPSM_graph)
```

### Shellmaker FR by OC Linear Model
```{r}
FR_OC_NPSM_lm <- lm(data = (Filter_data %>% filter(Site == "Shellmaker")), L_hr_m2 ~ Avg_OC_Ratio)
summary(FR_OC_NPSM_lm)
```

### Diagnostic Plots
```{r}
par(mfrow=c(2,2))
plot(FR_OC_NPSM_lm)
```

L/hr/m^2 X WQ
=====================================

### Temperature
```{r FR_Temp, fig.height=10, fig.width=12, echo=FALSE}
FR_Temp <- ggplot(Filter_data, aes(Temp_C_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_Temp <- ggplot(Filter_data, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

FR_pos_Temp <- ggplot(FR_data_pos, aes(Temp_C_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Temp <- ggplot(Chl_Rmd_data_pos, aes(Temp_C_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Temperature Upstream (C)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_Temp, Chl_Rmd_Temp, FR_pos_Temp, Chl_Rmd_pos_Temp, nrow = 2)
```

### FR by Temp Linear Model
```{r}
FR_temp_lm <- lm(data = Filter_data, L_hr_m2 ~ Temp_C_Up)
summary(FR_temp_lm)
```

### Diagnostic Plots
```{r}
par(mfrow=c(2,2))
plot(FR_temp_lm)
```

### Salinity
```{r FR_Salinity, fig.height=10, fig.width=12, echo=FALSE}

FR_Sal <- ggplot(Filter_data, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_Sal <- ggplot(Filter_data, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

FR_pos_Sal <- ggplot(FR_data_pos, aes(Sal_ppt_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Hab_FR_Label,
       title = 'Positive FR only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Sal <- ggplot(Chl_Rmd_data_pos, aes(Sal_ppt_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Salinity Upstream (ppt)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_Sal, Chl_Rmd_Sal, FR_pos_Sal, Chl_Rmd_pos_Sal, nrow = 2)
```

### FR by Salinity Linear Model
```{r}
FR_Sal_lm <- lm(data = Filter_data, L_hr_m2 ~ Sal_ppt_Up)
summary(FR_Sal_lm)
```

### Diagnostic Plots
```{r}
par(mfrow=c(2,2))
plot(FR_Sal_lm)
```

### Chlorophyll 
```{r FR_Chl, fig.height=10, fig.width=12, echo=FALSE}
FR_Chl <- ggplot(Filter_data, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_Chl <- ggplot(Filter_data, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

FR_pos_Chl <- ggplot(FR_data_pos, aes(Chl_ug_L_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Chl <- ggplot(Chl_Rmd_data_pos, aes(Chl_ug_L_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) +  
  theme_classic() +
  labs(x = 'Chlorophyll Upstream (ug/L)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_Chl, Chl_Rmd_Chl, FR_pos_Chl, Chl_Rmd_pos_Chl, nrow = 2)
```

### FR by Chl Linear Model
```{r}
FR_Chl_lm <- lm(data = Filter_data, L_hr_m2 ~ Chl_ug_L_Up)
summary(FR_Chl_lm)
```

### Diagnostic Plots
```{r}
par(mfrow=c(2,2))
plot(FR_Chl_lm)
```

### Turbidity
```{r FR_Turbidity, fig.height=10, fig.width=12, echo=FALSE}
FR_Turb <- ggplot(Filter_data, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_Turb <- ggplot(Filter_data, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'All Filtration Trials') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
FR_pos_Turb <- ggplot(FR_data_pos, aes(Turbidity_NTU_Up, L_hr_m2)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Hab_FR_Label,
       title = 'Positive FR Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

Chl_Rmd_pos_Turb <- ggplot(Chl_Rmd_data_pos, aes(Turbidity_NTU_Up, pcnt_Chl_rmvd)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  theme_classic() +
  labs(x = 'Turbidity Upstream (NTU)',
       y = Prt_Chl_Label,
       title = 'Positive Chl Removed Only') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(FR_Turb, Chl_Rmd_Turb, FR_pos_Turb, Chl_Rmd_pos_Turb, nrow =2)
```

### FR by Turbidity Linear Model
```{r}
FR_Turb_lm <- lm(data = Filter_data, L_hr_m2 ~ Turbidity_NTU_Up)
summary(FR_Turb_lm)
```

### Diagnostic Plots
```{r}
par(mfrow=c(2,2))
plot(FR_Turb_lm)
```

TPM & OC
=====================================

### TPM by OC
```{r TPM vs OC, echo=FALSE}
TPM_OC <- ggplot(data = Avg_TPM_summary_table, aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors) + 
  labs(x = TPM_Label, y = "Average Organic Content Ratio", title = "All Trials") + 
  theme_classic() +
  #geom_text(aes(label=Date), nudge_x = 0.007, nudge_y = 0, check_overlap = T)
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(TPM_OC)
```

> No reason to exclude that low NPD value right?

```{r eval=FALSE, include=FALSE}
##  No reason to exclude low data point
TPM_OC_no_ND_low <- ggplot(data = (Avg_TPM_summary_table %>% filter(!(Site == "Deanza") | !(Date == "4/18/19"))),
                             aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors) + 
  labs(x = "Total Particulate Matter", y = "Average Organic Content Ratio", title = "TPM --> OC", 
       subtitle = "Excluding NPD 4/18/19") + 
  theme_classic() +
  #geom_text(aes(label=Date), nudge_x = 0.007, nudge_y = 0, check_overlap = T)
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(TPM_OC_no_ND_low)
```

### Individual Sites TPM vs OC
```{r TPM_OC_facet - By Site, echo=FALSE}
OC_TPM_by_Site <- Avg_TPM_summary_table %>% 
  ggplot(aes(x = Avg_TPM, y = Avg_OC_Ratio, group = Site)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = TPM_Label,
       y = 'Average Organic Content Ratio',
       title = 'OC predicted by TPM (g/L)') +
  facet_wrap(~ Site) +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(OC_TPM_by_Site)
```

> Large spread of relationship among sites. Different TPM:OC signatures and relationships at different sites.

### TPM vs OC by sites
```{r TPM_OC_Sites, fig.height=10, fig.width=12,}
TPM_OC_Deanza <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Deanza")),
                        aes(x = Avg_TPM, y = Avg_OC_Ratio)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Deanza") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_NPSM <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Shellmaker")), 
                     aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Shellmaker") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_SR <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "San Rafael")),
                   aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "San Rafael") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

TPM_OC_MB <- ggplot(data = (Avg_TPM_summary_table %>% filter(Site == "Morro Bay")), 
                   aes(x = Avg_TPM, y = Avg_OC_Ratio, label = Date)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) + 
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = TPM_Label, 
       y = "Average Organic Content Ratio", 
       title = "Morro Bay") + 
  theme_classic() +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

grid.arrange(TPM_OC_Deanza, TPM_OC_NPSM, TPM_OC_SR, TPM_OC_MB, nrow = 2)
```

DTW - Shell length
=====================================

### Newport Olympia Shell length vs DTW
```{r Oly_DTW_Shell_length, echo=FALSE}
#Olympia DTW predicted by Shell Length - Newport, CA
# All excavation quadrat samples processed to date aggregated 
NPD_oly <- NPD_density %>% 
  filter(species == "O. lurida") %>% 
  drop_na() %>% 
  as_tibble() 

Oly_shell_DTW <- ggplot(NPD_oly, aes(length_mm, tissue_dry_weight_g)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'With outlier (bad data)') +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")

plot(Oly_shell_DTW)
```

> Outlier probably sample processing error or error in data entry. 

### DTW Shell length Outlier analysis (mean -+ SD * 2.2)
```{r Oly_DTW_Shell_length_outier_removed}
# function to calculate average, standard deviation, outlier data. 
find_outlier <- function(data){
  average <- mean(data)
  stdev <- sd(data)
  # Outlier data defined by outside 2.2 standard deviations from the mean 
  outlier <- ifelse((data < (average - 2.2 * stdev) | (data > (average + 2.2 * stdev))),
         TRUE, FALSE)
}

# Remove outlier from graph 
NPD_oly_DTW_outlier <- NPD_oly %>%
  mutate(DTW_outlier = find_outlier(NPD_oly$tissue_dry_weight_g))
# Graph with outliers removed
Oly_shell_DTW_rm_out <- ggplot(NPD_oly_DTW_outlier %>% 
                                  filter(DTW_outlier == FALSE), 
                                aes(length_mm, tissue_dry_weight_g)) +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
 # scale_color_manual(values = Site_colors, guide=FALSE) + 
  labs(x = 'Shell Length (mm)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Shell Length - Newport, CA',
       subtitle = 'Outlier removed (outside mean +- 2.2 SD)') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")

plot(Oly_shell_DTW_rm_out)
```

> Shell length explains 48% of Dry Tissue Weight. Compare this relationship to Gray & Langdon (Yaquina Bay)

### Linear model without outlier
```{r}
Oly_DTW_lm_rm_out <- lm(data = NPD_oly_DTW_outlier %>% 
                           filter(DTW_outlier == FALSE),
                         tissue_dry_weight_g ~ length_mm)

summary(Oly_DTW_lm_rm_out)
```

### Diagnostic plots
```{r}
par(mfrow=c(2,2))
plot(Oly_DTW_lm_rm_out)
```

### Total Wet Weight vs Dry Tissue Weight
```{r}
Oly_TWW_DTW<- ggplot(NPD_oly, aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = 'Total wet weight (g)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Total Wet Weight - Newport, CA') +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "top")
plot(Oly_TWW_DTW)
```

### TWW vs DTW (remove outlier)
```{r}
# use DTW outlier data to plot graph
Oly_TWW_DTW_rm_out <- ggplot(NPD_oly_DTW_outlier %>% 
                                  filter(DTW_outlier == FALSE),
                        aes(total_wet_weight_g, tissue_dry_weight_g)) +
  geom_point(aes(color = Site)) +
  scale_color_manual(values = Site_colors, guide=FALSE) + 
  theme_classic() +
  labs(x = 'Total wet weight (g)',
       y = 'Dry Tissue Weight (g)',
       title = 'Olympia Oyster DTW predicted by Total Wet Weight - Newport, CA') +
  geom_smooth(method=lm, se=TRUE, level=0.95, color = 'grey50') +
  ggpmisc::stat_poly_eq(aes(label = paste("atop(",..eq.label.., ",",..adj.rr.label.., ")", sep ="")),
               formula = x_y_formula,
               parse = TRUE,
               label.x = "right",
               label.y = "bottom")
plot(Oly_TWW_DTW_rm_out)
```

> Gray and Langdon (2017): "Unless explicitly mentioned, DTW of experimental oysters was estimated using the species-specific allometric relationship between DTW and total wet weight (TWW), which were determined in preliminary analysis (O. lurida: DTW = 0.0044TWW − 0.043, R2 =0.93, F1,32 =78.80, p value <0.0001; C. gigas: DTW = 0.039TWW − 0.06, R2 =0.89, F1,29 = 225.97, p value <0.0001).

### Linear model without outlier
```{r}
Oly_TWW_DTW_lm_rm_out <- lm(data = NPD_oly_DTW_outlier %>% 
                           filter(DTW_outlier == FALSE),
                         tissue_dry_weight_g ~ total_wet_weight_g)

summary(Oly_TWW_DTW_lm_rm_out)
```

### Diagnostic plots
```{r}
par(mfrow=c(2,2))
plot(Oly_TWW_DTW_lm_rm_out)
```

Up & Down Chl
=====================================

### Facet Plots
```{r Bar_Graphs_up_vs_down, eval=FALSE, include=FALSE}
Bar_up_down_data <- Master_analysis_table %>%
  select(Experiment, Date, Site, Chl_ug_L_Up, Chl_ug_L_Down) %>%
  rename(Upstream = Chl_ug_L_Up, Downstream = Chl_ug_L_Down) %>%  
  gather(Upstream, Downstream, key = Position, value = Chl_ug_L) %>% 
  mutate(Position = fct_relevel(Position, 'Upstream', 'Downstream')) %>% 
  mutate(Site = fct_relevel(Site, 'Deanza', 'Shellmaker', 'San Rafael', 'Morro Bay')) %>% 
  mutate(Site_exp_date = paste(Site, Experiment,
                                     Date,
                                     sep = ' ')) %>% 
  mutate(Exp_Date = paste(Experiment, Date, sep = ' ')) %>% 
  arrange(Site, mdy(Date))

#Bar_up_down_data$Position <- as.factor(Bar_up_down_data$Position)

Paired_bar_chl_graph <- ggplot(data = Bar_up_down_data, aes(x = Site_exp_date, y = Chl_ug_L, fill = Position)) +
    geom_bar(stat="identity", position = "dodge") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    facet_grid(~ Site, scales = "free", space = "free") + #'free' allows axis b/w sites uneaven
    geom_bar(data = (Bar_up_down_data %>%
                       filter(!Experiment %in% c('Filtration'))),
             color = "grey22",
             stat="identity",
             position = "dodge") +
    labs(x = 'Experiment', y = 'Chlorophyl (ug/L)')

plot(Paired_bar_chl_graph)
```

### Graphs using grid.arrange()
```{r Bar_Graphs_up_vs_down_grid.arrange, eval=FALSE, include=FALSE}
############## Try 2 ####### make separate graphs, combine using grid.arrange()

##### Can't figure out how to properly label x axis. Works with Exp_Date, but can't shorten without messing up data:label pairs. Can't spend more time on this right now. come back if time -AM 2020_3_3

NPD_bar_data <- Bar_up_down_data %>% 
  filter(Site == "Deanza") %>% 
  mutate(graph_Label = ifelse(grepl("^Filtration", Exp_Date), str_replace(Exp_Date, "Filtration ", ""),
                             str_replace(Exp_Date, "^Neg Control .", "")))

NPD_bar_graph <- ggplot(data = NPD_bar_data, aes(x = Exp_Date, y = Chl_ug_L, 
                                                 fill = Position)) +
    geom_col(position = position_dodge(width = 0.9, preserve = "single")) +
    geom_col(data = (NPD_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.x = element_blank(),
          legend.position = c(0.9, 0.8),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(y = 'Chlorophyll a (ug/L)', title = "Newport Deanza") +
  # This labels the x-axis
    #scale_x_discrete(labels = Exp_Date) +
    ylim(0, 8)
NPD_bar_graph

NPSM_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'Shellmaker')

NPSM_bar_graph <- ggplot(data = NPSM_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (NPSM_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "Newport Shellmaker") +
    # scale_x_discrete(labels = NPSM_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE) 

MB_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'Morro Bay')

MB_bar_graph <- ggplot(data = MB_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (MB_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "Morro Bay") +
   # scale_x_discrete(labels = MB_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE)

SR_bar_data <- Bar_up_down_data %>% 
  filter(Site == 'San Rafael')

SR_bar_graph <- ggplot(data = SR_bar_data,
                          aes(x = Exp_Date, y = Chl_ug_L, fill = Position)) +
    geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
    geom_col(data = (SR_bar_data %>% # add boarder around Neg Control experiments
                       filter(!Experiment %in% c('Filtration'))),
             color = "black",
             position = "dodge") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          plot.title = element_text(hjust = 0.5)) + # center title
    labs(title = "San Rafael") +
    #scale_x_discrete(labels = SR_bar_data$Date) +
    ylim(0, 8) +
    guides(fill = FALSE)

Chl_graphs <- list(NPD_bar_graph, NPSM_bar_graph, SR_bar_graph, MB_bar_graph) 
all_chl_graphs <- grid.arrange(grobs = Chl_graphs,
             widths = c(1,1,1,1,1,1,1,1,1,1,1,1,1,1),
             layout_matrix = rbind(c(NA,1,1,1,1,1,1,1,1,1,1,1,1, NA),
                                   c(2,2,2,2,2,3,3,3,3,3,4,4,4,4)))
plot(all_chl_graphs)
#ggsave("Insitu_Filter_up_vs_down_all_sites.png", all_chl_graphs)
```

```{r Paire t tests, eval=FALSE, include=FALSE}
#### Paired t-test all filtration trials --- Mean Upstream Chl vs Mean Downstream Chl
####### Double Check this analysis - AM 2020_3_22
Master_analysis_table_FILTER <- Master_analysis_table %>%
  filter(Experiment == 'Filtration')

t.test(Master_analysis_table_FILTER$Chl_ug_L_Up,
       Master_analysis_table_FILTER$Chl_ug_L_Down,
       alternative =c("greater"),
       paired = TRUE,
       conf.level = 0.95)
## No difference between upstream and downstream Chl across all Filtraiton trails

##### Paired t-test on Positive L/hr/m^2 Filtration trails
Master_analysis_table_posFILTER <- Master_analysis_table %>% 
  filter(Experiment == 'Filtration',
         L_hr_m2 > 0)

t.test(Master_analysis_table_posFILTER$Chl_ug_L_Up,
       Master_analysis_table_posFILTER$Chl_ug_L_Down,
       alternative =c("greater"),
       paired = TRUE,
       conf.level = 0.95)
# No difference between upstream and downstream Chl across positive Filtration trials

######### Paired t-test on all trials (Filtraiton & Neg Control)
t.test(Master_analysis_table$Chl_ug_L_Up,
       Master_analysis_table$Chl_ug_L_Down,
       paried = TRUE,
       alternative =c("greater"),
       conf.level = 0.95)
## No difference between upstream and downstream Chl
```

Bivalve Density
=====================================

### Bivalve Density
```{r Bivalve_Density, fig.height=6, fig.width=8}
# read in bivalve density data from cleaned data file
Bivalve_Den_data <- fread(file.path(Bivalve_output_directory, "Bivalve_Density_summary.csv"))

# replace NAs with 0s
Bivalve_Den_data[is.na(Bivalve_Den_data)] <- 0

Bivalve_Den_data <- Bivalve_Den_data %>% 
  # move species from individual columns to a single column with new density column to contain data
  pivot_longer(c(Adula_diegensis_m2, Musculista_senhousia_m2,Mytilus_galloprovincialis_m2,
                 Ostrea_lurida_m2, Crassostrea_gigas_m2,Argopecten_ventricosa_m2, 
                 Geukensia_demissa_m2, Crassostrea_gigas_m2), 
               names_to = "Species", 
               values_to =  "individuals_m2") %>% 
  # remove "_m2" from species names in Species column
  mutate(Species = str_replace(Species, "_m2", ""))

#Reorder levels of Site factor - display North to South
order_by_site <- c("San Rafael", "Morro Bay", "Shellmaker", "Deanza") 
Bivalve_Den_data <- arrange(transform(Bivalve_Den_data, Site = factor(Site,levels = order_by_site)), Site)

# wes_palettes # lists all current palattes 
# Color palette for Species - Royal2, Darjeeling2, Cavalcanti1, BottleRocket2, IsleofDogs1
Species_colors <- rev(wes_palette("IsleofDogs1", 7, type = c("continuous")))

# Stacked bar graph
Bivalve_Den_graph <- ggplot(Bivalve_Den_data, aes(Site)) + 
  geom_col(aes(x = Site, y = individuals_m2, fill = Species)) +
  geom_text(aes(label = round(Bivalve_den_m2,0), y = Bivalve_den_m2), 
            vjust = -0.5) +
  theme_classic() +
  scale_fill_manual(values = Species_colors) +
  scale_y_continuous(breaks = seq(0, max(Bivalve_Den_data$Bivalve_den_m2), by = 500)) +
  labs(y = expression("Individuals per m"^2))
  
Bivalve_Den_graph
```

> Data for each site is from a single survey

```{r Species_Density_Graphs, eval=FALSE, cache=TRUE, include=FALSE}
# Graph Density by Species, exclude absent species

############## Newport Deanza ###################
(Graph_NPD_species_den <-
   ggplot(NPD_may18_species_den[which(NPD_may18_species_den$species_den_m2>0),], 
                               aes(Species, species_den_m2, fill = Species)) + 
  geom_col() + # columns
  theme_classic() + 
  labs (x = 'Bivlave Species', 
        y = 'Density (individuals / m^2)', 
        title = 'Newport Deanza Bivalve Density',
        subtitle = 'May 2018 Survey') +
  guides(fill = FALSE) + # removes color legend
  geom_text(aes(label = species_den_m2), vjust = -0.5)) # able to round values? 
                                                                      
############## Newport Shellmaker ##############
(Graph_NPSM_species_den <-   ggplot(NPSM_may18_species_den[which(NPD_may18_species_den$species_den_m2>0),], 
                                 aes(Species, species_den_m2, fill = Species)) + 
  geom_col() + # columns
  theme_classic() + 
  labs (x = 'Bivlave Species', 
        y = 'Density (individuals / m^2)', 
        title = 'Newport Shellmaker Bivalve Density',
        subtitle = 'May 2018 Survey') +
  guides(fill = FALSE) + # removes color legend
  geom_text(aes(label = species_den_m2), vjust = -0.5)) # able to round values? 


# Save graph to "./0_Graph_Output/Graphs_Bivalve_Density"
# Not needed Whit Rmd Knit yet
######### May need to reformat .pdf  ###########
#ggsave(file.path(Bivlave_density_graph_directory, "NPD_may18_bivalve_species_density.pdf"), Graph_NPD_species_den )
#ggsave(file.path(Bivlave_density_graph_directory, "NPSM_may18_bivalve_species_density.pdf"), Graph_NPSM_species_den )

##### FIgure ####### -->> biomass comparison among species
```